### 2014-01-31 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/abstract.tex
Draft abstract

A variety of conventional feature selection methods choose informative
features or feature sets and empirically lead to good accuracy
improvements, but few focus on feature selection w.r.t.\ specific loss
functions; in particular, there seems to be little work on feature
selection for classifiers if a secondary objective after accuracy is
either precision or recall.  In this paper we propose a novel
probabilistic model of feature selection based on a probabilistic
voting model and argue that MAP inference w.r.t. to two extreme
objectives in this model yield respective high precision and high
recall feature selection approaches.  We derive an efficient formula
for feature selection in this model using the filtering framework and
empirically compare to a wide variety of existing filtering-based
feature selection methods.  Results show that our high precision and
high recall feature selection approaches do reliably improve these
respective objectives.  Furthermore, our modeling framework provides
us with a way to interpret existing feature selection methods and
suggests that the use of greedy approaches (such as mutual
information) appear to maximize precision while diversity-based
approaches (such as MRMR) appear to maximize recall, hence providing
us with a framework for reinterpreting the loss functions implicitly
targeted by existing feature selection methods.

### 2014-01-31  feature-selection-high-recall/FeatureSelectionProject/doc/derivations/Derivation_old.tex
added derivations in pdf and tex, plots in pdf and vsd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% ICML 2014 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Use the following line _only_ if you're still using LaTeX 2.09.
%\documentstyle[icml2014,epsf,natbib]{article}
% If you rely on Latex2e packages, like most moden people use this:
\documentclass{article}

%for equations
\usepackage{amsmath}
\usepackage[margin=0.5in]{geometry}

% For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}

\begin{document}

\section{Derivation Approach 1}
Given a set of features $F$ where selected features are denoted as $f_i \in F$, we aim to select an optimal subset of features $F^* \subset F$ (where $|F^*_k| = k$ and $k < |F|$) relevant and not redundant to a given classifier and classification task. For computational efficiency, we will build $F^*_k$ in a greedy manner by choosing the next optimal feature $f^*_k$ given the previous set of optimal features $F^*_{k-1} = \left\lbrace f^*_1,\dots, f^*_{k-1} \right\rbrace$ and recursively defining $F^*_k = F^*_{k-1}\cup \lbrace f^*_k\rbrace$ with $F^*_0 = \emptyset$.

To begin the derivation, we provide a directed graphical model in Figure 1 to formalize the independence assumptions in probabilistic feature selection model for classification tasks. Shaded nodes represent observed variables while unshaded nodes are latent. The observed variables are the vector of attributes $\vec{x}^d$, the features $f_i$ (where for $1 \leq i \leq k$, $f_i \in F$) and the actual label $y^d$. The $y^d_i$ are binary random variables described by the conditional probability given $\vec{x^d}$ and $ f_i$, where $f_i$ are binary variables indicating whether the respective attribute $x^d_i$ are relevant (1) or not (0) to the classification task.

The conditional probabilities table (CPTs) are as follows: $P(y^d_i|\vec{x}^d, f_i)$ represents the classification label prediction distribution given the data $\vec{x}^d$ and feature $f_i$.

We now formally define our initial objective: 
\[
f_{k}^* = \operatorname*{arg\,max}_{f_k} E_D[P\left(y^d | \vec{x}^d,F_{k-1}^{*},f_k\right)]
\]
Since jointly optimizing this objective is NP-hard, we take a greedy approach where we choose the best $f^*_k$ assuming $F^*_{k-1}$ is given. Then we can greedily optimize this objective as follows:

\begin{gather}
f_{k}^* = \operatorname*{arg\,max}_{f_k} E_D[P\left(y^d | \vec{x}^d,F_{k-1}^{*},f_k\right)]\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \frac{1}{|D|} \sum_{d \in D} P(y^d | \vec{x}^d,F_{k-1}^{*},f_k)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} \frac{P(y^d, \vec{x}^d, F_{k-1}^{*},f_k)}{P(\vec{x}^d, F_{k-1}^{*},f_k)}\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} \sum_{{\{y_{i}^d\}}_{1\leq i \leq k}} \frac{P(y^d, \vec{x}^d, F_{k-1}^{*},f_k,\{y_{i}^d\}_{1\leq i \leq k})}{P(\vec{x}^d, F_{k-1}^{*},f_k)}\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} \sum_{{\{y_{i}^d\}}_{1\leq i \leq k}} \frac{P(y^d| \{y^d_i\}_{1 \leq i \leq k}) \prod_{i=1}^{k-1}\left(P(y_i^d |\vec{x}^d, f_i)\right)P(y_k^d |\vec{x}^d, f_k) P(\vec{x}^d) \prod_{i=1}^{k-1}\left(P(f_i)\right) P(f_k)}{P(\vec{x}^d, F_{k-1}^{*},f_k)}\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} \sum_{{\{y_{i}^d\}}_{1\leq i \leq k}} P(y^d| \{y^d_i\}_{1 \leq i \leq k}) \prod_{i=1}^{k-1}\left(P(y_i^d |\vec{x}^d, f_i)\right)P(y_k^d |\vec{x}^d, f_k)\label{eq:generalderivation}
\end{gather}

Here, we rewrote the expectation of a binary event as its probability, factorized the conditional probability in the joint probability divided by the marginal, marginalized over $\{y^d_i\}_{1 \leq i \leq k}$, factorized joint probability in conditional and prior following the graphical model and exploited d-separation to remove irrelevant conditions and cancel terms in the equation. Thus, we can optimize our initial objective aiming two goals of classification tasks: Precision and Recall. The following sections shows in detail how to develop these approaches.

\subsection{Precision case}
In order to select the subset of features providing high precision classifier we need the agreement of all features predictors $y^d_i$ to do a precise prediction. Therefore, we need a conjunction operation between the predictors $y^d_i$. Considering a binary classification problem, when the actual label is true we need all of the predictors $y^d_i$ equals to true. However, if the actual label were false, just one of the predictors $y^d_i$ would have to be false. Thus the probability  $P(y^d| \{y^d_i\}_{1 \leq i \leq k})$ can be expressed as follows:
\begin{gather}
P(y^d| \{y^d_i\}_{1 \leq i \leq k}) = I\left[y^d = \bigwedge_{i=1}^k y^d_i \right] = 
\begin{cases}
     1 ; y^d = 1 \wedge \{y_i^d = 1\}_{1 \leq i \leq k}\\
     1 ; y^d = 0 \wedge \{y_i^d\}_{1 \leq i \leq k, \exists{y_i^d\|y_i^d = 0}}\\
     0 ; otherwise
\end{cases}\label{eq:precisioncase}
\end{gather}
According to these assumptions we can continue our derivation for achieve a high precision greedy feature selection algorithm. Here, we combined equations \eqref{eq:generalderivation} and \eqref{eq:precisioncase}, separated each term according to the actual label value $y^d$ and use the probability sum rule to rewire the second term as follows:
\begin{gather}
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} I\left[y^d = \bigwedge_{i=1}^k y^d_i \right] \prod_{i=1}^{k-1}\left(P(y_i^d |\vec{x}^d, f_i)\right)P(y_k^d |\vec{x}^d, f_k)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} I[y^d = 1] \prod_{i=1}^{k-1}\left(P(y_i^d = 1 |\vec{x}^d, f_i)\right)P(y_k^d = 1 |\vec{x}^d, f_k)\\ + I[y^d = 0] \sum_{\substack{\{y_i^d\}_{1 \leq i \leq k},\\ \exists{y_i^d\| y_i^d = 0} }} \prod_{i=1}^{k-1}\left(P(y_i^d |\vec{x}^d, f_i)\right)P(y_k^d |\vec{x}^d, f_k)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} I[y^d = 1] \prod_{i=1}^{k-1}\left(P(y_i^d = 1 |\vec{x}^d, f_i)\right)P(y_k^d = 1 |\vec{x}^d, f_k)\\ + I[y^d = 0]\left(1 - \prod_{i=1}^{k-1}\left(P(y_i^d = 1 |\vec{x}^d, f_i)\right)P(y_k^d = 1 |\vec{x}^d, f_k) \right)\label{eq:equationForPrecisionCase}
\end{gather}
From \eqref{eq:equationForPrecisionCase} we can intuitively describe how this equations is related with the precision metric defined in the classification evaluation confusion matrix. In the confusion matrix, Precision is calculated dividing the numbers of true positives by the number of all examples predicted as positive (in fact, true positives and false positives). When the actual label $y^d$ is true the second term of \eqref{eq:equationForPrecisionCase} becomes 0 and the first term gives higher score for the feature $f_k$ that provides a higher probability of predict true. Thus, we are stimulating the increasing of true positives in classification task. Meanwhile the actual label $y^d$ is false, the first term of \eqref{eq:equationForPrecisionCase} becomes 0 and the second gives lower score to features $f_k$ that have higher probability of label a given datum $\vec{x}^d$ as true. In this way we are penalizing features that generate false positive and reduce the amount of false positives. Thus, increasing true positives and reducing  false positives we are directly increasing the precision metric.

\subsection{Recall case}
In order to select the subset of features providing higher recall classifier we need at least one feature predictors $y^d_i$ predicting a given label to say that this datum is classified as this label. Therefore, we need a disjunction operation between the predictors $y^d_i$. Considering a binary classification problem, we need at least one predictors $y^d_i$ equals to true when the actual label is true, in order to evaluate the disjunction operation as true. However, if the actual label were false, all of the predictors $y^d_i$ would have to be false. Thus the probability  $P(y^d| \{y^d_i\}_{1 \leq i \leq k})$ can be expressed as follows:
\begin{gather}
P(y^d| \{y^d_i\}_{1 \leq i \leq k}) = I\left[y^d = \bigvee_{i=1}^k y^d_i\right] = 
\begin{cases}
     1 ; y^d = 1 \Rightarrow \{y_i^d\}_{1 \leq i \leq k, \exists{ y_i^d\| y_i^d = 1 }}\\
     1; y^d = 0 \Rightarrow \{y_i^d = 0\}_{1 \leq i \leq k}\\
     0; otherwise
\end{cases}\label{eq:recallcase}
\end{gather}
According to these assumptions we can continue our derivation for achieve a high recall greedy feature selection algorithm. Here, we combined equations \eqref{eq:generalderivation} and \eqref{eq:recallcase}, separated each term according to the actual label value $y^d$ and use the probability sum rule to rewrite the second term as follows:
\begin{gather}
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} I\left[y^d = \bigvee_{i=1}^k y^d_i\right] \prod_{i=1}^{k-1}\left(P(y_i^d |\vec{x}^d, f_i)\right)P(y_k^d |\vec{x}^d, f_k)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} I[y^d = 0] \prod_{i=1}^{k-1}\left(P(y_i^d = 0 |\vec{x}^d, f_i)\right)P(y_k^d = 0 |\vec{x}^d, f_k) \\+ I[y^d = 1] \sum_{\substack{\{y_i^d\}_{1 \leq i \leq k},\\ \exists{ y_i^d\| y_i^d = 1} }} \prod_{i=1}^{k-1}\left(P(y_i^d |\vec{x}^d, f_i)\right)P(y_k^d |\vec{x}^d, f_k)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} I[y^d = 0] \prod_{i=1}^{k-1}\left(P(y_i^d = 0 |\vec{x}^d, f_i)\right)P(y_k^d = 0 |\vec{x}^d, f_k) \\+ I[y^d = 1]\left(1 - \prod_{i=1}^{k-1}\left(P(y_i^d = 0 |\vec{x}^d, f_i)\right)P(y_k^d = 0 |\vec{x}^d, f_k)\right)\label{eq:equationForRecallCase}
\end{gather}
From \eqref{eq:equationForRecallCase} we can intuitively describe how this equations is related with the recall metric defined in the classification evaluation confusion matrix. In the confusion matrix, Recall is calculated dividing the numbers of true positives by the number of all examples that actually are true (in fact, true positives and false negatives). When the actual label $y^d$ is true, the first term of \eqref{eq:equationForRecallCase} becomes 0 and the second gives lower score to features $f_k$ that have higher probability of label a given datum $\vec{x}^d$ as false. Thus, we stimulating features that generate true positive and consequently reduce the amount of false negatives since the sum  of true positives and false negatives is a constant equal to the number of actual true examples in the data set. Thus, increasing true positives and reducing  false negatives we are directly increasing the recall metric.

In addition, when the actual label $y^d$ is false, the second term of \eqref{eq:equationForRecallCase} becomes 0 and the first gives higher score to features $f_k$ that have higher probability of label a given datum $\vec{x}^d$ as false. Thus, we are stimulating the increasing of true negatives and consequently the decreasing of false positives which are not related to recall. However, it could be seen as a surrogate objective that is improve the accuracy metric in the classification task given accuracy is calculated dividing true positives and true negatives by the total number of data points.

\section{Derivation Approach 2}
\begin{gather*}
 f_{k}^* = \operatorname*{arg\,max}_{f_k} log\left( P( D | F_{k-1}^{*},f_k)\right)\\
 f_{k}^* = \operatorname*{arg\,max}_{f_k}  log\left(\prod_{d \in D} P(y^d | \vec{x}^d,F_{k-1}^{*},f_k)\right)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} log\left(\frac{P(y^d, \vec{x}^d, F_{k-1}^{*},f_k)}{P(\vec{x}^d, F_{k-1}^{*},f_k)}\right)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} log\left(\sum_{{\{y_{i}^d\}}_{1\leq i \leq k}} \frac{P(y^d, \vec{x}^d, F_{k-1}^{*},f_k,\{y_{i}^d\}_{1\leq i \leq k})}{P(\vec{x}^d, F_{k-1}^{*},f_k)}\right)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} log\left(\sum_{{\{y_{i}^d\}}_{1\leq i \leq k}} \frac{P(y^d| \{y^d_i\}_{1 \leq i \leq k}) \prod_{i=1}^{k-1}\left(P(y_i^d |\vec{x}^d, f_i)\right)P(y_k^d |\vec{x}^d, f_k) P(\vec{x}^d) \prod_{i=1}^{k-1}\left(P(f_i)\right) P(f_k)}{P(\vec{x}^d, F_{k-1}^{*},f_k)}\right)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} log\left(\sum_{{\{y_{i}^d\}}_{1\leq i \leq k}} P(y^d| \{y^d_i\}_{1 \leq i \leq k}) \prod_{i=1}^{k-1}\left(P(y_i^d |\vec{x}^d, f_i)\right)P(y_k^d |\vec{x}^d, f_k)\right)\\  
\end{gather*}
\subsection{Precision case}
\begin{gather}
P(y^d| \{y^d_i\}_{1 \leq i \leq k}) = I\left[y^d = \bigwedge_{i=1}^k y^d_i \right] = 
\begin{cases}
     1 ; y^d = 1 \wedge \{y_i^d = 1\}_{1 \leq i \leq k}\\
     1 ; y^d = 0 \wedge \{y_i^d\}_{1 \leq i \leq k, \exists{y_i^d\|y_i^d = 0}}\\
     0 ; otherwise
\end{cases}
\end{gather}
\begin{gather*}
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} log\left(I\left[y^d = \bigwedge_{i=1}^k y^d_i \right] \prod_{i=1}^{k-1}\left(P(y_i^d |\vec{x}^d, f_i)\right)P(y_k^d |\vec{x}^d, f_k)\right)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} log\left(I[y^d = 1] \prod_{i=1}^{k-1}\left(P(y_i^d = 1 |\vec{x}^d, f_i)\right)P(y_k^d = 1 |\vec{x}^d, f_k) + I[y^d = 0] \sum_{\substack{\{y_i^d\}_{1 \leq i \leq k},\\ \exists{ y_i^d\| y_i^d = 0 }}} \prod_{i=1}^{k-1}\left(P(y_i^d |\vec{x}^d, f_i)\right)P(y_k^d |\vec{x}^d, f_k)\right)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} log\left(I[y^d = 1] \prod_{i=1}^{k-1}\left(P(y_i^d = 1 |\vec{x}^d, f_i)\right)P(y_k^d = 1 |\vec{x}^d, f_k) + I[y^d = 0](1 - \prod_{i=1}^{k-1}\left(P(y_i^d = 1 |\vec{x}^d, f_i)\right)P(y_k^d = 1 |\vec{x}^d, f_k))\right)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} I[y^d = 1]log\left( \prod_{i=1}^{k-1}\left(P(y_i^d = 1 |\vec{x}^d, f_i)\right)P(y_k^d = 1 |\vec{x}^d, f_k)\right) \\+ I[y^d = 0] log\left( 1 - \prod_{i=1}^{k-1}\left(P(y_i^d = 1 |\vec{x}^d, f_i)\right)P(y_k^d = 1 |\vec{x}^d, f_k)\right)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} I[y^d = 1]\sum_{i=1}^{k-1}log\left(P(y_i^d = 1 |\vec{x}^d, f_i)\right) + log\left(P(y_k^d = 1 |\vec{x}^d, f_k)\right) \\+ I[y^d = 0]log\left( 1 - \prod_{i=1}^{k-1}\left(P(y_i^d = 1 |\vec{x}^d, f_i)\right)P(y_k^d = 1 |\vec{x}^d, f_k)\right)\\
\end{gather*}
\subsection{Recall case}
\begin{gather}
P(y^d| \{y^d_i\}_{1 \leq i \leq k}) = I\left[y^d = \bigvee_{i=1}^k y^d_i\right] = 
\begin{cases}
     1 ; y^d = 1 \Rightarrow \{y_i^d\}_{1 \leq i \leq k, \exists{ y_i^d\| y_i^d = 1 }}\\
     1; y^d = 0 \Rightarrow \{y_i^d = 0\}_{1 \leq i \leq k}\\
     0; otherwise
\end{cases}
\end{gather}
\begin{gather*}
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} log\left(I\left[y^d = \bigvee_{i=1}^k y^d_i \right] \prod_{i=1}^{k-1}\left(P(y_i^d |\vec{x}^d, f_i)\right)P(y_k^d |\vec{x}^d, f_k)\right)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} log\left(I[y^d = 0] \prod_{i=1}^{k-1}\left(P(y_i^d = 0 |\vec{x}^d, f_i)\right)P(y_k^d = 0 |\vec{x}^d, f_k) + I[y^d = 1] \sum_{\substack{\{y_i^d\}_{1 \leq i \leq k},\\ \exists{y_i^d\| y_i^d = 1}}} \prod_{i=1}^{k-1}\left(P(y_i^d |\vec{x}^d, f_i)\right)P(y_k^d |\vec{x}^d, f_k)\right)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} log\left(I[y^d = 0] \prod_{i=1}^{k-1}\left(P(y_i^d = 0 |\vec{x}^d, f_i)\right)P(y_k^d = 0 |\vec{x}^d, f_k) + I[y^d = 1]\left(1 - \prod_{i=1}^{k-1}\left(P(y_i^d = 0 |\vec{x}^d, f_i)\right)P(y_k^d = 0 |\vec{x}^d, f_k)\right)\right)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} I[y^d = 0]log\left( \prod_{i=1}^{k-1}\left(P(y_i^d = 0 |\vec{x}^d, f_i)\right)P(y_k^d = 0 |\vec{x}^d, f_k)\right) \\+ I[y^d = 1]log\left( 1 - \prod_{i=1}^{k-1}\left(P(y_i^d = 0 |\vec{x}^d, f_i)\right)P(y_k^d = 0 |\vec{x}^d, f_k)\right)\\
f_{k}^* = \operatorname*{arg\,max}_{f_k} \sum_{d \in D} I[y^d = 0]\sum_{i=1}^{k-1}log\left(P(y_i^d = 0 |\vec{x}^d, f_i)\right) + log\left(P(y_k^d = 0 |\vec{x}^d, f_k)\right) \\+ I[y^d = 1]log\left( 1 - \prod_{i=1}^{k-1}\left(P(y_i^d = 0 |\vec{x}^d, f_i)\right)P(y_k^d = 0 |\vec{x}^d, f_k)\right)\\
\end{gather*}
\end{document}

### 2014-01-31 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/derivations/Derivation.tex
added derivations in pdf and tex, plots in pdf and vsd

\documentclass[11pt,a4paper]{article}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{color}
\usepackage[colorlinks=true, linkcolor=blue]{hyperref}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{setspace}
\onehalfspacing

\begin{document}

\title{Probablistic Model for High Precision/Recall Feature Selection}
\author{Draft for ICML 2014}
\maketitle
\section{Introduction}
Feature selection is the selection of a subset of features $F^*$ from the complete feature space $F,$ for a specific classification/prediction problem, without loosing too much performance on some given measures. The benefit of feature selection include more explainable model, reduced computation time/power, and the avoidance of overfitting.

Existing feature selection algorithms, whose performance show no statistical difference on out benchmark, are mostly ad-hoc. They give various answers to optimisation, but none of them gives the question. In this project, we started from the first principles, proposed a graphical model, and built a new feature selection system upon it.

\section{Graphical Model}

To begin the derivation, we propose a graphical model of feature selection for binary classification problem, as shown in \hyperref[fig:model]{figure~\ref{fig:model}}. Double-circle nodes represent observed variables, including the data point vector $\vec{x}^{\,d},$ selected features $f_i^*$ (where $1\leq i\leq k,$ $f_i\in F$) and the supervised class label $y^d.$ Single-circle nodes represent latent variables, including a selected attribute of data point vector $f_i^x,$ and prediction from a feature $y^d_i.$

Since jointly optimising this objective is NP-hard, we will build $F^*$ in a greedy manner by choosing the next optimal feature $f^*_k$ given the previous set of optimal features $F^*_{k-1}$ and recursively defining $F^*_k = F^*_{k-1}\cup f^*_k$ with $F^*_0 = \emptyset$. The measure of the fitness of a model can either be Expectation or Likelihood.

\begin{figure}[htbp]
	\centering
	\includegraphics[scale=1]{Plots_1.pdf}
	\caption{Graphical model. Double-wall circle denotes observed nodes, single-wall circle denotes hidden nodes.}
	\label{fig:model}
\end{figure}

\section{Expectation}
The initial objective is defined as:
\[f_k^*=\operatorname*{arg\,max}_{f_k}E_D\left[P\left(y^d|\vec{x}^{\,d},F_k\right)\right]\]

\begin{align}
f_k^*&=\operatorname*{arg\,max}_{f_k}E_D\left[P\left(y^d|\vec{x}^{\,d},F_k\right)\right]\nonumber\\
&=\operatorname*{arg\,max}_{f_k}\frac{1}{|D|}\sum_{d\in D} P\left(y^d | \vec{x}^{\,d},F_k\right)\nonumber\\
&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\sum_{\{y_{i}^d\}_{1\leq i\leq k}}\frac{P\left(y^d,\vec{x}^{\,d},F_k,\{y_{i}^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
=\operatorname*{arg\,max}_{f_k}&\sum_{d \in D}\sum_{{\{y_{i}^d\}}_{1\leq i\leq k}}\frac{P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\left(\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d}, f_i\right)\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\sum_{\{y_i^d\}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\label{eq:expect}
\end{align}

Here, we rewrote the expectation of a binary event as its probability, factorized the conditional probability in the joint probability divided by the marginal, marginalised over $\{y^d_i\}_{1\leq i\leq k}$, factorized joint probability in conditional and prior following the graphical model and exploited d-separation to remove irrelevant conditions and to cancel terms in the equation.

Now we can optimise our initial objective aiming three goals of classification tasks: Precision, Recall, and General n-out-of-k.

\subsection{Precision}
In order to select the subset of features providing high precision binary classifier we need the agreement of all features predictors $y^d_i$ to predict true. That is, when $y^d$ is true we need all of the predictors $y^d_i$ equals to true, and if $y^d$ were false, just one of the predictors $y^d_i$ would have to be false. Then the probability $P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)$ can be expressed as follows:
\begin{equation}
P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)=I\left[y^d=\bigwedge_{i=1}^k y^d_i\right]=
\begin{cases}
	y^d=1 \text{ when } \{y_i^d=1\}_{1\leq i\leq k}\\
	y^d=0 \text{ when } \{y_i^d\}_{1\leq i\leq k,\exists{y_j^d\|y_j^d=0}}
\end{cases}\label{eq:expect_pre_1}
\end{equation}
Then, we combined equations \eqref{eq:expect} and \eqref{eq:expect_pre_1}, separated each term according to the actual label value $y^d$ and used the probability sum rule to rewire the second term as follows:
\begin{align}
f_k^*&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}I\left[y^d=\bigwedge_{i=1}^k y^d_i\right]\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\nonumber\\[0.5em]
&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}
\begin{cases}
	y^d=1: \prod_{i=1}^kP\left(y_i^d=1|\vec{x}^{\,d},f_i\right)\\
	y^d=0: \sum_{\substack{\{y_i^d\}_{1\leq i\leq k},\\ \exists{y_i^d\|y_i^d=0}}}\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)
\end{cases}\nonumber\\[0.5em]
&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}
\begin{cases}
	y^d=1: \prod_{i=1}^kP\left(y_i^d = 1|\vec{x}^{\,d},f_i\right)\\
	y^d=0: 1-\prod_{i=1}^kP\left(y_i^d = 1|\vec{x}^{\,d},f_i\right)
\end{cases}\label{eq:expect_pre_2}\\[0.5em]
&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}
\begin{cases}
	y^d=1: \prod_{i=1}^kP\left(y^d = 1|\vec{x}_i^{\,d},f_i\right)\\
	y^d=0: 1-\prod_{i=1}^kP\left(y^d = 1|\vec{x}_i^{\,d},f_i\right)\nonumber
\end{cases}
\end{align}
From \eqref{eq:expect_pre_2} we can intuitively describe how this equation is related to the precision metric. In the confusion matrix, Precision is calculated dividing the numbers of true positives by the number of all examples predicted as positive (true positives and false positives). When $y^d$ is true, \eqref{eq:expect_pre_2} gives higher score to feature that have higher probability to predict true, encouraging true positives. Meanwhile, if $y^d$ is false, \eqref{eq:expect_pre_2} gives lower score to features that have higher probability to predict true, penalising false positives.

\subsection{Recall case}
In order to select the subset of features providing high recall binary classifier we need at least one $y^d_i$ to predict true. Therefore, we need a disjunction operation between the predictors $y^d_i$. That is, when $y^d$ is true, we need at least one predictor $y^d_i$ to equals to true, and if $y^d$ were false, all of the predictors $y^d_i$ would have to be false. Then the probability $P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)$ can be expressed as follows:
\begin{equation}
P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)=I\left[y^d=\bigvee_{i=1}^k y^d_i\right]=
\begin{cases}
	y^d=1 \text{ when } \{y_i^d\}_{1\leq i\leq k,\exists{y_j^d\|y_j^d=1}}\\
	y^d=0 \text{ when } \{y_i^d=0\}_{1\leq i\leq k}
\end{cases}\label{eq:expect_recall_1}
\end{equation}
Here, we combined equations \eqref{eq:expect} and \eqref{eq:expect_recall_1}, separated each term according to the actual label value $y^d$ and used the probability sum rule to rewrite the second term as follows:
\begin{align}
f_k^*&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}I\left[y^d=\bigvee_{i=1}^k y^d_i\right]\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\nonumber\\[0.5em]
&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}
\begin{cases}
	y^d=0: \prod_{i=1}^kP\left(y_i^d=0|\vec{x}^{\,d},f_i\right)\\
	y^d=1: \sum_{\substack{\{y_i^d\}_{1\leq i\leq k},\\ \exists{y_i^d\|y_i^d=1}}}\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)
\end{cases}\nonumber\\[0.5em]
&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}
\begin{cases}
	y^d=0: \prod_{i=1}^kP\left(y_i^d=0|\vec{x}^{\,d},f_i\right)\\
	y^d=1: 1-\prod_{i=1}^kP\left(y_i^d=0|\vec{x}^{\,d},f_i\right)
\end{cases}\label{eq:expect_recall_2}\\
&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}
\begin{cases}
	y^d=0: \prod_{i=1}^kP\left(y^d=0|\vec{x}_i^{\,d},f_i\right)\\
	y^d=1: 1-\prod_{i=1}^kP\left(y^d=0|\vec{x}_i^{\,d},f_i\right)
\end{cases}\nonumber
\end{align}
From \eqref{eq:expect_recall_2} we can intuitively describe how this equation is related to the precision metric. In the confusion matrix, Recall is calculated dividing the numbers of actual true positives by the number of all true positives (true positives and false negatives). When $y^d$ is false, \eqref{eq:expect_recall_2} gives higher score to feature that have higher probability to predict false, encouraging true negatives. Meanwhile, if $y^d$ is true, \eqref{eq:expect_recall_2} gives lower score to features that have higher probability to predict false, penalizing false negatives.

\subsection{General n-out-of-k}
In order to balance Expectation and Recall, we use a voting notation. When $y^d$ is true, then at lease $n$ out of $k$ selected predictors $y_i^d$ are true. However, if $y^d$ is false, then the number of predictors $y_i^d$ that predict true is strictly less than $n.$ Then the probability $P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)$ can be expressed as follows:
\begin{gather}
P\left(y^d|\{y_i^d\}_{1\leq i\leq k}\right)=I\left[\,\sum_{i=1}^ky_i^d\geq n\right]\label{eq:expect_general_1}
\end{gather}
Here, we combined equations \eqref{eq:expect} and \eqref{eq:expect_general_1}, separated the result according to the prediction of $y_i^d$ and used the probability sum rule to rewrite the second term as follows:
\begin{align}
f_k^*&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\sum_{\{\vec{y}^{\,d}\|\sum_{i=1}^ky_i^d\geq n\}}\prod_{i=1}^kP\left(y_i^d|f_i,\vec{x}^{\,d}\right)\nonumber\\
&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\sum_{\{\vec{y}^{\,d}\|\sum_{i=1}^ky_i^d\geq n\}}P\left(y_1^d|f_1,\vec{x}^{\,d}\right)\prod_{i=2}^kP\left(y_i^d|f_i,\vec{x}^{\,d}\right)\nonumber\\
&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\left[P\left(y_1^d=1|f_1,\vec{x}^{\,d}\right)+P\left(y_1^d=0|f_1,\vec{x}^{\,d}\right)\right]\sum_{\{\vec{y}^{\,d}\|\sum_{i=1}^ky_i^d\geq n\}}\prod_{i=2}^kP\left(y_i^d|f_i,\vec{x}^{\,d}\right)\nonumber\\
&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\left[P\left(y_1^d=1|f_1,\vec{x}^{\,d}\right)\sum_{\{\vec{y}^{\,d}\|\sum_{i=2}^ky_i^d\geq n-1\}}\prod_{i=2}^kP\left(y_i^d|f_i,\vec{x}^{\,d}\right)\right.\nonumber\\ &\hspace{6em}\left.+P\left(y_1^d=0|f_1,\vec{x}^{\,d}\right)\sum_{\{\vec{y}^{\,d}\|\sum_{i=2}^ky_i^d\geq n\}}\prod_{i=2}^kP\left(y_i^d|f_i,\vec{x}^{\,d}\right)\right]\nonumber\\
&\approx\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\left[P\left(y^d=1|f_1,\vec{x}^{\,d}\right)\underbrace{\sum_{\{\vec{y}^{\,d}\|\sum_{i=2}^ky_i^d\geq n-1\}}\prod_{i=2}^kP\left(y_i^d|f_i,\vec{x}^{\,d}\right)}_{recursion}\right.\nonumber\\ &\hspace{6em}\left.+P\left(y^d=0|f_1,\vec{x}^{\,d}\right)\underbrace{\sum_{\{\vec{y}^{\,d}\|\sum_{i=2}^ky_i^d\geq n\}}\prod_{i=2}^kP\left(y_i^d|f_i,\vec{x}^{\,d}\right)}_{recursion}\right]\label{eq:expect_general_2}
\end{align}
In \eqref{eq:expect_general_2}, the result is recursively defined. This recursion can be turned into dynamic programming, as shown in \hyperref[fig:dp]{figure~\ref{fig:dp}}, reducing time complexity from $O\left(2^k\right)$ to $O\left(nk\right).$

\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.8]{Plots_5.pdf}
	\caption{Dynamic programming table to turn the recursion in \eqref{eq:expect_general_2} to dynamic programming.}
	\label{fig:dp}
\end{figure}

\section{Likelihood}
\begin{align}
f_k^*&\equiv\operatorname*{arg\,max}_{f_k}\,log\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}log\left(\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\right)\nonumber\\
&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}log\sum_{\{y_i^d\}_{1\leq i\leq k}}\frac{P\left(y^d,\vec{x}^{\,d}, F_k,\{y_i^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
&=\operatorname*{arg\,max}_{f_k} \sum_{d \in D} log\sum_{{\{y_i^d\}}_{1\leq i \leq k}} \frac{P\left(y^d| \{y^d_i\}_{1 \leq i \leq k}\right) \prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d}, F_k\right)}\nonumber\\
&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\nonumber
\end{align}
Here, we rewrote the likelihood of a binary event as its probability, factorized the conditional probability in the joint probability divided by the marginal, marginalized over $\{y^d_i\}_{1\leq i\leq k}$, factorized joint probability in conditional and prior following the graphical model and exploited d-separation to remove irrelevant conditions and to cancel terms in the equation.

Since $\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)$ is exactly the same as the result in the expectation case, and the logarithm is a monotonous function, the choice of likelihood instead of expectation has no further affect on the algorithm.
\end{document}

### 2014-01-31 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/Wtihout_NOutOfK/generateGraphs.m
Results

@@ -1,0 +1,57 @@
+%script to generate graphs
+%todo: specify the labels for each algoritghm, it follows the order in
+%wich the algorithms appears in the xml
+
+%clear 
+clear all, close all;
+
+data = xml2struct('featureSelection.xml');
+
+%config legends and plot colors => TODO
+%legendKeys = data.simulation.Attributes.algs;
+%legendDef = containers.Map(legendKeys, {'',''});
+
+%loop over Data Sets
+nDS = size(data.Simulation.DataSet,2);
+for d=1:nDS
+    dSName = cleanString(data.Simulation.DataSet{d}.Attributes.name);
+    dSNumFea = str2double(data.Simulation.DataSet{d}.Attributes.nfeatures);
+    
+    %loop over classifiers
+    nCl = size(data.Simulation.DataSet{d}.Classifier,2);
+    for c = 1:nCl
+        CName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Attributes.name);
+        
+        %loop over metrics
+        nM = size(data.Simulation.DataSet{d}.Classifier{c}.Metric,2);
+        for m = 1:nM
+            MName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Attributes.name);
+            nAlg = size(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm,2);
+                               
+            %plot each graph
+            figure, hold on;
+            
+            %TODO: define symbols 
+            plotSymbols = {'-g<','-mv','-mo','-m^','-gs','-bp','-bd','-rp','-g>','-mx','-rd','-mh'};
+            legendKeys = {}; 
+            for alg = 1:nAlg
+                mean = str2num(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Mean.Text);
+                algname = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name);
+                legendKeys = [legendKeys, algname];
+                plot(1:dSNumFea, mean, plotSymbols{alg})
+                
+                
+            end;
+            
+            %plot settings
+            title(cleanString(strjoin({dSName, CName, MName},' ')));
+            xlabel('Number of features');
+            ylabel(MName);
+            legend(legendKeys,'Location', 'SouthOutside');
+            %axis([1 dSNumFea 0 1])
[…]

### 2014-01-31  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/abstract.tex
Abstract update

Feature selection is important in many practical classification
settings to address computational constraints or to prevent
overfitting when the data may be high-dimensional but contain
relatively few samples.  While a wide variety of feature selection
methods have been proposed in the literature, little research seems to
focus on feature selection specifically targeted for precision or
recall.  In this paper we propose a novel probabilistic model of
feature selection and argue that MAP inference w.r.t. to two extreme
objectives in this model respectively yield high precision and high
recall feature selection.  From each objective, we then derive an
efficient formula for feature selection in the filtering framework
(i.e., greedy forward selection) and we empirically compare the
resulting feature selection criteria to a wide variety of existing
methods.  Results show that our high precision and high recall feature
selection approaches improve their intended objectives and more
reliably than existing methods whose precision and recall performance
may vary widely across datasets and classifiers.

%Furthermore, our modeling framework provides us with a way to
%interpret existing feature selection methods and suggests that the
%use of greedy approaches (such as mutual information) appear to
%maximize precision while diversity-based approaches (such as MRMR)
%appear to maximize recall, hence providing us with a framework for
%reinterpreting the loss functions implicitly targeted by existing
%feature selection methods.

% could look at class balance
% what other feature properties?

% may want to mention why P/R important... depends on what is
% important (more costly for false positives or false negatives)
% and accuracy easy to optimize in imbalanced cases

### 2014-01-31  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/intro.tex
Abstract update

\section{Introduction}

Feature selection~\cite{guyon_jmlr03}

While historically, feature selection

\COMMENT
- Feature selection motivations
** too little data (e.g., bioinformatics, or text with few labels)
** features costly to evaluate
** explainability
** minimize feature elicitation for future data collection (questionnaires, medical tests -- blood tests)
** computation / Big Data
** mobile devices (RAM, computation)
** linear speed (LibLinear 1000x faster than LibSVM)
** poly kernels without kernelized approach without loss of evaluation efficiency
** need to argue SVM/logistic L1 not always best... not always logistic regression/SVM problem, also eval efficient, but training not, so 
inefficient for large-scale or resource-constrained training... show empirical better than L1, also more control over amount of feature 
selection (need a tool that implements full regularization path -- constrains optimization method)

Filtering-based feature selection methods ...

"A Probabilistic Model for High Precision and Recall Feature Selection"
"A Probabilistic Model/Perspective of Feature Selection for Trading off Precision and Recall"
Conventional feature selection methods choose informative features or feature sets and empirically lead to good accuracy improvements, but 
few focus directly on precision or recall (or mention that they're method is actually biased towards one vs. other).  In this paper we 
propose a new probabilistic classification model based on a logical or weighted voting approach that directly encourages feature selection 
according to the continuum between pure precision and pure recall.  Supports filter, wrapper, and embedded approaches (where we create a 
new high precision/recall variant of Naive Bayes).  Suggests a way of analyzing existing approaches and identifying what they are 
optimizing.  In fact, MI (or other independent greedy methods) appear to be maximizing precision while MRMR appears to maximizing recall.
- Idea: we have a generative model... write down how we want features to generate the class... now the only leverage we have is to select 
features to maximize expected (log) likelihood
** if we use an aggregation function that allows any feature to falsify (noisy-and), we encourage agreement (precision)
** if we use an aggregation function that allows any feature to tip the vote to true (noisy-or), we encourage coverage (recall)... noisy-
max not multiclass unless we're ordinal (I think)
** we can trade off precision and recall by requiring n-out-of-k features, n=k/2 is majority vote... does this correspond to F-score or 
accuracy (can we compare beta & k, 3d plot showing F_beta for k?)
** of course probabilistic since class predictions are latent so we get a soft version (noisy-or, noisy-and) ... clearer derivation of 
noisy-or, noisy-max etc. than direct specification?  I think so.
** maximizing overall likelihood so will try to get features that correctly classify more of the data (especially where votes of others are 
weak)
** can do a probabilistic analysis of the 4x4 contigency table
** a new naive classifier, how do we do overall as a naive classifier?  accuracy will tell us this, can tune k though for whatever metric 
we care about!  interesting as a classifier since we look at total probability mass of at least k votes... what does this buy us over 
standard naive Bayes?  Should evaluate.
==> is there a way to do DP for dynamic programming for Bayesian model averaging over all class inclusions/exclusions?
... for each feature can leave in or leave out -- if leave out get 1, otherwise probability (sum over all models, probability of prediction 
* normalized likelihood of that model vs. all others -- add in feature one at a time?)
... would this also work for query expansion?  some sort of DP MAP query for jointly most useful retrieval set?
** online learning... discrete parameter
** spectrum/contiuum of tradeoffs for feature selection
- To explore: correlated features, diversity of features (MRMR) -- good for recall
- Filter method
- Wrapper method
- Embedded method - use a naive independence classifier
  (do we unify view for embedded method?  we could maximize likelihood for voting classifier	
- Computational tricks worth noting (extreme cases and 1- trick for probabilities, DP)
- In general we want to optimize precision/recall tradeoff (extreme solutions are trivial), n-out-of-k interpolates F-score... really?  Can 
we show a strong mathematical connection?
- Intepretation as a voting classifier... then majority vote is k/2-call@k
** precision, recall, what is f-score?  pure precision/recall not ideal
** reinterpretation of existing methods as focusing more on precision (MI) or recall (MRMR)
** does trade-off between precision and recall yield an F-Beta score
** should probably write out a direct classification approach with y being I[y = y_1 v ... v y_k] and then maximize E[p(y*|...)] or 
likelihood.  This model supports all view in the proposed paper.  Which is better?
** will get the effect that optimization only matters when new feature can swing the vote... for recall this will be false negatives, for 
recall this will be false positives, for majority vote, it will be borderline cases.
** recall encourages diversity... explains why diverse feature selection methods don't always improve accuracy.  If we wanted precision, we 
don't mind redundancy, in fact we encourage it.
** start with and, or, generalize to weighted voting scheme
** an information-theoretic intepretation?  expectation over data of log probability should yield this
** what sort of similarity metrics do we get?
** need to motivate directly that the logical/voting function encourages precision vs. recall... that with disjunction, new features will 
only address correcting false negatives and likewise for precision and conjunction and correcting false positives
** what sort of features do we select... analyze 2 newsgroups
***
- A new naive independence voting-based classifier with tunable objective and objective-oriented feature selection via a voting scheme
- A new naive independence voting-based classifier for the precision/recall trade-off
** feature selection for cases other than accuracy!
** efficient, supports different objectives from precision to recall and in-between (F-score?)... is the objective just for feature 
selection?
** directly supports feature selection... important in independent classifiers
** supports online computation... and online feature selection scoring
** supports discrete and Gaussian models
*** we could also modify the model to make the logical function (weighted voting explicit)... can marginalize this out... in this way the 
prediction matches feature selection
** learning parameters -- for directed model, as usual
** how to work out argmax_y* P(y*|...) -- looks like its just going to multiply probabilities for each class -- is this another view of 
Naive bayes
** how to work out feature selection -- y* observed...
*** could choose fb to maximize logical function in expectation... expected correctness?
*** could choose fb to maximize likelihood -- would be log version of above with logical function for hidden variable
*** after doing extreme cases, allow general voting, not just all-or-none

*** training recall/precision directly a bad idea... hurts accuracy, but can select features so as to focus on one of these
*** we focus on the filter method in this work
\ENDCOMMENT

### 2014-02-02 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/Wtihout_NOutOfK/generateGraphs.m

@@ -1,57 +1,0 @@
-%script to generate graphs
-%todo: specify the labels for each algoritghm, it follows the order in
-%wich the algorithms appears in the xml
-
-%clear 
-clear all, close all;
-
-data = xml2struct('featureSelection.xml');
-
-%config legends and plot colors => TODO
-%legendKeys = data.simulation.Attributes.algs;
-%legendDef = containers.Map(legendKeys, {'',''});
-
-%loop over Data Sets
-nDS = size(data.Simulation.DataSet,2);
-for d=1:nDS
-    dSName = cleanString(data.Simulation.DataSet{d}.Attributes.name);
-    dSNumFea = str2double(data.Simulation.DataSet{d}.Attributes.nfeatures);
-    
-    %loop over classifiers
-    nCl = size(data.Simulation.DataSet{d}.Classifier,2);
-    for c = 1:nCl
-        CName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Attributes.name);
-        
-        %loop over metrics
-        nM = size(data.Simulation.DataSet{d}.Classifier{c}.Metric,2);
-        for m = 1:nM
-            MName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Attributes.name);
-            nAlg = size(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm,2);
-                               
-            %plot each graph
-            figure, hold on;
-            
-            %TODO: define symbols 
-            plotSymbols = {'-g<','-mv','-mo','-m^','-gs','-bp','-bd','-rp','-g>','-mx','-rd','-mh'};
-            legendKeys = {}; 
-            for alg = 1:nAlg
-                mean = str2num(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Mean.Text);
-                algname = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name);
-                legendKeys = [legendKeys, algname];
-                plot(1:dSNumFea, mean, plotSymbols{alg})
-                
-                
-            end;
-            
-            %plot settings
-            title(cleanString(strjoin({dSName, CName, MName},' ')));
-            xlabel('Number of features');
-            ylabel(MName);
-            legend(legendKeys,'Location', 'SouthOutside');
-            %axis([1 dSNumFea 0 1])
[…]

### 2014-02-02  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BarGraphs/FeatureSelectionXClassifier/GenerateBarGraph.m

@@ -1,0 +1,76 @@
+%script to generate barGraph, major = feature selection, minor = classifier
+
+%clear
+clear all, close all;
+
+%xml file
+file = 'featureSelection.xml';
+
+%read the xml to struct
+data = xml2struct(file);
+
+%number of data sets
+nDS = size(data.Simulation.DataSet,2);
+for d=1:nDS
+    dSName = data.Simulation.DataSet{d}.Attributes.name;
+    
+    %loop over metrics
+    nM = size(data.Simulation.DataSet{d}.Classifier{1}.Metric,2);
+    for m = 1:nM
+        MName = data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Attributes.name;
+        nCl = size(data.Simulation.DataSet{d}.Classifier,2);
+        nAlg = size(data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Algorithms.Algorithm,2);
+        Y = zeros(nAlg,nCl);
+        Error = zeros(nAlg,nCl);
+        
+        algLegend = {};
+        for alg = 1:nAlg
+            algname = data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name;
+            algLegend = [algLegend, cleanString(algname)];
+            classifiersLegends = {};
+            %loop over classifiers
+            nCl = size(data.Simulation.DataSet{1}.Classifier,2);
+            for c = 1:nCl
+                CName = data.Simulation.DataSet{1}.Classifier{c}.Attributes.name;
+                classifiersLegends = [classifiersLegends, cleanString(CName)];
+                
+                %xpath expression
+                exp = strcat('//DataSet[@name="',dSName ,'"]/Classifier[@name="',CName,'"]/Metric[@name="',MName,'"]/Algorithms/Algorithm[@name="',algname,'"]/Mean');
+                nodeList = queryXml(exp,file);
+                
+                % Iterate through the nodes that are returned. but it is just
+                % one node in each interation
+                acc = 0.0;
+                count = 0;
+                samples = [];
+                for i = 1:nodeList.getLength
+                    node = nodeList.item(i-1);
+                    %convert text matrix to number matrix
+                    values = str2num( node.getFirstChild.getNodeValue);
+                    samples = [samples, values];
+                    acc = acc + sum(values);
+                    count = count + length(values);
[…]

### 2014-02-02  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BoxPlot/acronym.m

@@ -1,0 +1,6 @@
+function output = acronym( input )
+  words_cell = textscan(input,'%s','delimiter',' ');
+  words      = words_cell{ : };
+  letters    = cellfun(@(x) textscan(x,'%c%*s'), words);
+  output     = upper(letters');
+end

### 2014-02-02  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/LineGraphs/FullResults/generateGraphs.m

@@ -1,0 +1,57 @@
+%script to generate graphs
+%todo: specify the labels for each algoritghm, it follows the order in
+%wich the algorithms appears in the xml
+
+%clear 
+clear all, close all;
+
+data = xml2struct('featureSelection.xml');
+
+%config legends and plot colors => TODO
+%legendKeys = data.simulation.Attributes.algs;
+%legendDef = containers.Map(legendKeys, {'',''});
+
+%loop over Data Sets
+nDS = size(data.Simulation.DataSet,2);
+for d=1:nDS
+    dSName = cleanString(data.Simulation.DataSet{d}.Attributes.name);
+    dSNumFea = str2double(data.Simulation.DataSet{d}.Attributes.nfeatures);
+    
+    %loop over classifiers
+    nCl = size(data.Simulation.DataSet{d}.Classifier,2);
+    for c = 1:nCl
+        CName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Attributes.name);
+        
+        %loop over metrics
+        nM = size(data.Simulation.DataSet{d}.Classifier{c}.Metric,2);
+        for m = 1:nM
+            MName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Attributes.name);
+            nAlg = size(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm,2);
+                               
+            %plot each graph
+            figure, hold on;
+            
+            %TODO: define symbols 
+            plotSymbols = {'-g<','-mv','-mo','-m^','-gs','-bp','-bd','-rp','-g>','-mx','-rd','-mh','-kd','-kp'};
+            legendKeys = {}; 
+            for alg = 1:nAlg
+                mean = str2num(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Mean.Text);
+                algname = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name);
+                legendKeys = [legendKeys, algname];
+                plot(1:dSNumFea, mean, plotSymbols{alg})
+                
+                
+            end;
+            
+            %plot settings
+            title(cleanString(strjoin({dSName, CName, MName},' ')));
+            xlabel('Number of features');
+            ylabel(MName);
+            legend(legendKeys,'Location', 'SouthOutside');
[…]

### 2014-02-02 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BarGraphs/FeatureSelectionXClassifier/barweb.m

@@ -1,0 +1,195 @@
+function handles = barweb(barvalues, errors, width, groupnames, bw_title, bw_xlabel, bw_ylabel, bw_colormap, gridstatus, bw_legend, error_sides, legend_type)
+
+%
+% Usage: handles = barweb(barvalues, errors, width, groupnames, bw_title, bw_xlabel, bw_ylabel, bw_colormap, gridstatus, bw_legend, error_sides, legend_type)
+%
+% Ex: handles = barweb(my_barvalues, my_errors, [], [], [], [], [], bone, [], bw_legend, 1, 'axis')
+%
+% barweb is the m-by-n matrix of barvalues to be plotted.
+% barweb calls the MATLAB bar function and plots m groups of n bars using the width and bw_colormap parameters.
+% If you want all the bars to be the same color, then set bw_colormap equal to the RBG matrix value ie. (bw_colormap = [1 0 0] for all red bars)
+% barweb then calls the MATLAB errorbar function to draw barvalues with error bars of length error.
+% groupnames is an m-length cellstr vector of groupnames (i.e. groupnames = {'group 1'; 'group 2'}).  For no groupnames, enter [] or {}
+% The errors matrix is of the same form of the barvalues matrix, namely m group of n errors.
+% Gridstatus is either 'x','xy', 'y', or 'none' for no grid.
+% No legend will be shown if the legend paramter is not provided
+% 'error_sides = 2' plots +/- std while 'error_sides = 1' plots just + std
+% legend_type = 'axis' produces the legend along the x-axis while legend_type = 'plot' produces the standard legend.  See figure for more details
+%
+% The following default values are used if parameters are left out or skipped by using [].
+% width = 1 (0 < width < 1; widths greater than 1 will produce overlapping bars)
+% groupnames = '1', '2', ... number_of_groups
+% bw_title, bw_xlabel, bw_ylabel = []
+% bw_color_map = jet
+% gridstatus = 'none'
+% bw_legend = []
+% error_sides = 2;
+% legend_type = 'plot';
+%
[…]

### 2014-02-02 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BoxPlot/createBoxPlot.m

@@ -1,0 +1,23 @@
+function createBoxPlot(ymatrix1, boxLengends, titleName, ylabelTxt, xlabelTxt )
+%CREATEFIGURE(YMATRIX1)
+%  YMATRIX1:  bar matrix data
+
+%  Auto-generated by MATLAB on 31-Jan-2014 14:50:05
+
+for i=1:length(boxLengends)
+    boxLengends{i} = strjoin(acronym(boxLengends{i}),'.');
+end;
+
+% Create multiple lines using matrix input to bar
+figure, boxplot(ymatrix1,boxLengends)
+
+
+% Create title
+title(titleName);
+
+% Create xlabel
+xlabel(xlabelTxt);
+
+% Create ylabel
+ylabel(ylabelTxt);
+

### 2014-02-02 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/LineGraphs/FullResultsWithoutNoutOfK/generateGraphs.m

@@ -1,0 +1,57 @@
+%script to generate graphs
+%todo: specify the labels for each algoritghm, it follows the order in
+%wich the algorithms appears in the xml
+
+%clear 
+clear all, close all;
+
+data = xml2struct('featureSelection.xml');
+
+%config legends and plot colors => TODO
+%legendKeys = data.simulation.Attributes.algs;
+%legendDef = containers.Map(legendKeys, {'',''});
+
+%loop over Data Sets
+nDS = size(data.Simulation.DataSet,2);
+for d=1:nDS
+    dSName = cleanString(data.Simulation.DataSet{d}.Attributes.name);
+    dSNumFea = str2double(data.Simulation.DataSet{d}.Attributes.nfeatures);
+    
+    %loop over classifiers
+    nCl = size(data.Simulation.DataSet{d}.Classifier,2);
+    for c = 1:nCl
+        CName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Attributes.name);
+        
+        %loop over metrics
+        nM = size(data.Simulation.DataSet{d}.Classifier{c}.Metric,2);
+        for m = 1:nM
+            MName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Attributes.name);
+            nAlg = size(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm,2);
+                               
+            %plot each graph
+            figure, hold on;
+            
+            %TODO: define symbols 
+            plotSymbols = {'-g<','-mv','-mo','-m^','-gs','-g>','-mx','-mh','-bp','-bd','-rp','-rd'};
+            legendKeys = {}; 
+            for alg = 1:nAlg
+                mean = str2num(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Mean.Text);
+                algname = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name);
+                legendKeys = [legendKeys, algname];
+                plot(1:dSNumFea, mean, plotSymbols{alg})
+                
+                
+            end;
+            
+            %plot settings
+            title(cleanString(strjoin({dSName, CName, MName},' ')));
+            xlabel('Number of features');
+            ylabel(MName);
+            legend(legendKeys,'Location', 'SouthOutside');
+            %axis([1 dSNumFea 0 1])
[…]

### 2014-02-03 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/intro.tex
AAAI format, merged derivation writeup from Libo

--- 2014-01-31  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/intro.tex
@@
 \COMMENT
+key insight: literature suggests redundancy is bad idea, but in fact, it is critical for precision (implies agreement)
+
+how to strongly justify the model and objectives we use?  voting?
+
+Good discussion: http://jmlr.org/papers/volume13/brown12a/brown12a.pdf
+
 - Feature selection motivations

### 2014-02-03 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/model.tex
AAAI format, merged derivation writeup from Libo

--- 2014-01-31 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/derivations/Derivation.tex
@@
-\documentclass[11pt,a4paper]{article}
-\usepackage{amsmath}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{color}
-\usepackage[colorlinks=true, linkcolor=blue]{hyperref}
-\usepackage{fullpage}
-\usepackage{graphicx}
-\usepackage{setspace}
-\onehalfspacing
+\section{A Probabilistic Model of Feature Selection}
 
-\begin{document}
-
-\title{Probablistic Model for High Precision/Recall Feature Selection}
-\author{Draft for ICML 2014}
-\maketitle
-\section{Introduction}
 Feature selection is the selection of a subset of features $F^*$ from the complete feature space $F,$ for a specific classification/prediction problem, without loosing too much performance on some given measures.
@@
 
-\section{Graphical Model}
+\subsection{Graphical Model}
 
-To begin the derivation, we propose a graphical model of feature selection for binary classification problem, as shown in \hyperref[fig:model]{figure~\ref{fig:model}}.
+To begin the derivation, we propose a graphical model of feature selection for binary classification problem, as shown in figure~\ref{fig:model}.
 Double-circle nodes represent observed variables, including the data point vector $\vec{x}^{\,d},$ selected features $f_i^*$ (where $1\leq i\leq k,$ $f_i\in F$) and the supervised class label $y^d.$ Single-circle nodes represent latent variables, including a selected attribute of data point vector $f_i^x,$ and prediction from a feature $y^d_i.$
@@
 
-\begin{figure}[htbp]
+\begin{figure}[tbp!]
 	\centering
-	\includegraphics[scale=1]{Plots_1.pdf}
+	\includegraphics[scale=0.9]{Plots_1.pdf}
 	\caption{Graphical model. Double-wall circle denotes observed nodes, single-wall circle denotes hidden nodes.}
@@
 The initial objective is defined as:
-\[f_k^*=\operatorname*{arg\,max}_{f_k}E_D\left[P\left(y^d|\vec{x}^{\,d},F_k\right)\right]\]
+\[f_k^*=\argmax_{f_k}E_D\left[P\left(y^d|\vec{x}^{\,d},F_k\right)\right]\]
 
 \begin{align}
-f_k^*&=\operatorname*{arg\,max}_{f_k}E_D\left[P\left(y^d|\vec{x}^{\,d},F_k\right)\right]\nonumber\\
-&=\operatorname*{arg\,max}_{f_k}\frac{1}{|D|}\sum_{d\in D} P\left(y^d | \vec{x}^{\,d},F_k\right)\nonumber\\
-&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
-&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\sum_{\{y_{i}^d\}_{1\leq i\leq k}}\frac{P\left(y^d,\vec{x}^{\,d},F_k,\{y_{i}^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
-=\operatorname*{arg\,max}_{f_k}&\sum_{d \in D}\sum_{{\{y_{i}^d\}}_{1\leq i\leq k}}\frac{P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\left(\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d}, f_i\right)\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
-&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\sum_{\{y_i^d\}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\label{eq:expect}
+f_k^*&=\argmax_{f_k}E_D\left[P\left(y^d|\vec{x}^{\,d},F_k\right)\right]\nonumber\\
+&=\argmax_{f_k}\frac{1}{|D|}\sum_{d\in D} P\left(y^d | \vec{x}^{\,d},F_k\right)\nonumber\\
+&=\argmax_{f_k}\sum_{d\in D}\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
+&=\argmax_{f_k}\sum_{d\in D}\sum_{\{y_{i}^d\}_{1\leq i\leq k}}\frac{P\left(y^d,\vec{x}^{\,d},F_k,\{y_{i}^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
+=\argmax_{f_k}&\sum_{d \in D}\sum_{{\{y_{i}^d\}}_{1\leq i\leq k}}\frac{P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\left(\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d}, f_i\right)\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
+&=\argmax_{f_k}\sum_{d\in D}\sum_{\{y_i^d\}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\label{eq:expect}
 \end{align}
@@
 \begin{align}
-f_k^*&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}I\left[y^d=\bigwedge_{i=1}^k y^d_i\right]\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\nonumber\\[0.5em]
-&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}
+f_k^*&=\argmax_{f_k}\sum_{d\in D}I\left[y^d=\bigwedge_{i=1}^k y^d_i\right]\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\nonumber\\[0.5em]
+&=\argmax_{f_k}\sum_{d\in D}
 \begin{cases}
@@
 \end{cases}\nonumber\\[0.5em]
-&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}
+&=\argmax_{f_k}\sum_{d\in D}
 \begin{cases}
@@
 \end{cases}\label{eq:expect_pre_2}\\[0.5em]
-&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}
+&=\argmax_{f_k}\sum_{d\in D}
 \begin{cases}
@@
 \begin{align}
-f_k^*&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}I\left[y^d=\bigvee_{i=1}^k y^d_i\right]\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\nonumber\\[0.5em]
-&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}
+f_k^*&=\argmax_{f_k}\sum_{d\in D}I\left[y^d=\bigvee_{i=1}^k y^d_i\right]\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\nonumber\\[0.5em]
+&=\argmax_{f_k}\sum_{d\in D}
 \begin{cases}
@@
 \end{cases}\label{eq:expect_recall_2}\\
-&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}
+&=\argmax_{f_k}\sum_{d\in D}
 \begin{cases}
@@
 
-\subsection{General n-out-of-k}
-In order to balance Expectation and Recall, we use a voting notation.
-When $y^d$ is true, then at lease $n$ out of $k$ selected predictors $y_i^d$ are true.
-However, if $y^d$ is false, then the number of predictors $y_i^d$ that predict true is strictly less than $n.$ Then the probability $P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)$ can be expressed as follows:
-\begin{gather}
-P\left(y^d|\{y_i^d\}_{1\leq i\leq k}\right)=I\left[\,\sum_{i=1}^ky_i^d\geq n\right]\label{eq:expect_general_1}
-\end{gather}
-Here, we combined equations \eqref{eq:expect} and \eqref{eq:expect_general_1}, separated the result according to the prediction of $y_i^d$ and used the probability sum rule to rewrite the second term as follows:
+\subsection{Likelihood}
 \begin{align}
-f_k^*&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\sum_{\{\vec{y}^{\,d}\|\sum_{i=1}^ky_i^d\geq n\}}\prod_{i=1}^kP\left(y_i^d|f_i,\vec{x}^{\,d}\right)\nonumber\\
-&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\sum_{\{\vec{y}^{\,d}\|\sum_{i=1}^ky_i^d\geq n\}}P\left(y_1^d|f_1,\vec{x}^{\,d}\right)\prod_{i=2}^kP\left(y_i^d|f_i,\vec{x}^{\,d}\right)\nonumber\\
-&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\left[P\left(y_1^d=1|f_1,\vec{x}^{\,d}\right)+P\left(y_1^d=0|f_1,\vec{x}^{\,d}\right)\right]\sum_{\{\vec{y}^{\,d}\|\sum_{i=1}^ky_i^d\geq n\}}\prod_{i=2}^kP\left(y_i^d|f_i,\vec{x}^{\,d}\right)\nonumber\\
-&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\left[P\left(y_1^d=1|f_1,\vec{x}^{\,d}\right)\sum_{\{\vec{y}^{\,d}\|\sum_{i=2}^ky_i^d\geq n-1\}}\prod_{i=2}^kP\left(y_i^d|f_i,\vec{x}^{\,d}\right)\right.\nonumber\\ &\hspace{6em}\left.+P\left(y_1^d=0|f_1,\vec{x}^{\,d}\right)\sum_{\{\vec{y}^{\,d}\|\sum_{i=2}^ky_i^d\geq n\}}\prod_{i=2}^kP\left(y_i^d|f_i,\vec{x}^{\,d}\right)\right]\nonumber\\
-&\approx\operatorname*{arg\,max}_{f_k}\sum_{d\in D}\left[P\left(y^d=1|f_1,\vec{x}^{\,d}\right)\underbrace{\sum_{\{\vec{y}^{\,d}\|\sum_{i=2}^ky_i^d\geq n-1\}}\prod_{i=2}^kP\left(y_i^d|f_i,\vec{x}^{\,d}\right)}_{recursion}\right.\nonumber\\ &\hspace{6em}\left.+P\left(y^d=0|f_1,\vec{x}^{\,d}\right)\underbrace{\sum_{\{\vec{y}^{\,d}\|\sum_{i=2}^ky_i^d\geq n\}}\prod_{i=2}^kP\left(y_i^d|f_i,\vec{x}^{\,d}\right)}_{recursion}\right]\label{eq:expect_general_2}
-\end{align}
-In \eqref{eq:expect_general_2}, the result is recursively defined.
-This recursion can be turned into dynamic programming, as shown in \hyperref[fig:dp]{figure~\ref{fig:dp}}, reducing time complexity from $O\left(2^k\right)$ to $O\left(nk\right).$
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[scale=0.8]{Plots_5.pdf}
-	\caption{Dynamic programming table to turn the recursion in \eqref{eq:expect_general_2} to dynamic programming.}
-	\label{fig:dp}
-\end{figure}
-
-\section{Likelihood}
-\begin{align}
-f_k^*&\equiv\operatorname*{arg\,max}_{f_k}\,log\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
-&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}log\left(\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\right)\nonumber\\
-&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}log\sum_{\{y_i^d\}_{1\leq i\leq k}}\frac{P\left(y^d,\vec{x}^{\,d}, F_k,\{y_i^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
-&=\operatorname*{arg\,max}_{f_k} \sum_{d \in D} log\sum_{{\{y_i^d\}}_{1\leq i \leq k}} \frac{P\left(y^d| \{y^d_i\}_{1 \leq i \leq k}\right) \prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d}, F_k\right)}\nonumber\\
-&=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\nonumber
+f_k^*&\equiv\argmax_{f_k}\,log\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
+&=\argmax_{f_k}\sum_{d\in D}log\left(\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\right)\nonumber\\
+&=\argmax_{f_k}\sum_{d\in D}log\sum_{\{y_i^d\}_{1\leq i\leq k}}\frac{P\left(y^d,\vec{x}^{\,d}, F_k,\{y_i^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
+&=\argmax_{f_k} \sum_{d \in D} log\sum_{{\{y_i^d\}}_{1\leq i \leq k}} \frac{P\left(y^d| \{y^d_i\}_{1 \leq i \leq k}\right) \prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d}, F_k\right)}\nonumber\\
+&=\argmax_{f_k}\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\nonumber
 \end{align}
@@
 Since $\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)$ is exactly the same as the result in the expectation case, and the logarithm is a monotonous function, the choice of likelihood instead of expectation has no further affect on the algorithm.
-\end{document}

### 2014-02-03  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex

\section{Empirical}
In this section, we conduct experiments to study the feature selection performances of several well known methods such as Symmetrical Uncertainty Rank, Gain Ratio Rank, Information Gain Rank, Correlation Based Rank, Conditional Entropy Rank \cite{guyon_jmlr03}, Correlation-based Feature Subset Selection \cite{Hall1998},  Reliff \cite{Robnik-Sikonja2003} , mRMR \cite{peng2005} and our proposed methods: High Precision Expectation, High Precision Log likelihood, High Recall Expectation and High Recall Log likelihood. The first six methods are variable rank methods and the last six are subset rank methods.

In these experimental study, we evaluated each feature selection method in binary classification problems such as Breast Cancer, Pima Diabetes, Heart Statlog, Spect and Vote. These data sets can be downloaded from UCI machine learning repository \cite{Bache+Lichman:2013}. In addition, we used three different classifiers to solve each of the binary classifier problem. Logistic Regression, SVM Linear and Naive Bayes were used in the experiments and the first two are implemented in LibLinear library \cite{REF08a} and the last one is implemented in Weka software \cite{weka}.

To evaluate the feature selection performances we reported classification metrics performing 10-fold cross-validation from one until the max number of features selected for each classifier solving each of the binary classification problem. Specifically, we reported Accuracy, Precision, Recall and F-Score for the true label class, that could be identified by the context of the problem and usually be the class with least samples in the data set.

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BarGraphs/FeatureSelectionXClassifier/acronym.m

@@ -1,6 +1,0 @@
-function output = acronym( input )
-  words_cell = textscan(input,'%s','delimiter',' ');
-  words      = words_cell{ : };
-  letters    = cellfun(@(x) textscan(x,'%c%*s'), words);
-  output     = upper(letters');
-end

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BarGraphs/dataSetXFeatureSelection/GenerateBarGraph.m

@@ -1,73 +1,0 @@
-%script to generate barGraph
-
-%clear 
-clear all, close all;
-
-%xml file
-file = 'featureSelection.xml';
-
-%read the xml to struct
-data = xml2struct(file);
-
-%number of data sets
-nDS = size(data.Simulation.DataSet,2);
-
-%number of algs
-nAlg = size(data.Simulation.DataSet{1}.Classifier{1}.Metric{1}.Algorithms.Algorithm,2);
-
-%loop over classifiers
-nCl = size(data.Simulation.DataSet{1}.Classifier,2);
-for c = 1:nCl
-     CName = data.Simulation.DataSet{1}.Classifier{c}.Attributes.name;
-     
-    %loop over metrics
-    nM = size(data.Simulation.DataSet{1}.Classifier{c}.Metric,2);
-    for m = 1:nM
-      MName = data.Simulation.DataSet{1}.Classifier{c}.Metric{m}.Attributes.name;
-      
-      %compute average and plot
-      Y = zeros(nDS,nAlg);
-      Error = zeros(nDS,nAlg);
-      dataSetLegends = {};
-      for d=1:nDS  
-          dSName = data.Simulation.DataSet{d}.Attributes.name;
-          dataSetLegends = [dataSetLegends, cleanString(dSName)];
-          legendKeys = {}; 
-          
-          for alg = 1:nAlg
-            algname = data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name;
-            %xpath expression
-            exp = strcat('//DataSet[@name="',dSName ,'"]/Classifier[@name="',CName,'"]/Metric[@name="',MName,'"]/Algorithms/Algorithm[@name="',algname,'"]/Mean');
-            nodeList = queryXml(exp,file);
-            legendKeys = [legendKeys, cleanString(algname)];
-            
-            % Iterate through the nodes that are returned. but it is just
-            % one node in each interation
-            acc = 0.0;
-            count = 0;
-            samples = [];
-            for i = 1:nodeList.getLength
-                node = nodeList.item(i-1);
-                %convert text matrix to number matrix
-                values = str2num( node.getFirstChild.getNodeValue);
-                samples = [samples, values];
-                acc = acc + sum(values);
-                count = count + length(values);
-                %disp(str2num( node.getFirstChild.getNodeValue))
[…]

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BarGraphs/dataSetXFeatureSelection_avgCl/GenerateBarGraph.m

@@ -1,76 +1,0 @@
-%script to generate barGraph
-
-%clear
-clear all, close all;
-
-%xml file
-file = 'featureSelection.xml';
-
-%read the xml to struct
-data = xml2struct(file);
-
-%number of data sets
-nDS = size(data.Simulation.DataSet,2);
-
-%number of algs
-nAlg = size(data.Simulation.DataSet{1}.Classifier{1}.Metric{1}.Algorithms.Algorithm,2);
-
-
-%loop over metrics
-nM = size(data.Simulation.DataSet{1}.Classifier{1}.Metric,2);
-for m = 1:nM
-    MName = data.Simulation.DataSet{1}.Classifier{1}.Metric{m}.Attributes.name;
-    
-    %compute average and plot
-    Y = zeros(nDS,nAlg);
-    Error = zeros(nDS,nAlg);
-    dataSetLegends = {};
-    for d=1:nDS
-        dSName = data.Simulation.DataSet{d}.Attributes.name;
-        dataSetLegends = [dataSetLegends, cleanString(dSName)];
-        legendKeys = {};
-        
-        for alg = 1:nAlg
-            algname = data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name;
-            legendKeys = [legendKeys, cleanString(algname)];
-            
-            % Iterate through the nodes that are returned. but it is just
-            % one node in each interation
-            acc = 0.0;
-            count = 0;
-            samples = [];
-            %loop over classifiers
-            nCl = size(data.Simulation.DataSet{1}.Classifier,2);
-            for c = 1:nCl
-                CName = data.Simulation.DataSet{1}.Classifier{c}.Attributes.name;
-                
-                %xpath expression
-                exp = strcat('//DataSet[@name="',dSName ,'"]/Classifier[@name="',CName,'"]/Metric[@name="',MName,'"]/Algorithms/Algorithm[@name="',algname,'"]/Mean');
-                nodeList = queryXml(exp,file);
-                for i = 1:nodeList.getLength
-                    node = nodeList.item(i-1);
-                    %convert text matrix to number matrix
-                    values = str2num( node.getFirstChild.getNodeValue);
-                    samples = [samples, values];
-                    acc = acc + sum(values);
-                    count = count + length(values);
[…]

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BarGraphs/dataSetXFeatureSelection_avgCl/cleanString.m

@@ -1,22 +1,0 @@
-function [ S ] = cleanString( S )
-
- 
- S = lower(regexprep(S,'[^a-zA-Z]',' '));
-
- skipset={'a','an','and','or','in','the'}; 
-
-
-if iscell(S)
-    S=cellfun(@(x) capitalize(x, skipset),S,'uniformoutput',false);
-else
-    skip=0;
-    Sw=regexp(S,'[ \t]','split');
-    skip(2:length(Sw))=ismember(lower(Sw(2:end)),skipset); %skip(1) is always 0
-    Sw(~skip)=cellfun(@(x) [upper(x(1)) x(2:end)],Sw(~skip),'uniformoutput',false);
-    S=sprintf('%s ',Sw{:});
-    S(end)='';
-    
-    
-end 
-end
-

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BoxPlot/GenerateBoxPlot.m

@@ -1,72 +1,0 @@
-%script to generate barGraph
-
-%clear
-clear all, close all;
-
-%xml file
-file = 'featureSelection.xml';
-
-%read the xml to struct
-data = xml2struct(file);
-
-%number of data sets
-nDS = size(data.Simulation.DataSet,2);
-
-%number of algs
-nAlg = size(data.Simulation.DataSet{1}.Classifier{1}.Metric{1}.Algorithms.Algorithm,2);
-
-
-%loop over metrics
-nM = size(data.Simulation.DataSet{1}.Classifier{1}.Metric,2);
-for m = 1:nM
-    MName = data.Simulation.DataSet{1}.Classifier{1}.Metric{m}.Attributes.name;
-    
-    %compute average and plot
-    Y = zeros(nDS,nAlg);
-    dataSetLegends = {};
-    for d=1:nDS
-        dSName = data.Simulation.DataSet{d}.Attributes.name;
-        dataSetLegends = [dataSetLegends, cleanString(dSName)];
-        legendKeys = {};
-        
-        for alg = 1:nAlg
-            algname = data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name;
-            legendKeys = [legendKeys, cleanString(algname)];
-            
-            % Iterate through the nodes that are returned. but it is just
-            % one node in each interation
-            acc = 0.0;
-            count = 0;
-            %loop over classifiers
-            nCl = size(data.Simulation.DataSet{1}.Classifier,2);
-            for c = 1:nCl
-                CName = data.Simulation.DataSet{1}.Classifier{c}.Attributes.name;
-                
-                %xpath expression
-                exp = strcat('//DataSet[@name="',dSName ,'"]/Classifier[@name="',CName,'"]/Metric[@name="',MName,'"]/Algorithms/Algorithm[@name="',algname,'"]/Mean');
-                nodeList = queryXml(exp,file);
-                for i = 1:nodeList.getLength
-                    node = nodeList.item(i-1);
-                    %convert text matrix to number matrix
-                    values = str2num( node.getFirstChild.getNodeValue);
-                    acc = acc + sum(values);
-                    count = count + length(values);
-                    %disp(str2num( node.getFirstChild.getNodeValue))
-                end;
-                
-            end;
-            Y(d,alg) = acc/count;
-        end;
[…]

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BoxPlot/createBoxPlot.m

@@ -1,23 +1,0 @@
-function createBoxPlot(ymatrix1, boxLengends, titleName, ylabelTxt, xlabelTxt )
-%CREATEFIGURE(YMATRIX1)
-%  YMATRIX1:  bar matrix data
-
-%  Auto-generated by MATLAB on 31-Jan-2014 14:50:05
-
-for i=1:length(boxLengends)
-    boxLengends{i} = strjoin(acronym(boxLengends{i}),'.');
-end;
-
-% Create multiple lines using matrix input to bar
-figure, boxplot(ymatrix1,boxLengends)
-
-
-% Create title
-title(titleName);
-
-% Create xlabel
-xlabel(xlabelTxt);
-
-% Create ylabel
-ylabel(ylabelTxt);
-

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/LineGraphs/FullResults/generateGraphs.m

@@ -1,57 +1,0 @@
-%script to generate graphs
-%todo: specify the labels for each algoritghm, it follows the order in
-%wich the algorithms appears in the xml
-
-%clear 
-clear all, close all;
-
-data = xml2struct('featureSelection.xml');
-
-%config legends and plot colors => TODO
-%legendKeys = data.simulation.Attributes.algs;
-%legendDef = containers.Map(legendKeys, {'',''});
-
-%loop over Data Sets
-nDS = size(data.Simulation.DataSet,2);
-for d=1:nDS
-    dSName = cleanString(data.Simulation.DataSet{d}.Attributes.name);
-    dSNumFea = str2double(data.Simulation.DataSet{d}.Attributes.nfeatures);
-    
-    %loop over classifiers
-    nCl = size(data.Simulation.DataSet{d}.Classifier,2);
-    for c = 1:nCl
-        CName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Attributes.name);
-        
-        %loop over metrics
-        nM = size(data.Simulation.DataSet{d}.Classifier{c}.Metric,2);
-        for m = 1:nM
-            MName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Attributes.name);
-            nAlg = size(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm,2);
-                               
-            %plot each graph
-            figure, hold on;
-            
-            %TODO: define symbols 
-            plotSymbols = {'-g<','-mv','-mo','-m^','-gs','-bp','-bd','-rp','-g>','-mx','-rd','-mh','-kd','-kp'};
-            legendKeys = {}; 
-            for alg = 1:nAlg
-                mean = str2num(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Mean.Text);
-                algname = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name);
-                legendKeys = [legendKeys, algname];
-                plot(1:dSNumFea, mean, plotSymbols{alg})
-                
-                
-            end;
-            
-            %plot settings
-            title(cleanString(strjoin({dSName, CName, MName},' ')));
-            xlabel('Number of features');
-            ylabel(MName);
-            legend(legendKeys,'Location', 'SouthOutside');
[…]

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/LineGraphs/FullResultsWithoutNoutOfK/generateGraphs.m

@@ -1,57 +1,0 @@
-%script to generate graphs
-%todo: specify the labels for each algoritghm, it follows the order in
-%wich the algorithms appears in the xml
-
-%clear 
-clear all, close all;
-
-data = xml2struct('featureSelection.xml');
-
-%config legends and plot colors => TODO
-%legendKeys = data.simulation.Attributes.algs;
-%legendDef = containers.Map(legendKeys, {'',''});
-
-%loop over Data Sets
-nDS = size(data.Simulation.DataSet,2);
-for d=1:nDS
-    dSName = cleanString(data.Simulation.DataSet{d}.Attributes.name);
-    dSNumFea = str2double(data.Simulation.DataSet{d}.Attributes.nfeatures);
-    
-    %loop over classifiers
-    nCl = size(data.Simulation.DataSet{d}.Classifier,2);
-    for c = 1:nCl
-        CName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Attributes.name);
-        
-        %loop over metrics
-        nM = size(data.Simulation.DataSet{d}.Classifier{c}.Metric,2);
-        for m = 1:nM
-            MName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Attributes.name);
-            nAlg = size(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm,2);
-                               
-            %plot each graph
-            figure, hold on;
-            
-            %TODO: define symbols 
-            plotSymbols = {'-g<','-mv','-mo','-m^','-gs','-g>','-mx','-mh','-bp','-bd','-rp','-rd'};
-            legendKeys = {}; 
-            for alg = 1:nAlg
-                mean = str2num(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Mean.Text);
-                algname = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name);
-                legendKeys = [legendKeys, algname];
-                plot(1:dSNumFea, mean, plotSymbols{alg})
-                
-                
-            end;
-            
-            %plot settings
-            title(cleanString(strjoin({dSName, CName, MName},' ')));
-            xlabel('Number of features');
-            ylabel(MName);
-            legend(legendKeys,'Location', 'SouthOutside');
-            %axis([1 dSNumFea 0 1])
[…]

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BarGraphs/FeatureSelectionXClassifier/GenerateBarGraph.m

@@ -1,76 +1,0 @@
-%script to generate barGraph, major = feature selection, minor = classifier
-
-%clear
-clear all, close all;
-
-%xml file
-file = 'featureSelection.xml';
-
-%read the xml to struct
-data = xml2struct(file);
-
-%number of data sets
-nDS = size(data.Simulation.DataSet,2);
-for d=1:nDS
-    dSName = data.Simulation.DataSet{d}.Attributes.name;
-    
-    %loop over metrics
-    nM = size(data.Simulation.DataSet{d}.Classifier{1}.Metric,2);
-    for m = 1:nM
-        MName = data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Attributes.name;
-        nCl = size(data.Simulation.DataSet{d}.Classifier,2);
-        nAlg = size(data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Algorithms.Algorithm,2);
-        Y = zeros(nAlg,nCl);
-        Error = zeros(nAlg,nCl);
-        
-        algLegend = {};
-        for alg = 1:nAlg
-            algname = data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name;
-            algLegend = [algLegend, cleanString(algname)];
-            classifiersLegends = {};
-            %loop over classifiers
-            nCl = size(data.Simulation.DataSet{1}.Classifier,2);
-            for c = 1:nCl
-                CName = data.Simulation.DataSet{1}.Classifier{c}.Attributes.name;
-                classifiersLegends = [classifiersLegends, cleanString(CName)];
-                
-                %xpath expression
-                exp = strcat('//DataSet[@name="',dSName ,'"]/Classifier[@name="',CName,'"]/Metric[@name="',MName,'"]/Algorithms/Algorithm[@name="',algname,'"]/Mean');
-                nodeList = queryXml(exp,file);
-                
-                % Iterate through the nodes that are returned. but it is just
-                % one node in each interation
-                acc = 0.0;
-                count = 0;
-                samples = [];
-                for i = 1:nodeList.getLength
-                    node = nodeList.item(i-1);
-                    %convert text matrix to number matrix
-                    values = str2num( node.getFirstChild.getNodeValue);
-                    samples = [samples, values];
-                    acc = acc + sum(values);
-                    count = count + length(values);
[…]

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BarGraphs/FeatureSelectionXClassifier/createBarGraph.m

@@ -1,31 +1,0 @@
-function createBarGraph(ymatrix1, xgroupsLabels, barLegends, titleName, ylabelTxt, xlabelTxt )
-%CREATEFIGURE(YMATRIX1)
-%  YMATRIX1:  bar matrix data
-
-%  Auto-generated by MATLAB on 31-Jan-2014 14:50:05
-
-% Create figure
-figure1 = figure;
-
-% Create axes
-axes1 = axes('Parent',figure1,'XTickLabel',xgroupsLabels,...
-    'XTick',1:length(xgroupsLabels));
-box(axes1,'on');
-hold(axes1,'all');
-
-% Create multiple lines using matrix input to bar
-bar1 = bar(ymatrix1,'Parent',axes1);
-
-
-% Create title
-title(titleName);
-
-% Create xlabel
-xlabel(xlabelTxt);
-
-%set legend
-legend(barLegends,'Location', 'SouthOutside');
-
-% Create ylabel
-ylabel(ylabelTxt);
-

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BarGraphs/dataSetXFeatureSelection_avgCl/barweb.m

@@ -1,195 +1,0 @@
-function handles = barweb(barvalues, errors, width, groupnames, bw_title, bw_xlabel, bw_ylabel, bw_colormap, gridstatus, bw_legend, error_sides, legend_type)
-
-%
-% Usage: handles = barweb(barvalues, errors, width, groupnames, bw_title, bw_xlabel, bw_ylabel, bw_colormap, gridstatus, bw_legend, error_sides, legend_type)
-%
-% Ex: handles = barweb(my_barvalues, my_errors, [], [], [], [], [], bone, [], bw_legend, 1, 'axis')
-%
-% barweb is the m-by-n matrix of barvalues to be plotted.
-% barweb calls the MATLAB bar function and plots m groups of n bars using the width and bw_colormap parameters.
-% If you want all the bars to be the same color, then set bw_colormap equal to the RBG matrix value ie. (bw_colormap = [1 0 0] for all red bars)
-% barweb then calls the MATLAB errorbar function to draw barvalues with error bars of length error.
-% groupnames is an m-length cellstr vector of groupnames (i.e. groupnames = {'group 1'; 'group 2'}).  For no groupnames, enter [] or {}
-% The errors matrix is of the same form of the barvalues matrix, namely m group of n errors.
-% Gridstatus is either 'x','xy', 'y', or 'none' for no grid.
-% No legend will be shown if the legend paramter is not provided
-% 'error_sides = 2' plots +/- std while 'error_sides = 1' plots just + std
-% legend_type = 'axis' produces the legend along the x-axis while legend_type = 'plot' produces the standard legend.  See figure for more details
-%
-% The following default values are used if parameters are left out or skipped by using [].
-% width = 1 (0 < width < 1; widths greater than 1 will produce overlapping bars)
-% groupnames = '1', '2', ... number_of_groups
-% bw_title, bw_xlabel, bw_ylabel = []
-% bw_color_map = jet
-% gridstatus = 'none'
-% bw_legend = []
-% error_sides = 2;
-% legend_type = 'plot';
-%
[…]

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BarGraphs/dataSetXFeatureSelection_avgCl/createBarGraph.m

@@ -1,30 +1,0 @@
-function createBarGraph(ymatrix1, xgroupsLabels, barLegends, titleName, ylabelTxt, xlabelTxt )
-%CREATEFIGURE(YMATRIX1)
-%  YMATRIX1:  bar matrix data
-
-%  Auto-generated by MATLAB on 31-Jan-2014 14:50:05
-
-% Create figure
-figure1 = figure;
-
-% Create axes
-axes1 = axes('Parent',figure1,'XTickLabel',xgroupsLabels,...
-    'XTick',1:length(xgroupsLabels));
-box(axes1,'on');
-hold(axes1,'all');
-
-% Create multiple lines using matrix input to bar
-bar1 = bar(ymatrix1,'Parent',axes1);
-
-% Create title
-title(titleName);
-
-% Create xlabel
-xlabel(xlabelTxt);
-
-%set legend
-legend(barLegends,'Location', 'SouthOutside');
-
-% Create ylabel
-ylabel(ylabelTxt);
-

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BarGraphs/dataSetXFeatureSelection_avgCl/queryXml.m

@@ -1,24 +1,0 @@
-function [ nodeList ] = queryXml( xpathExp, file )
-
-% Import the XPath classes
-import javax.xml.xpath.*
-
-% Construct the DOM.
-doc = xmlread(which(file));
-
-% Create an XPath expression.
-factory = XPathFactory.newInstance;
-xpath = factory.newXPath;
-expression = xpath.compile(xpathExp);
-
-% Apply the expression to the DOM.
-nodeList = expression.evaluate(doc,XPathConstants.NODESET);
-
-% Iterate through the nodes that are returned.
-for i = 1:nodeList.getLength
-    node = nodeList.item(i-1);
-    disp(char(node.getAttribute('name')))
-end;
-
-end
-

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BarGraphs/FeatureSelectionXClassifier/GenerateBarGraph.m

@@ -1,0 +1,76 @@
+%script to generate barGraph, major = feature selection, minor = classifier
+
+%clear
+clear all, close all;
+
+%xml file
+file = 'featureSelection.xml';
+
+%read the xml to struct
+data = xml2struct(file);
+
+%number of data sets
+nDS = size(data.Simulation.DataSet,2);
+for d=1:nDS
+    dSName = data.Simulation.DataSet{d}.Attributes.name;
+    
+    %loop over metrics
+    nM = size(data.Simulation.DataSet{d}.Classifier{1}.Metric,2);
+    for m = 1:nM
+        MName = data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Attributes.name;
+        nCl = size(data.Simulation.DataSet{d}.Classifier,2);
+        nAlg = size(data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Algorithms.Algorithm,2);
+        Y = zeros(nAlg,nCl);
+        Error = zeros(nAlg,nCl);
+        
+        algLegend = {};
+        for alg = 1:nAlg
+            algname = data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name;
+            algLegend = [algLegend, cleanString(algname)];
+            classifiersLegends = {};
+            %loop over classifiers
+            nCl = size(data.Simulation.DataSet{1}.Classifier,2);
+            for c = 1:nCl
+                CName = data.Simulation.DataSet{1}.Classifier{c}.Attributes.name;
+                classifiersLegends = [classifiersLegends, cleanString(CName)];
+                
+                %xpath expression
+                exp = strcat('//DataSet[@name="',dSName ,'"]/Classifier[@name="',CName,'"]/Metric[@name="',MName,'"]/Algorithms/Algorithm[@name="',algname,'"]/Mean');
+                nodeList = queryXml(exp,file);
+                
+                % Iterate through the nodes that are returned. but it is just
+                % one node in each interation
+                acc = 0.0;
+                count = 0;
+                samples = [];
+                for i = 1:nodeList.getLength
+                    node = nodeList.item(i-1);
+                    %convert text matrix to number matrix
+                    values = str2num( node.getFirstChild.getNodeValue);
+                    samples = [samples, values];
+                    acc = acc + sum(values);
+                    count = count + length(values);
[…]

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BarGraphs/dataSetXFeatureSelection/queryXml.m

@@ -1,0 +1,24 @@
+function [ nodeList ] = queryXml( xpathExp, file )
+
+% Import the XPath classes
+import javax.xml.xpath.*
+
+% Construct the DOM.
+doc = xmlread(which(file));
+
+% Create an XPath expression.
+factory = XPathFactory.newInstance;
+xpath = factory.newXPath;
+expression = xpath.compile(xpathExp);
+
+% Apply the expression to the DOM.
+nodeList = expression.evaluate(doc,XPathConstants.NODESET);
+
+% Iterate through the nodes that are returned.
+for i = 1:nodeList.getLength
+    node = nodeList.item(i-1);
+    disp(char(node.getAttribute('name')))
+end;
+
+end
+

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BarGraphs/dataSetXFeatureSelection_avgCl/GenerateBarGraph.m

@@ -1,0 +1,76 @@
+%script to generate barGraph
+
+%clear
+clear all, close all;
+
+%xml file
+file = 'featureSelection.xml';
+
+%read the xml to struct
+data = xml2struct(file);
+
+%number of data sets
+nDS = size(data.Simulation.DataSet,2);
+
+%number of algs
+nAlg = size(data.Simulation.DataSet{1}.Classifier{1}.Metric{1}.Algorithms.Algorithm,2);
+
+
+%loop over metrics
+nM = size(data.Simulation.DataSet{1}.Classifier{1}.Metric,2);
+for m = 1:nM
+    MName = data.Simulation.DataSet{1}.Classifier{1}.Metric{m}.Attributes.name;
+    
+    %compute average and plot
+    Y = zeros(nDS,nAlg);
+    Error = zeros(nDS,nAlg);
+    dataSetLegends = {};
+    for d=1:nDS
+        dSName = data.Simulation.DataSet{d}.Attributes.name;
+        dataSetLegends = [dataSetLegends, cleanString(dSName)];
+        legendKeys = {};
+        
+        for alg = 1:nAlg
+            algname = data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name;
+            legendKeys = [legendKeys, cleanString(algname)];
+            
+            % Iterate through the nodes that are returned. but it is just
+            % one node in each interation
+            acc = 0.0;
+            count = 0;
+            samples = [];
+            %loop over classifiers
+            nCl = size(data.Simulation.DataSet{1}.Classifier,2);
+            for c = 1:nCl
+                CName = data.Simulation.DataSet{1}.Classifier{c}.Attributes.name;
+                
+                %xpath expression
+                exp = strcat('//DataSet[@name="',dSName ,'"]/Classifier[@name="',CName,'"]/Metric[@name="',MName,'"]/Algorithms/Algorithm[@name="',algname,'"]/Mean');
+                nodeList = queryXml(exp,file);
+                for i = 1:nodeList.getLength
+                    node = nodeList.item(i-1);
+                    %convert text matrix to number matrix
+                    values = str2num( node.getFirstChild.getNodeValue);
+                    samples = [samples, values];
+                    acc = acc + sum(values);
+                    count = count + length(values);
[…]

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BoxPlot/BoxPlot2/GenerateBoxPlot.m

@@ -1,0 +1,73 @@
+%script to generate barGraph
+
+%clear
+clear all, close all;
+
+%xml file
+file = 'featureSelection.xml';
+
+%read the xml to struct
+data = xml2struct(file);
+
+%number of data sets
+nDS = size(data.Simulation.DataSet,2);
+
+%number of algs
+nAlg = size(data.Simulation.DataSet{1}.Classifier{1}.Metric{1}.Algorithms.Algorithm,2);
+
+
+%loop over metrics
+nM = size(data.Simulation.DataSet{1}.Classifier{1}.Metric,2);
+for m = 1:nM
+    MName = data.Simulation.DataSet{1}.Classifier{1}.Metric{m}.Attributes.name;
+    
+    %compute average and plot
+    Y = zeros(nDS,nAlg);
+    dataSetLegends = {};
+    for d=1:nDS
+        dSName = data.Simulation.DataSet{d}.Attributes.name;
+        dataSetLegends = [dataSetLegends, cleanString(dSName)];
+        legendKeys = {};
+        
+        for alg = 1:nAlg
+            algname = data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name;
+            legendKeys = [legendKeys, cleanString(algname)];
+            
+            % Iterate through the nodes that are returned. but it is just
+            % one node in each interation
+            acc = 0.0;
+            count = 0;
+            %loop over classifiers
+            nCl = size(data.Simulation.DataSet{1}.Classifier,2);
+            for c = 1:nCl
+                CName = data.Simulation.DataSet{1}.Classifier{c}.Attributes.name;
+                
+                if(~strcmpi(CName,'SVM_LINEAR'))
+                    %xpath expression
+                    exp = strcat('//DataSet[@name="',dSName ,'"]/Classifier[@name="',CName,'"]/Metric[@name="',MName,'"]/Algorithms/Algorithm[@name="',algname,'"]/Mean');
+                    nodeList = queryXml(exp,file);
+                    for i = 1:nodeList.getLength
+                        node = nodeList.item(i-1);
+                        %convert text matrix to number matrix
+                        values = str2num( node.getFirstChild.getNodeValue);
+                        acc = acc + sum(values);
+                        count = count + length(values);
+                        %disp(str2num( node.getFirstChild.getNodeValue))
+                    end;
[…]

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/LineGraphs/FullResults/generateGraphs.m

@@ -1,0 +1,57 @@
+%script to generate graphs
+%todo: specify the labels for each algoritghm, it follows the order in
+%wich the algorithms appears in the xml
+
+%clear 
+clear all, close all;
+
+data = xml2struct('featureSelection.xml');
+
+%config legends and plot colors => TODO
+%legendKeys = data.simulation.Attributes.algs;
+%legendDef = containers.Map(legendKeys, {'',''});
+
+%loop over Data Sets
+nDS = size(data.Simulation.DataSet,2);
+for d=1:nDS
+    dSName = cleanString(data.Simulation.DataSet{d}.Attributes.name);
+    dSNumFea = str2double(data.Simulation.DataSet{d}.Attributes.nfeatures);
+    
+    %loop over classifiers
+    nCl = size(data.Simulation.DataSet{d}.Classifier,2);
+    for c = 1:nCl
+        CName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Attributes.name);
+        
+        %loop over metrics
+        nM = size(data.Simulation.DataSet{d}.Classifier{c}.Metric,2);
+        for m = 1:nM
+            MName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Attributes.name);
+            nAlg = size(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm,2);
+                               
+            %plot each graph
+            figure, hold on;
+            
+            %TODO: define symbols 
+            plotSymbols = {'-g<','-gv','-g>','-g^','-g*','-mo','-mx','-ms','-bd','-bp','-rd','-rp','-kd','-kp'};
+            legendKeys = {}; 
+            for alg = 1:nAlg
+                mean = str2num(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Mean.Text);
+                algname = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name);
+                legendKeys = [legendKeys, algname];
+                plot(1:dSNumFea, mean, plotSymbols{alg})
+                
+                
+            end;
+            
+            %plot settings
+            title(cleanString(strjoin({dSName, CName, MName},' ')));
+            xlabel('Number of features');
+            ylabel(MName);
+            legend(legendKeys,'Location', 'SouthOutside');
[…]

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/LineGraphs/FullResultsWithoutNoutOfK/generateGraphs.m

@@ -1,0 +1,57 @@
+%script to generate graphs
+%todo: specify the labels for each algoritghm, it follows the order in
+%wich the algorithms appears in the xml
+
+%clear 
+clear all, close all;
+
+data = xml2struct('featureSelection.xml');
+
+%config legends and plot colors => TODO
+%legendKeys = data.simulation.Attributes.algs;
+%legendDef = containers.Map(legendKeys, {'',''});
+
+%loop over Data Sets
+nDS = size(data.Simulation.DataSet,2);
+for d=1:nDS
+    dSName = cleanString(data.Simulation.DataSet{d}.Attributes.name);
+    dSNumFea = str2double(data.Simulation.DataSet{d}.Attributes.nfeatures);
+    
+    %loop over classifiers
+    nCl = size(data.Simulation.DataSet{d}.Classifier,2);
+    for c = 1:nCl
+        CName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Attributes.name);
+        
+        %loop over metrics
+        nM = size(data.Simulation.DataSet{d}.Classifier{c}.Metric,2);
+        for m = 1:nM
+            MName = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Attributes.name);
+            nAlg = size(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm,2);
+                               
+            %plot each graph
+            figure, hold on;
+            
+            %TODO: define symbols 
+           plotSymbols = {'-g<','-gv','-g>','-g^','-g*','-mo','-mx','-ms','-bd','-bp','-rd','-rp'};
+            legendKeys = {}; 
+            for alg = 1:nAlg
+                mean = str2num(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Mean.Text);
+                algname = cleanString(data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name);
+                legendKeys = [legendKeys, algname];
+                plot(1:dSNumFea, mean, plotSymbols{alg})
+                
+                
+            end;
+            
+            %plot settings
+            title(cleanString(strjoin({dSName, CName, MName},' ')));
+            xlabel('Number of features');
+            ylabel(MName);
+            legend(legendKeys,'Location', 'SouthOutside');
+            %axis([1 dSNumFea 0 1])
[…]

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BoxPlot/BoxPlot3/createBoxPlot.m

@@ -1,23 +1,0 @@
-function createBoxPlot(ymatrix1, boxLengends, titleName, ylabelTxt, xlabelTxt )
-%CREATEFIGURE(YMATRIX1)
-%  YMATRIX1:  bar matrix data
-
-%  Auto-generated by MATLAB on 31-Jan-2014 14:50:05
-
-for i=1:length(boxLengends)
-    boxLengends{i} = strjoin(acronym(boxLengends{i}),'');
-end;
-
-% Create multiple lines using matrix input to bar
-figure, boxplot(ymatrix1,boxLengends)
-
-
-% Create title
-title(titleName);
-
-% Create xlabel
-xlabel(xlabelTxt);
-
-% Create ylabel
-ylabel(ylabelTxt);
-

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BoxPlot/BoxPlot3/GenerateBoxPlot.m

@@ -1,73 +1,0 @@
-%script to generate barGraph
-
-%clear
-clear all, close all;
-
-%xml file
-file = 'featureSelection.xml';
-
-%read the xml to struct
-data = xml2struct(file);
-
-%number of data sets
-nDS = size(data.Simulation.DataSet,2);
-
-%number of algs
-nAlg = size(data.Simulation.DataSet{1}.Classifier{1}.Metric{1}.Algorithms.Algorithm,2);
-
-
-%loop over metrics
-nM = size(data.Simulation.DataSet{1}.Classifier{1}.Metric,2);
-for m = 1:nM
-    MName = data.Simulation.DataSet{1}.Classifier{1}.Metric{m}.Attributes.name;
-    
-    %loop over classifiers
-    nCl = size(data.Simulation.DataSet{1}.Classifier,2);
-    for c = 1:nCl
-        CName = data.Simulation.DataSet{1}.Classifier{c}.Attributes.name;
-        
-        %compute average and plot
-        Y = zeros(nDS,nAlg);
-        dataSetLegends = {};
-        for d=1:nDS
-            dSName = data.Simulation.DataSet{d}.Attributes.name;
-            dataSetLegends = [dataSetLegends, cleanString(dSName)];
-            legendKeys = {};
-            
-            for alg = 1:nAlg
-                algname = data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name;
-                legendKeys = [legendKeys, cleanString(algname)];
-                
-                %xpath expression
-                exp = strcat('//DataSet[@name="',dSName ,'"]/Classifier[@name="',CName,'"]/Metric[@name="',MName,'"]/Algorithms/Algorithm[@name="',algname,'"]/Mean');
-                
-                acc = 0.0;
-                count = 0;
-                nodeList = queryXml(exp,file);
-                for i = 1:nodeList.getLength
-                    node = nodeList.item(i-1);
-                    %convert text matrix to number matrix
-                    values = str2num( node.getFirstChild.getNodeValue);
-                    acc = acc + sum(values);
-                    count = count + length(values);
-                    %disp(str2num( node.getFirstChild.getNodeValue))
-                end;
-                Y(d,alg) = acc/count;
-            end;
-            
-            %normalize
-            Y(d,:) = Y(d,:) ./ max(Y(d,:));
-        end;
-        
[…]

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/BoxPlot/BoxPlot3/acronym.m

@@ -1,9 +1,0 @@
-function output = acronym( input )
-  words_cell = textscan(input,'%s','delimiter',' ');
-  words      = words_cell{ : };
-  letters    = cellfun(@(x) textscan(x,'%c%*s'), words);
-  if(length(letters) > 3)
-    output = upper(letters(1:3)');
-  else
-     output = upper(letters');
-end

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/OthersDataSets/BarGraphs/dataSetXFeatureSelection_avgCl/createBarGraph.m

@@ -1,0 +1,30 @@
+function createBarGraph(ymatrix1, xgroupsLabels, barLegends, titleName, ylabelTxt, xlabelTxt )
+%CREATEFIGURE(YMATRIX1)
+%  YMATRIX1:  bar matrix data
+
+%  Auto-generated by MATLAB on 31-Jan-2014 14:50:05
+
+% Create figure
+figure1 = figure;
+
+% Create axes
+axes1 = axes('Parent',figure1,'XTickLabel',xgroupsLabels,...
+    'XTick',1:length(xgroupsLabels));
+box(axes1,'on');
+hold(axes1,'all');
+
+% Create multiple lines using matrix input to bar
+bar1 = bar(ymatrix1,'Parent',axes1);
+
+% Create title
+title(titleName);
+
+% Create xlabel
+xlabel(xlabelTxt);
+
+%set legend
+legend(barLegends,'Location', 'SouthOutside');
+
+% Create ylabel
+ylabel(ylabelTxt);
+

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/OthersDataSets/BoxPlot/BoxPlot1/GenerateBoxPlot.m

@@ -1,0 +1,72 @@
+%script to generate barGraph
+
+%clear
+clear all, close all;
+
+%xml file
+file = 'featureSelection.xml';
+
+%read the xml to struct
+data = xml2struct(file);
+
+%number of data sets
+nDS = size(data.Simulation.DataSet,2);
+
+%number of algs
+nAlg = size(data.Simulation.DataSet{1}.Classifier{1}.Metric{1}.Algorithms.Algorithm,2);
+
+
+%loop over metrics
+nM = size(data.Simulation.DataSet{1}.Classifier{1}.Metric,2);
+for m = 1:nM
+    MName = data.Simulation.DataSet{1}.Classifier{1}.Metric{m}.Attributes.name;
+    
+    %compute average and plot
+    Y = zeros(nDS,nAlg);
+    dataSetLegends = {};
+    for d=1:nDS
+        dSName = data.Simulation.DataSet{d}.Attributes.name;
+        dataSetLegends = [dataSetLegends, cleanString(dSName)];
+        legendKeys = {};
+        
+        for alg = 1:nAlg
+            algname = data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name;
+            legendKeys = [legendKeys, cleanString(algname)];
+            
+            % Iterate through the nodes that are returned. but it is just
+            % one node in each interation
+            acc = 0.0;
+            count = 0;
+            %loop over classifiers
+            nCl = size(data.Simulation.DataSet{1}.Classifier,2);
+            for c = 1:nCl
+                CName = data.Simulation.DataSet{1}.Classifier{c}.Attributes.name;
+                
+                %xpath expression
+                exp = strcat('//DataSet[@name="',dSName ,'"]/Classifier[@name="',CName,'"]/Metric[@name="',MName,'"]/Algorithms/Algorithm[@name="',algname,'"]/Mean');
+                nodeList = queryXml(exp,file);
+                for i = 1:nodeList.getLength
+                    node = nodeList.item(i-1);
+                    %convert text matrix to number matrix
+                    values = str2num( node.getFirstChild.getNodeValue);
+                    acc = acc + sum(values);
+                    count = count + length(values);
+                    %disp(str2num( node.getFirstChild.getNodeValue))
+                end;
+                
+            end;
+            Y(d,alg) = acc/count;
+        end;
[…]

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/OthersDataSets/BoxPlot/BoxPlot3/createBoxPlot.m

@@ -1,0 +1,23 @@
+function createBoxPlot(ymatrix1, boxLengends, titleName, ylabelTxt, xlabelTxt )
+%CREATEFIGURE(YMATRIX1)
+%  YMATRIX1:  bar matrix data
+
+%  Auto-generated by MATLAB on 31-Jan-2014 14:50:05
+
+for i=1:length(boxLengends)
+    boxLengends{i} = strjoin(acronym(boxLengends{i}),'');
+end;
+
+% Create multiple lines using matrix input to bar
+figure, boxplot(ymatrix1,boxLengends)
+
+
+% Create title
+title(titleName);
+
+% Create xlabel
+xlabel(xlabelTxt);
+
+% Create ylabel
+ylabel(ylabelTxt);
+

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Added Libo's related work

--- 2014-02-03  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
@@
 \section{Empirical}
-In this section, we conduct experiments to study the feature selection performances of several well known methods such as Symmetrical Uncertainty Rank, Gain Ratio Rank, Information Gain Rank, Correlation Based Rank, Conditional Entropy Rank \cite{guyon_jmlr03}, Correlation-based Feature Subset Selection \cite{Hall1998},  Reliff \cite{Robnik-Sikonja2003} , mRMR \cite{peng2005} and our proposed methods: High Precision Expectation, High Precision Log likelihood, High Recall Expectation and High Recall Log likelihood.
-The first six methods are variable rank methods and the last six are subset rank methods.
 
-In these experimental study, we evaluated each feature selection method in binary classification problems such as Breast Cancer, Pima Diabetes, Heart Statlog, Spect and Vote.
-These data sets can be downloaded from UCI machine learning repository \cite{Bache+Lichman:2013}.
-In addition, we used three different classifiers to solve each of the binary classifier problem.
-Logistic Regression, SVM Linear and Naive Bayes were used in the experiments and the first two are implemented in LibLinear library \cite{REF08a} and the last one is implemented in Weka software \cite{weka}.
+In this section, we conduct experiments to study the feature selection
+performances of several well known methods such as Symmetrical
+Uncertainty Rank, Gain Ratio Rank, Information Gain Rank, Correlation
+Based Rank, Conditional Entropy Rank \cite{guyon_jmlr03},
+Correlation-based Feature Subset Selection \cite{Hall1998}, Reliff
+\cite{Robnik-Sikonja2003} , mRMR \cite{peng2005} and our proposed
+methods: High Precision Expectation, High Precision Log likelihood,
+High Recall Expectation and High Recall Log likelihood. The first five
+methods are variable rank methods and the last seven are subset rank
+methods.
 
-To evaluate the feature selection performances we reported classification metrics performing 10-fold cross-validation from one until the max number of features selected for each classifier solving each of the binary classification problem.
-Specifically, we reported Accuracy, Precision, Recall and F-Score for the true label class, that could be identified by the context of the problem and usually be the class with least samples in the data set.
+In these experimental study, we evaluated each feature selection
+method in binary classification problems such as Breast Cancer, Pima
+Diabetes, Heart Statlog, Spect and Vote. These data sets can be
+downloaded from UCI machine learning repository
+\cite{Bache+Lichman:2013}. In addition, we used three different
+classifiers to solve each of the binary classifier problem. Logistic
+Regression, SVM Linear and Naive Bayes were used in the experiments
+and the first two are implemented in LibLinear library \cite{REF08a}
+and the last one is implemented in Weka software \cite{weka}.
+
+To evaluate the feature selection performances we reported
+classification metrics performing 10-fold cross-validation from one
+until the max number of features selected for each classifier solving
+each of the binary classification problem. Specifically, we reported
+Accuracy, Precision, Recall and F-Score for the true label class, that
+could be identified by the context of the problem and usually be the
+class with least samples in the data set.

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/related_work.tex
Added Libo's related work

\section{Related Work}

Existing feature selection algorithms fall into categories of filter
methods and wrapper methods \cite{guyon_jmlr03}. While
wrapper methods, such as SVM-RFE \cite{guyon2002gene}, select features
by evaluating theit usefulness to a given classifier, filter methods
evaluate feature subsets according to certain properties of
themselves. Within filter methods, feature selection algorithms can be
further classified into ranking methods and subset methods. The former
evaluates each features independently, while the latter evaluates a
subset at a time \cite{brown2012conditional}. Listed below is a brief
introduction to algorithms to which we compared our proposed model.

Correlation based rank is a na\"{i}ve ranking algorithm that ranks
features according to their linear correlation with the output,
i.e.\ Pearson's $r.$ More sophisticated ranking methods to which we
compared our model include:
\begin{enumerate}
\item The conditional entropy of class $Y$ given feature $X$,
  i.e.\ $H\left(Y|X\right),$ quantifies the amount of information in
  $Y$ that is not provided by $X.$ Substracting $H\left(Y|X\right)$
  from the entropy of class $Y,$ the information gain of class $Y$
  given feature $X$ is the mutual information between feature $X$ and
  class $Y,$ i.e.\ $I\left(X;Y\right).$
\item The gain ratio of feature $X$ is defined as the information gain
  of feature $X$ normalized against the entropy of itself,
  i.e.\ $\frac{I\left(X;Y\right)}{H\left(X\right)}.$
\item The summetric uncertainty between feature $X$ and class $Y$
  measures the amount of redundancy between them. It is defined as
  $U\left(X,Y\right)=2\frac{I\left(X;Y\right)}{H\left(X\right)+H\left(Y\right)}.$
\item The Relief method \cite{kira1992feature} evaluates the relevance
  of features to the output class according to how well their values
  distinguish between nearest instances of the same and different
  classes.
\end{enumerate}

The only subset algorithm to which we compared our work is MRMR
\cite{peng2005}. MRMR is an information-theory-based method
that not only maximises the relevance of selected features to the
supervised output class, but also minimises the redundancy among
selected features. Different search strategies can be applied using
MRMR as heuristics.

Although existing algorithms give various solutions, they are mostly
ad-hoc, until \cite{brown2012conditional}. Brown et al.\ derived an
information-theoretical model from first principles, and retro-fitted
existing information-theory-based feature selection methods to the
model. In this paper, we consider the other side of the same coin. We
proposed a probability-theory-based graphical model that has intuitive
qualitative meaning in precision and recall, and we built a
generalized feature selection scheme upon it.

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Rough empirical results section

@@
 \section{Empirical}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table*}[tbp!]
+\centering
+\begin{tabular}{|l|r|r|r|r|l|} \hline
+Dataset & \# Features & \# Data & \# Features/\# Data & \% True Labels & Feature Type\\ \hline \hline 
+Breast Cancer	& 9	& 699	& 0.013	& 34 \%	& All Numeric\\ \hline
+Diabetes        & 8	& 768	& 0.010	& 35 \%	& All Numeric\\ \hline
+Heart Statlog	& 13	& 270	& 0.048	& 44 \%	& All Numeric\\ \hline
+Spect	        & 22	& 80	& 0.275 & 33 \%	& Categorical\\ \hline
+Vote	        & 16	& 435	& 0.037	& 39 \%	& Categorical\\ \hline
+Newsgroup	& 500	& 1963	& 0.255	& 49 \%	& All Binary\\ \hline
+%Horse Colic	& 22	& 368	& 0.060	& 37 \%	& Categorical (16) and numeric (6)\\ \hline
+%Credit-American	& 15	& 690	& 0.022	& 44 \%	& Categorical(9) and numeric (6)\\ \hline
+%Credit-German	& 20	& 1000	& 0.020 & 30 \%	& Categorical (13) and Numeric (7)\\ \hline
+%Hepatitis	& 19	& 155	& 0.123	& 21 \%	& Categorical (13) and Numeric (6)\\ \hline
+%Ionosphere	& 34	& 351	& 0.097	& 36 \%	& All Numeric\\ \hline
+%KR-vs-KP	& 36	& 3196	& 0.011	& 48 \%	& All Categorical\\ \hline
+%Labor	        & 16	& 57	& 0.281	& 35 \%	& Categorical (8) and Numeric (8)\\ \hline
+%Mushroom	& 22	& 8124	& 0.003	& 48 \%	& All Categorical\\ \hline
+%Sick	        & 29	& 3772	& 0.008	&  6 \%	& Categorical (23) and Numeric (6)\\ \hline
+%Sonar	        & 60	& 208	& 0.288 & 47 \%	& All Numeric\\ \hline
+\end{tabular}
+\caption{\footnotesize Statistics of the various datasets evaluated in this work.}
+\label{table:stats}
+\end{table*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 performances of several well known methods such as Symmetrical
-Uncertainty Rank, Gain Ratio Rank, Information Gain Rank, Correlation
-Based Rank, Conditional Entropy Rank \cite{guyon_jmlr03},
-Correlation-based Feature Subset Selection \cite{Hall1998}, Reliff
-\cite{Robnik-Sikonja2003} , mRMR \cite{peng2005} and our proposed
-methods: High Precision Expectation, High Precision Log likelihood,
-High Recall Expectation and High Recall Log likelihood. The first five
-methods are variable rank methods and the last seven are subset rank
-methods.
+Uncertainty Rank (SUR), Gain Ratio Rank (GRR), Information Gain Rank
+(IGR), Correlation Based Rank (CBR), Conditional Entropy Rank (CER)~\cite{guyon_jmlr03}, 
+Correlation-based Feature Subset Selection (CFS)~\cite{Hall1998}, 
+Reliff (R)~\cite{Robnik-Sikonja2003} , mRMR~\cite{peng2005} and our proposed 
+methods: High Recall Expectation (HRE) and High Recall Log likelihood (HRL), 
+High Precision Expectation (HPE), High Precision Log likelihood (HPL). 
+The first five methods are variable rank methods and the last seven
+are subset rank methods.  {\bf TODO Rodrigo: explain variable rank
+and subset rank first.}
 
-In these experimental study, we evaluated each feature selection
-method in binary classification problems such as Breast Cancer, Pima
-Diabetes, Heart Statlog, Spect and Vote. These data sets can be
-downloaded from UCI machine learning repository
-\cite{Bache+Lichman:2013}. In addition, we used three different
-classifiers to solve each of the binary classifier problem. Logistic
-Regression, SVM Linear and Naive Bayes were used in the experiments
-and the first two are implemented in LibLinear library \cite{REF08a}
-and the last one is implemented in Weka software \cite{weka}.
+{\bf TODO Rodrigo: please update acronyms in plots with those given above,
+use MRMR for MRMR... sorry, does not seem sensible to shorten this to 3 letters.}
 
-To evaluate the feature selection performances we reported
-classification metrics performing 10-fold cross-validation from one
-until the max number of features selected for each classifier solving
-each of the binary classification problem. Specifically, we reported
-Accuracy, Precision, Recall and F-Score for the true label class, that
-could be identified by the context of the problem and usually be the
-class with least samples in the data set.
+% TODO: Scott... any interesting things to point out?  
+%       Class imbalance / feature-data ratios?
+
+In this experimental study, we evaluated each feature selection
+method on a variety of binary classification problems 
+from the UCI machine learning repository \cite{Bache+Lichman:2013}.
+These datasets along with their properties are outlined in 
+Table~\ref{table:stats}.
+
+In addition, we used three different classifiers to solve each of the
+binary classifier problem. Logistic Regression (LR), SVM Linear (SVM) and Naive
+Bayes (NB) were used in the experiments and the first two are implemented
+in the LibLinear library~\cite{REF08a} and the last one is implemented in
+the Weka software~\cite{weka}.
+
+To evaluate feature selection algorithm performance, we perform 
+10-fold nested cross-validation (nesting for tuning hyperparameters of each classification
+algorithm) and evaluate accuracy, precision, and recall at each stage of
+feature selection from the first selected feature through to the maximum
+(either 50 or the number of features in the dataset, whichever is smaller).
+%and F-Score for the true label class, that
+%could be identified by the context of the problem and usually be the
+%class with least samples in the data set.
+
+In our evaluation, we wish to answer the following questions:
+Do different feature selection methods perform better with
+each classifier or on each dataset in comparison to others?
+How reliably do the different feature selection methods perform overall
+in terms of their performance distribution?
+%\item Do any dataset features seem to correlate with algorithm performance?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tbp!]
+\centering
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/BarGraphs/dataSetXFeatureSelection_avgCl/Accuracy.pdf}\\
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/BarGraphs/dataSetXFeatureSelection_avgCl/Precision.pdf}\\
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/BarGraphs/dataSetXFeatureSelection_avgCl/Recall.pdf}
+\caption{\footnotesize Performance of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.}
+\label{fig:perf_vs_dataset}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tbp!]
+\centering
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/BarGraphs/FeatureSelectionXClassifier/vote Accuracy.pdf}\\
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/BarGraphs/FeatureSelectionXClassifier/vote Precision.pdf}\\
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/BarGraphs/FeatureSelectionXClassifier/vote Recall.pdf}
+\caption{\footnotesize Performance of various feature selection algorithms per classifier, averaged across dataset and each stage of feature selection.}
+\label{fig:perf_vs_classifier}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tbp!]
+\centering
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/BoxPlot/BoxPlot1/Accuracy.pdf}\\
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/BoxPlot/BoxPlot1/Precision.pdf}\\
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/BoxPlot/BoxPlot1/Recall.pdf}
+\caption{\footnotesize Performance distribution of various feature selection algorithms with samples taken for each dataset, classifier type, and stage of feature selection.}
+\label{fig:perf_vs_fs_alg}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To answer these questions, we first start with
+Figure~\ref{fig:perf_vs_dataset}, where we evaluate the performance of
+various feature selection algorithms per dataset, averaged across
+classifier type and each stage of feature selection.  We observe...
+% TODO Scott
+
+In Figure~\ref{fig:perf_vs_classifier}, we examine how well our 
+novel feature selection algorithms HRE, HRL, HPE, HPL 
+perform vs. classifier, noting that overall performance is best
+for Naive Bayes followed by Logistic Regression and noticeably worse for
+the SVM --- it seems simply that the probabilistic nature of our feature selection
+dovetail best with classification methods that are themselves probabilistic,
+and overall best with Naive Bayes which makes the same independence assumptions.
+{\bf TODO Rodrigo: can we get bargraphs like those in FeatureSelection classifier,
+except only showing HRE, HRL, HPE, HPL *and* averaging over all datasets?
+So major group={HRE, HRL, HPE, HPL}, minor group={SVM,LR,NB} and one graph
+for each of A/P/R/F.  Also the filename should not have spaces.}
+
+Next we examine Figure~\ref{fig:perf_vs_fs_alg}, where we evaluate the
+performance distribution of various feature selection algorithms with
+samples taken for each dataset, classifier type, and stage of feature
+selection.  Here we see Y.  We observe...

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/intro.tex
Rough empirical results section

@@
 While historically, feature selection
+
+Naturally do not want to optimize for precision and recall directly (all false trivially optimizes precision, while all true trivially optimizes accuracy).
+But when selecting features for a classifier intended to maximize accuracy, we may have a secondary preference for features that improve precision (reduce false positive rate) or improve recall (reduce false negative rate).
+To this end, we remark that no previous work seems to have examined feature selection in the context of the precision-recall trade-off
+
+in well-known contingency table
+
+{\centering
+\begin{tabular}{|l||l|l|l|l|} \hline
+          &   & \multicolumn{2}{|l|}{Actual} & \\ \hline \hline
+          &   &  T & F & \#$T_P$\\ \hline
+predicted & T & TP & FP & \#$F_P$ \\ \hline
+          & F & FN & TN & \\ \hline
+          &   & \#$T_A$ & \#$F_A$ & \\ \hline
+\end{tabular}}
+
+accuracy = tp + tn / tp + fp + fn + tn
+
+precision = tp / tp + fp
+
+recall = tp / tp + fn
+
+can switch in columns, but typically predicting more false hurts recall and more true hurts precision
+
+So precision and recall become secondary objectives after accuracy... provides flexibility in feature selection that has not been explicitly considered.
+
+% Yet on other hand certain methods must have done better/wose b/c of implicit assumptions that we should analyze later.
 

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/OthersDataSet10/BarGraphs/dataSetXFeatureSelection/createBarGraph.m

@@ -1,0 +1,31 @@
+function createBarGraph(ymatrix1, xgroupsLabels, barLegends, titleName, ylabelTxt, xlabelTxt )
+%CREATEFIGURE(YMATRIX1)
+%  YMATRIX1:  bar matrix data
+
+%  Auto-generated by MATLAB on 31-Jan-2014 14:50:05
+
+% Create figure
+figure1 = figure;
+
+% Create axes
+axes1 = axes('Parent',figure1,'XTickLabel',xgroupsLabels,...
+    'XTick',1:length(xgroupsLabels));
+box(axes1,'on');
+hold(axes1,'all');
+
+% Create multiple lines using matrix input to bar
+bar1 = bar(ymatrix1,'Parent',axes1);
+
+
+% Create title
+title(titleName);
+
+% Create xlabel
+xlabel(xlabelTxt);
+
+%set legend
+legend(barLegends,'Location', 'SouthOutside');
+
+% Create ylabel
+ylabel(ylabelTxt);
+

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/OthersDataSet8/BoxPlot/BoxPlot3/GenerateBoxPlot.m

@@ -1,0 +1,73 @@
+%script to generate barGraph
+
+%clear
+clear all, close all;
+
+%xml file
+file = 'featureSelection.xml';
+
+%read the xml to struct
+data = xml2struct(file);
+
+%number of data sets
+nDS = size(data.Simulation.DataSet,2);
+
+%number of algs
+nAlg = size(data.Simulation.DataSet{1}.Classifier{1}.Metric{1}.Algorithms.Algorithm,2);
+
+
+%loop over metrics
+nM = size(data.Simulation.DataSet{1}.Classifier{1}.Metric,2);
+for m = 1:nM
+    MName = data.Simulation.DataSet{1}.Classifier{1}.Metric{m}.Attributes.name;
+    
+    %loop over classifiers
+    nCl = size(data.Simulation.DataSet{1}.Classifier,2);
+    for c = 1:nCl
+        CName = data.Simulation.DataSet{1}.Classifier{c}.Attributes.name;
+        
+        %compute average and plot
+        Y = zeros(nDS,nAlg);
+        dataSetLegends = {};
+        for d=1:nDS
+            dSName = data.Simulation.DataSet{d}.Attributes.name;
+            dataSetLegends = [dataSetLegends, cleanString(dSName)];
+            legendKeys = {};
+            
+            for alg = 1:nAlg
+                algname = data.Simulation.DataSet{d}.Classifier{1}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name;
+                legendKeys = [legendKeys, cleanString(algname)];
+                
+                %xpath expression
+                exp = strcat('//DataSet[@name="',dSName ,'"]/Classifier[@name="',CName,'"]/Metric[@name="',MName,'"]/Algorithms/Algorithm[@name="',algname,'"]/Mean');
+                
+                acc = 0.0;
+                count = 0;
+                nodeList = queryXml(exp,file);
+                for i = 1:nodeList.getLength
+                    node = nodeList.item(i-1);
+                    %convert text matrix to number matrix
+                    values = str2num( node.getFirstChild.getNodeValue);
+                    acc = acc + sum(values);
+                    count = count + length(values);
+                    %disp(str2num( node.getFirstChild.getNodeValue))
+                end;
+                Y(d,alg) = acc/count;
+            end;
+            
+            %normalize
+            Y(d,:) = Y(d,:) ./ max(Y(d,:));
+        end;
+        
[…]

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/OthersDataSet9/BoxPlot/BoxPlot2/acronym.m

@@ -1,0 +1,9 @@
+function output = acronym( input )
+  words_cell = textscan(input,'%s','delimiter',' ');
+  words      = words_cell{ : };
+  letters    = cellfun(@(x) textscan(x,'%c%*s'), words);
+  if(length(letters) > 3)
+    output = upper(letters(1:3)');
+  else
+     output = upper(letters');
+end

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/OthersDataSet8/BarGraphs/FeatureSelectionXClassifier/barweb.m

@@ -1,0 +1,197 @@
+function handles = barweb(barvalues, errors, width, groupnames, bw_title, bw_xlabel, bw_ylabel, bw_colormap, gridstatus, bw_legend, error_sides, legend_type)
+
+%
+% Usage: handles = barweb(barvalues, errors, width, groupnames, bw_title, bw_xlabel, bw_ylabel, bw_colormap, gridstatus, bw_legend, error_sides, legend_type)
+%
+% Ex: handles = barweb(my_barvalues, my_errors, [], [], [], [], [], bone, [], bw_legend, 1, 'axis')
+%
+% barweb is the m-by-n matrix of barvalues to be plotted.
+% barweb calls the MATLAB bar function and plots m groups of n bars using the width and bw_colormap parameters.
+% If you want all the bars to be the same color, then set bw_colormap equal to the RBG matrix value ie. (bw_colormap = [1 0 0] for all red bars)
+% barweb then calls the MATLAB errorbar function to draw barvalues with error bars of length error.
+% groupnames is an m-length cellstr vector of groupnames (i.e. groupnames = {'group 1'; 'group 2'}).  For no groupnames, enter [] or {}
+% The errors matrix is of the same form of the barvalues matrix, namely m group of n errors.
+% Gridstatus is either 'x','xy', 'y', or 'none' for no grid.
+% No legend will be shown if the legend paramter is not provided
+% 'error_sides = 2' plots +/- std while 'error_sides = 1' plots just + std
+% legend_type = 'axis' produces the legend along the x-axis while legend_type = 'plot' produces the standard legend.  See figure for more details
+%
+% The following default values are used if parameters are left out or skipped by using [].
+% width = 1 (0 < width < 1; widths greater than 1 will produce overlapping bars)
+% groupnames = '1', '2', ... number_of_groups
+% bw_title, bw_xlabel, bw_ylabel = []
+% bw_color_map = jet
+% gridstatus = 'none'
+% bw_legend = []
+% error_sides = 2;
+% legend_type = 'plot';
+%
[…]

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/OthersDataSet8/BarGraphs/dataSetXFeatureSelection/GenerateBarGraph.m

@@ -1,0 +1,73 @@
+%script to generate barGraph
+
+%clear 
+clear all, close all;
+
+%xml file
+file = 'featureSelection.xml';
+
+%read the xml to struct
+data = xml2struct(file);
+
+%number of data sets
+nDS = size(data.Simulation.DataSet,2);
+
+%number of algs
+nAlg = size(data.Simulation.DataSet{1}.Classifier{1}.Metric{1}.Algorithms.Algorithm,2);
+
+%loop over classifiers
+nCl = size(data.Simulation.DataSet{1}.Classifier,2);
+for c = 1:nCl
+     CName = data.Simulation.DataSet{1}.Classifier{c}.Attributes.name;
+     
+    %loop over metrics
+    nM = size(data.Simulation.DataSet{1}.Classifier{c}.Metric,2);
+    for m = 1:nM
+      MName = data.Simulation.DataSet{1}.Classifier{c}.Metric{m}.Attributes.name;
+      
+      %compute average and plot
+      Y = zeros(nDS,nAlg);
+      Error = zeros(nDS,nAlg);
+      dataSetLegends = {};
+      for d=1:nDS  
+          dSName = data.Simulation.DataSet{d}.Attributes.name;
+          dataSetLegends = [dataSetLegends, cleanString(dSName)];
+          legendKeys = {}; 
+          
+          for alg = 1:nAlg
+            algname = data.Simulation.DataSet{d}.Classifier{c}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name;
+            %xpath expression
+            exp = strcat('//DataSet[@name="',dSName ,'"]/Classifier[@name="',CName,'"]/Metric[@name="',MName,'"]/Algorithms/Algorithm[@name="',algname,'"]/Mean');
+            nodeList = queryXml(exp,file);
+            legendKeys = [legendKeys, cleanString(algname)];
+            
+            % Iterate through the nodes that are returned. but it is just
+            % one node in each interation
+            acc = 0.0;
+            count = 0;
+            samples = [];
+            for i = 1:nodeList.getLength
+                node = nodeList.item(i-1);
+                %convert text matrix to number matrix
+                values = str2num( node.getFirstChild.getNodeValue);
+                samples = [samples, values];
+                acc = acc + sum(values);
+                count = count + length(values);
+                %disp(str2num( node.getFirstChild.getNodeValue))
[…]

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/OthersDataSet9/BoxPlot/BoxPlot2/cleanString.m

@@ -1,0 +1,22 @@
+function [ S ] = cleanString( S )
+
+ 
+ S = lower(regexprep(S,'[^a-zA-Z]',' '));
+
+ skipset={'a','an','and','or','in','the'}; 
+
+
+if iscell(S)
+    S=cellfun(@(x) capitalize(x, skipset),S,'uniformoutput',false);
+else
+    skip=0;
+    Sw=regexp(S,'[ \t]','split');
+    skip(2:length(Sw))=ismember(lower(Sw(2:end)),skipset); %skip(1) is always 0
+    Sw(~skip)=cellfun(@(x) [upper(x(1)) x(2:end)],Sw(~skip),'uniformoutput',false);
+    S=sprintf('%s ',Sw{:});
+    S(end)='';
+    
+    
+end 
+end
+

### 2014-02-04  feature-selection-high-recall/FeatureSelectionProject/doc/ResultsPlot/OthersDataSets/BarGraphs/bargraph4/GenerateBarGraph.m

@@ -1,0 +1,84 @@
+%script to generate barGraph, major = feature selection, minor = classifier
+
+%clear
+clear all, close all;
+
+%xml file
+file = 'featureSelection.xml';
+
+%read the xml to struct
+data = xml2struct(file);
+
+
+
+%loop over metrics
+nM = size(data.Simulation.DataSet{1}.Classifier{1}.Metric,2);
+nCl = size(data.Simulation.DataSet{1}.Classifier,2);
+
+for m = 1:nM
+    MName = data.Simulation.DataSet{1}.Classifier{1}.Metric{m}.Attributes.name;
+    nAlg = size(data.Simulation.DataSet{1}.Classifier{1}.Metric{m}.Algorithms.Algorithm,2);
+    
+    Y = zeros(nAlg,nCl);
+    Error = zeros(nAlg,nCl);    
+    algLegend = {};
+    
+    for alg = 1:nAlg
+        algname = data.Simulation.DataSet{1}.Classifier{1}.Metric{m}.Algorithms.Algorithm{alg}.Attributes.name;
+        if(strcmpi(algname,'HIGH_REC_EXPECT_APP')|strcmpi(algname,'HIGH_REC_LOG_APP')|strcmpi(algname,'HIGH_PRE_EXPECT_APP')|strcmpi(algname,'HIGH_PRE_LOGLIK_APP'))
+            algLegend = [algLegend, cleanString(algname)];
+            classifiersLegends = {};
+            
+            %loop over classifiers
+            nCl = size(data.Simulation.DataSet{1}.Classifier,2);
+            for c = 1:nCl
+                CName = data.Simulation.DataSet{1}.Classifier{c}.Attributes.name;
+                classifiersLegends = [classifiersLegends, cleanString(CName)];
+                
+                % Iterate through the nodes that are returned. but it is just
+                % one node in each interation
+                acc = 0.0;
+                count = 0;
+                samples = [];
+                %number of data sets
+                nDS = size(data.Simulation.DataSet,2);
+                for d=1:nDS
+                    dSName = data.Simulation.DataSet{d}.Attributes.name;
+                    
+                    %xpath expression
+                    exp = strcat('//DataSet[@name="',dSName ,'"]/Classifier[@name="',CName,'"]/Metric[@name="',MName,'"]/Algorithms/Algorithm[@name="',algname,'"]/Mean');
+                    nodeList = queryXml(exp,file);
+                    
+                    
+                    for i = 1:nodeList.getLength
+                        node = nodeList.item(i-1);
[…]

### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex

@@
 The first five methods are variable rank methods and the last seven
-are subset rank methods.  {\bf TODO Rodrigo: explain variable rank
-and subset rank first.}
+are subset rank methods.
+The first five methods are variable rank methods that select variables by ranking them with some metric and the last seven are subset rank methods that assess subsets of variables and consider previous selections to decide the next selection.
 

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Empirical results update

@@
 \section{Empirical}
-In this section, we conduct experiments to study the feature selection performances of several well known methods such as Symmetrical Uncertainty Rank, Gain Ratio Rank, Information Gain Rank, Correlation Based Rank, Conditional Entropy Rank \cite{guyon_jmlr03}, Correlation-based Feature Subset Selection \cite{Hall1998},  Reliff \cite{Robnik-Sikonja2003} , mRMR \cite{peng2005} and our proposed methods: High Precision Expectation, High Precision Log likelihood, High Recall Expectation and High Recall Log likelihood.
-The first six methods are variable rank methods and the last six are subset rank methods.
 
-In these experimental study, we evaluated each feature selection method in binary classification problems such as Breast Cancer, Pima Diabetes, Heart Statlog, Spect and Vote.
-These data sets can be downloaded from UCI machine learning repository \cite{Bache+Lichman:2013}.
-In addition, we used three different classifiers to solve each of the binary classifier problem.
-Logistic Regression, SVM Linear and Naive Bayes were used in the experiments and the first two are implemented in LibLinear library \cite{REF08a} and the last one is implemented in Weka software \cite{weka}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table*}[tbp!]
+\centering
+\begin{tabular}{|l|r|r|r|r|l|} \hline
+Dataset & \# Features & \# Data & \# Features/\# Data & \% True Labels & Feature Type\\ \hline \hline 
+Breast Cancer	& 9	& 699	& 0.013	& 34 \%	& All Numeric\\ \hline
+Diabetes        & 8	& 768	& 0.010	& 35 \%	& All Numeric\\ \hline
+Heart Statlog	& 13	& 270	& 0.048	& 44 \%	& All Numeric\\ \hline
+Spect	        & 22	& 80	& 0.275 & 33 \%	& Categorical\\ \hline
+Vote	        & 16	& 435	& 0.037	& 39 \%	& Categorical\\ \hline
+Newsgroup	& 500	& 1963	& 0.255	& 49 \%	& All Binary\\ \hline
+Horse Colic	& 22	& 368	& 0.060	& 37 \%	& Categorical (16) and numeric (6)\\ \hline
+Credit-American	& 15	& 690	& 0.022	& 44 \%	& Categorical(9) and numeric (6)\\ \hline
+Credit-German	& 20	& 1000	& 0.020 & 30 \%	& Categorical (13) and Numeric (7)\\ \hline
+Hepatitis	& 19	& 155	& 0.123	& 21 \%	& Categorical (13) and Numeric (6)\\ \hline
+Ionosphere	& 34	& 351	& 0.097	& 36 \%	& All Numeric\\ \hline
+%KR-vs-KP	& 36	& 3196	& 0.011	& 48 \%	& All Categorical\\ \hline
+%Labor	        & 16	& 57	& 0.281	& 35 \%	& Categorical (8) and Numeric (8)\\ \hline
+%Mushroom	& 22	& 8124	& 0.003	& 48 \%	& All Categorical\\ \hline
+%Sick	        & 29	& 3772	& 0.008	&  6 \%	& Categorical (23) and Numeric (6)\\ \hline
+%Sonar	        & 60	& 208	& 0.288 & 47 \%	& All Numeric\\ \hline
+\end{tabular}
+\caption{\footnotesize Statistics of the various datasets evaluated in this work.}
+\label{table:stats}
+\end{table*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-To evaluate the feature selection performances we reported classification metrics performing 10-fold cross-validation from one until the max number of features selected for each classifier solving each of the binary classification problem.
-Specifically, we reported Accuracy, Precision, Recall and F-Score for the true label class, that could be identified by the context of the problem and usually be the class with least samples in the data set.
+In this section, we conduct experiments to study the feature selection
+performances of several well known methods such as Symmetrical
+Uncertainty Rank (SUR), Gain Ratio Rank (GRR), Information Gain Rank
+(IGR), Correlation Based Rank (CBR), Conditional Entropy Rank (CER)~\cite{guyon_jmlr03}, 
+Correlation-based Feature Subset Selection (CFS)~\cite{Hall1998}, 
+Reliff (R)~\cite{Robnik-Sikonja2003} , mRMR~\cite{peng2005} and our proposed 
+methods: High Recall Expectation (HRE) and High Recall Log likelihood (HRL), 
+High Precision Expectation (HPE), High Precision Log likelihood (HPL). 
+The first five methods are variable rank methods and the last seven
+are subset rank methods.
+The first five methods are variable rank methods that select variables by ranking them with some metric and the last seven are subset rank methods that assess subsets of variables and consider previous selections to decide the next selection.
+
+{\bf TODO Rodrigo: please update acronyms in plots with those given above,
+use MRMR for MRMR... sorry, does not seem sensible to shorten this to 3 letters.}
+
+% TODO: Scott... any interesting things to point out?  
+%       Class imbalance / feature-data ratios?
+
+In this experimental study, we evaluated each feature selection
+method on a variety of binary classification problems 
+from the UCI machine learning repository \cite{Bache+Lichman:2013}.
+These datasets along with their properties are outlined in 
+Table~\ref{table:stats}.
+
+In addition, we used three different classifiers to solve each of the
+binary classifier problem. Logistic Regression (LR), SVM Linear (SVM) and Naive
+Bayes (NB) were used in the experiments and the first two are implemented
+in the LibLinear library~\cite{REF08a} and the last one is implemented in
+the Weka software~\cite{weka}.
+
+To evaluate feature selection algorithm performance, we perform 
+10-fold nested cross-validation (nesting for tuning hyperparameters of each classification
+algorithm) and evaluate accuracy, precision, and recall at each stage of
+feature selection from the first selected feature through to the maximum
+(either 50 or the number of features in the dataset, whichever is smaller).
+%and F-Score for the true label class, that
+%could be identified by the context of the problem and usually be the
+%class with least samples in the data set.
+
+In our evaluation, we wish to answer the following questions:
+Do different feature selection methods perform better with
+each classifier or on each dataset in comparison to others?
+How reliably do the different feature selection methods perform overall
+in terms of their performance distribution?
+%\item Do any dataset features seem to correlate with algorithm performance?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tbp!]
+\centering
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/BarGraphs/dataSetXFeatureSelection_avgCl/Accuracy.pdf}\\
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/BarGraphs/dataSetXFeatureSelection_avgCl/Recall.pdf}
+\caption{\footnotesize Performance of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.}
+\label{fig:perf_vs_dataset}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tbp!]
+\centering
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/BarGraphs/bargraph4/Accuracy.pdf}\\
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/BarGraphs/bargraph4/Recall.pdf}
+\caption{\footnotesize Performance of various feature selection algorithms per classifier, averaged across dataset and each stage of feature selection.}
+\label{fig:perf_vs_classifier}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tbp!]
+\centering
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/LineGraphs/FullResultsWithoutNoutOfK/Spect Logistic Regression Recall.pdf}
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/LineGraphs/FullResultsWithoutNoutOfK/Spect Naive Bayes Recall.pdf}\\
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/LineGraphs/FullResultsWithoutNoutOfK/Newsgroup Logistic Regression Recall.pdf}
+\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/LineGraphs/FullResultsWithoutNoutOfK/Newsgroup Naive Bayes Recall.pdf}
+\caption{\footnotesize Performance distribution of various feature selection algorithms with samples taken for each dataset, classifier type, and stage of feature selection.}
+\label{fig:perf_vs_fs_alg}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To answer these questions, we first start with
+Figure~\ref{fig:perf_vs_dataset}, where we evaluate the performance of
+various feature selection algorithms per dataset, averaged across
+classifier type and each stage of feature selection.  We observe...
+% TODO Scott
+
+In Figure~\ref{fig:perf_vs_classifier}, we examine how well our 
+novel feature selection algorithms HRE, HRL, HPE, HPL 
+perform vs. classifier, noting that overall performance is best
+for Naive Bayes followed by Logistic Regression and noticeably worse for
+the SVM --- it seems simply that the probabilistic nature of our feature selection
+dovetail best with classification methods that are themselves probabilistic,
+and overall best with Naive Bayes which makes the same independence assumptions.
+{\bf TODO Rodrigo: can we get bargraphs like those in FeatureSelection classifier,
+except only showing HRE, HRL, HPE, HPL *and* averaging over all datasets?
+So major group={HRE, HRL, HPE, HPL}, minor group={SVM,LR,NB} and one graph
+for each of A/P/R/F.  Also the filename should not have spaces.}
+
+Next we examine Figure~\ref{fig:perf_vs_fs_alg}, where we evaluate the
+performance distribution of various feature selection algorithms with
+samples taken for each dataset, classifier type, and stage of feature
+selection.  Here we see Y.  We observe...

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/intro.tex
Empirical results update

@@
 
+Naturally do not want to optimize for precision and recall directly (all false trivially optimizes precision, while all true trivially optimizes accuracy).
+But when selecting features for a classifier intended to maximize accuracy, we may have a secondary preference for features that improve precision (reduce false positive rate) or improve recall (reduce false negative rate).
+To this end, we remark that no previous work seems to have examined feature selection in the context of the precision-recall trade-off/
+
+% Part of the reason is that previous feature selection has not been specific to classification whereas precision/recall are
+
+% Consider the feature set jointly, weighted voting model
+
+% We get a heavier weighting of effect of data... a feature that pushes more things to their
+% class improves recall... so summation is reason for recall.  Each data gets it's own feature vote.
+
+% We get best performance with prob. classifiers, due to alignment of assumptions
+
+% We get best results with conjunction on high ratio of features to data
+% - conjunction forces agreement and reduces noise
+% - summation encourages coverage of the data
+% ... this works best when lot's of features, let data vote, but get probabilistic agreement
+
+% Show anecdotal results for Newsgroup and Spect logistic... we're best across both
+
+in well-known contingency table
+
+\begin{center}
+\begin{tabular}{l|l|l|} 
+\multicolumn{1}{l}{} &  \multicolumn{1}{l}{Label T} & \multicolumn{1}{l}{Label F} \\ \cline{2-3}
+Predicted T & TP & FP \\ \cline{2-3}
+Predicted F & FN & TN \\ \cline{2-3}
+%Predicted T & TP & FP & \#$T_P$ \\ \cline{2-3}
+%Predicted F & FN & TN & \#$F_P$ \\ \cline{2-3}
+%          &   & \#$T_A$ & \#$F_A$ & \\ \cline{2-3}
+\end{tabular}
+\end{center}
+
+accuracy = tp + tn / tp + fp + fn + tn
+
+precision = tp / tp + fp
+
+recall = tp / tp + fn
+
+can switch in columns, but typically predicting more false hurts recall and more true hurts precision
+
+So precision and recall become secondary objectives after accuracy... provides flexibility in feature selection that has not been explicitly considered.
+
+% Yet on other hand certain methods must have done better/wose b/c of implicit assumptions that we should analyze later.
+
 \COMMENT
+key insight: literature suggests redundancy is bad idea, but in fact, it is critical for precision (implies agreement)
+
+how to strongly justify the model and objectives we use?  voting?
+
+Good discussion: http://jmlr.org/papers/volume13/brown12a/brown12a.pdf
+
 - Feature selection motivations

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/background.tex
Update

--- 2014-01-31  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/intro.tex
@@
-\section{Introduction}
+\section{Background}
 
-Feature selection~\cite{guyon_jmlr03}
+in well-known contingency table
 
-While historically, feature selection
+\begin{center}
+\begin{tabular}{l|l|l|} 
+\multicolumn{1}{l}{} &  \multicolumn{1}{l}{Label T} & \multicolumn{1}{l}{Label F} \\ \cline{2-3}
+Predicted T & TP & FP \\ \cline{2-3}
+Predicted F & FN & TN \\ \cline{2-3}
+%Predicted T & TP & FP & \#$T_P$ \\ \cline{2-3}
+%Predicted F & FN & TN & \#$F_P$ \\ \cline{2-3}
+%          &   & \#$T_A$ & \#$F_A$ & \\ \cline{2-3}
+\end{tabular}
+\end{center}
 
-\COMMENT
-- Feature selection motivations
-** too little data (e.g., bioinformatics, or text with few labels)
-** features costly to evaluate
-** explainability
-** minimize feature elicitation for future data collection (questionnaires, medical tests -- blood tests)
-** computation / Big Data
-** mobile devices (RAM, computation)
-** linear speed (LibLinear 1000x faster than LibSVM)
-** poly kernels without kernelized approach without loss of evaluation efficiency
-** need to argue SVM/logistic L1 not always best... not always logistic regression/SVM problem, also eval efficient, but training not, so 
-inefficient for large-scale or resource-constrained training... show empirical better than L1, also more control over amount of feature 
-selection (need a tool that implements full regularization path -- constrains optimization method)
+accuracy = tp + tn / tp + fp + fn + tn
 
-Filtering-based feature selection methods ...
+precision = tp / tp + fp
 
-"A Probabilistic Model for High Precision and Recall Feature Selection"
-"A Probabilistic Model/Perspective of Feature Selection for Trading off Precision and Recall"
-Conventional feature selection methods choose informative features or feature sets and empirically lead to good accuracy improvements, but 
-few focus directly on precision or recall (or mention that they're method is actually biased towards one vs. other).  In this paper we 
-propose a new probabilistic classification model based on a logical or weighted voting approach that directly encourages feature selection 
-according to the continuum between pure precision and pure recall.  Supports filter, wrapper, and embedded approaches (where we create a 
-new high precision/recall variant of Naive Bayes).  Suggests a way of analyzing existing approaches and identifying what they are 
-optimizing.  In fact, MI (or other independent greedy methods) appear to be maximizing precision while MRMR appears to maximizing recall.
-- Idea: we have a generative model... write down how we want features to generate the class... now the only leverage we have is to select 
-features to maximize expected (log) likelihood
-** if we use an aggregation function that allows any feature to falsify (noisy-and), we encourage agreement (precision)
-** if we use an aggregation function that allows any feature to tip the vote to true (noisy-or), we encourage coverage (recall)... noisy-
-max not multiclass unless we're ordinal (I think)
-** we can trade off precision and recall by requiring n-out-of-k features, n=k/2 is majority vote... does this correspond to F-score or 
-accuracy (can we compare beta & k, 3d plot showing F_beta for k?)
-** of course probabilistic since class predictions are latent so we get a soft version (noisy-or, noisy-and) ... clearer derivation of 
-noisy-or, noisy-max etc. than direct specification?  I think so.
-** maximizing overall likelihood so will try to get features that correctly classify more of the data (especially where votes of others are 
-weak)
-** can do a probabilistic analysis of the 4x4 contigency table
-** a new naive classifier, how do we do overall as a naive classifier?  accuracy will tell us this, can tune k though for whatever metric 
-we care about!  interesting as a classifier since we look at total probability mass of at least k votes... what does this buy us over 
-standard naive Bayes?  Should evaluate.
-==> is there a way to do DP for dynamic programming for Bayesian model averaging over all class inclusions/exclusions?
-... for each feature can leave in or leave out -- if leave out get 1, otherwise probability (sum over all models, probability of prediction 
-* normalized likelihood of that model vs. all others -- add in feature one at a time?)
-... would this also work for query expansion?  some sort of DP MAP query for jointly most useful retrieval set?
-** online learning... discrete parameter
-** spectrum/contiuum of tradeoffs for feature selection
-- To explore: correlated features, diversity of features (MRMR) -- good for recall
-- Filter method
-- Wrapper method
-- Embedded method - use a naive independence classifier
-  (do we unify view for embedded method?  we could maximize likelihood for voting classifier	
-- Computational tricks worth noting (extreme cases and 1- trick for probabilities, DP)
-- In general we want to optimize precision/recall tradeoff (extreme solutions are trivial), n-out-of-k interpolates F-score... really?  Can 
-we show a strong mathematical connection?
-- Intepretation as a voting classifier... then majority vote is k/2-call@k
-** precision, recall, what is f-score?  pure precision/recall not ideal
-** reinterpretation of existing methods as focusing more on precision (MI) or recall (MRMR)
-** does trade-off between precision and recall yield an F-Beta score
-** should probably write out a direct classification approach with y being I[y = y_1 v ... v y_k] and then maximize E[p(y*|...)] or 
-likelihood.  This model supports all view in the proposed paper.  Which is better?
-** will get the effect that optimization only matters when new feature can swing the vote... for recall this will be false negatives, for 
-recall this will be false positives, for majority vote, it will be borderline cases.
-** recall encourages diversity... explains why diverse feature selection methods don't always improve accuracy.  If we wanted precision, we 
-don't mind redundancy, in fact we encourage it.
-** start with and, or, generalize to weighted voting scheme
-** an information-theoretic intepretation?  expectation over data of log probability should yield this
-** what sort of similarity metrics do we get?
-** need to motivate directly that the logical/voting function encourages precision vs. recall... that with disjunction, new features will 
-only address correcting false negatives and likewise for precision and conjunction and correcting false positives
-** what sort of features do we select... analyze 2 newsgroups
-***
-- A new naive independence voting-based classifier with tunable objective and objective-oriented feature selection via a voting scheme
-- A new naive independence voting-based classifier for the precision/recall trade-off
-** feature selection for cases other than accuracy!
-** efficient, supports different objectives from precision to recall and in-between (F-score?)... is the objective just for feature 
-selection?
-** directly supports feature selection... important in independent classifiers
-** supports online computation... and online feature selection scoring
-** supports discrete and Gaussian models
-*** we could also modify the model to make the logical function (weighted voting explicit)... can marginalize this out... in this way the 
-prediction matches feature selection
-** learning parameters -- for directed model, as usual
-** how to work out argmax_y* P(y*|...) -- looks like its just going to multiply probabilities for each class -- is this another view of 
-Naive bayes
-** how to work out feature selection -- y* observed...
-*** could choose fb to maximize logical function in expectation... expected correctness?
-*** could choose fb to maximize likelihood -- would be log version of above with logical function for hidden variable
-*** after doing extreme cases, allow general voting, not just all-or-none
-
-*** training recall/precision directly a bad idea... hurts accuracy, but can select features so as to focus on one of these
-*** we focus on the filter method in this work
-\ENDCOMMENT
+recall = tp / tp + fn

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/intro.tex
Update

@@
 
-Feature selection~\cite{guyon_jmlr03}
+Feature selection is important in many practical supervised learning
+settings to address computational constraints (e.g., in large-scale or
+online learning) or to prevent overfitting when the data may be
+high-dimensional but contain relatively few samples (e.g., as may
+occur in bioinformatics domains where features are abundant but data
+is costly to obtain)~\cite{guyon_jmlr03}.
+
+While a wide variety of feature selection methods have been proposed
+in the literature, little research seems to focus on feature selection
+specifically targeted to improve recall (minimization of false
+negatives) in binary classification.  One reason for this is simply
+that most feature selection methods are agnostic to the particular
+supervised learning task -- applying to tasks from classification to
+regression -- and hence are not focused on performance properties
+specific to binary classifiers.  Yet, recall is an important aspect of
+many binary classification problems (e.g., minimizing false negatives
+in the identification of cancerous tumors) and it is critical to have
+feature selection algorithms that are targeted to maintain high recall.
+
+Naturally though, it would not make sense for a classifier or feature
+selection method to focus on recall alone since the classifier which
+always predicts \emph{true} (independent of the data) obtains optimal
+recall performance.  To trade off precision with recall in order to
+maintain high accuracy, one often uses a geometric average of the
+two instead (known as F-score) but in practice most classifiers directly
+optimize accuracy or some surrogate, e.g., a convex surrogate of 0-1
+loss as in the SVM or maximum (conditional) likelihood as in Naive
+Bayes or logistic regression.  So how can one achieve a high recall
+SVM, Naive Bayes, or logistic regression classifier that already has
+a
+
+prevent this solution
+
+In this paper we propose a novel probabilistic voting model of feature
+selection and argue that choosing features so as to maximize
+likelihood objectives w.r.t. this model provides an effective method
+for high recall feature selection.  For each objective, we derive an
+efficient formula for feature selection in the filtering framework
+(i.e., greedy forward selection) and we empirically compare the
+resulting feature selection criteria to a wide variety of existing
+methods.  Results show that our high recall feature selection approach
+does indeed improve recall with improvements noticeable when there is
+a high feature to data ratio.  Such results provide a novel and
+efficient feature selection algorithm to target high-recall
+classification tasks.
+
+Feature selection
 
@@
 % Show anecdotal results for Newsgroup and Spect logistic... we're best across both
-
-in well-known contingency table
-
-\begin{center}
-\begin{tabular}{l|l|l|} 
-\multicolumn{1}{l}{} &  \multicolumn{1}{l}{Label T} & \multicolumn{1}{l}{Label F} \\ \cline{2-3}
-Predicted T & TP & FP \\ \cline{2-3}
-Predicted F & FN & TN \\ \cline{2-3}
-%Predicted T & TP & FP & \#$T_P$ \\ \cline{2-3}
-%Predicted F & FN & TN & \#$F_P$ \\ \cline{2-3}
-%          &   & \#$T_A$ & \#$F_A$ & \\ \cline{2-3}
-\end{tabular}
-\end{center}
-
-accuracy = tp + tn / tp + fp + fn + tn
-
-precision = tp / tp + fp
-
-recall = tp / tp + fn
 

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/abstract.tex
Update

@@
-A variety of conventional feature selection methods choose informative
-features or feature sets and empirically lead to good accuracy
-improvements, but few focus on feature selection w.r.t.\ specific loss
-functions; in particular, there seems to be little work on feature
-selection for classifiers if a secondary objective after accuracy is
-either precision or recall.  In this paper we propose a novel
-probabilistic model of feature selection based on a probabilistic
-voting model and argue that MAP inference w.r.t. to two extreme
-objectives in this model yield respective high precision and high
-recall feature selection approaches.  We derive an efficient formula
-for feature selection in this model using the filtering framework and
-empirically compare to a wide variety of existing filtering-based
-feature selection methods.  Results show that our high precision and
-high recall feature selection approaches do reliably improve these
-respective objectives.  Furthermore, our modeling framework provides
-us with a way to interpret existing feature selection methods and
-suggests that the use of greedy approaches (such as mutual
-information) appear to maximize precision while diversity-based
-approaches (such as MRMR) appear to maximize recall, hence providing
-us with a framework for reinterpreting the loss functions implicitly
-targeted by existing feature selection methods.
+Feature selection is important in many practical supervised learning
+settings to address computational constraints or to prevent
+overfitting when the data may be high-dimensional but contain
+relatively few samples.  While a wide variety of feature selection
+methods have been proposed in the literature, little research seems to
+focus on feature selection specifically targeted to improve recall in
+the case of binary classification.  In this paper we propose a novel
+probabilistic voting model of feature selection and argue that
+choosing features so as to maximize likelihood objectives w.r.t. this
+model provides an effective method for high recall feature selection.
+For each objective, we derive an efficient formula for feature
+selection in the filtering framework (i.e., greedy forward selection)
+and we empirically compare the resulting feature selection criteria to
+a wide variety of existing methods.  Results show that our high recall
+feature selection approach does indeed improve recall with
+improvements noticeable when there is a high feature to data ratio.
+Such results provide a novel and efficient feature selection algorithm
+to target high-recall classification tasks.
+
+%Furthermore, our modeling framework provides us with a way to
+%interpret existing feature selection methods and suggests that the
+%use of greedy approaches (such as mutual information) appear to
+%maximize precision while diversity-based approaches (such as MRMR)
+%appear to maximize recall, hence providing us with a framework for
+%reinterpreting the loss functions implicitly targeted by existing
+%feature selection methods.
+
+% could look at class balance
+% what other feature properties?
+
+% may want to mention why P/R important... depends on what is
+% important (more costly for false positives or false negatives)
+% and accuracy easy to optimize in imbalanced cases

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/related_work.tex

@@
 wrapper methods, such as SVM-RFE \cite{guyon2002gene}, select features
-by evaluating theit usefulness to a given classifier, filter methods
+by evaluating their usefulness to a given classifier, filter methods
 evaluate feature subsets according to certain properties of
@@
 features according to their linear correlation with the output,
-i.e.\ Pearson's $r.$ More sophisticated ranking methods to which we
-compared our model include:
+i.e.\ Pearson's $r.$ More sophisticated ranking methods include:
 \begin{enumerate}
-\item The conditional entropy of class $Y$ given feature $X$,
+\item The conditional entropy of class $Y$ given feature $X,$
   i.e.\ $H\left(Y|X\right),$ quantifies the amount of information in
-  $Y$ that is not provided by $X.$ Substracting $H\left(Y|X\right)$
+  $Y$ that is not provided by $X.$ Subtracting $H\left(Y|X\right)$
   from the entropy of class $Y,$ the information gain of class $Y$
@@
   i.e.\ $\frac{I\left(X;Y\right)}{H\left(X\right)}.$
-\item The summetric uncertainty between feature $X$ and class $Y$
+\item The symmetric uncertainty between feature $X$ and class $Y$
   measures the amount of redundancy between them. It is defined as
@@
 
-The only subset algorithm to which we compared our work is MRMR
-\cite{peng2005}. MRMR is an information-theory-based method
-that not only maximises the relevance of selected features to the
-supervised output class, but also minimises the redundancy among
-selected features. Different search strategies can be applied using
-MRMR as heuristics.
+Correlation based subset \cite{Hall1998} is an extension
+of Pearson's $r$ to subset methods. It measures the linear correlation
+between each pair of selected features in addition to the correlation
+between selected features and the output class. The other subset
+algorithm to which we compared our work is MRMR \cite{peng2005}.
+MRMR is an information-theory-based method that not only maximises
+the relevance of selected features to the supervised output class,
+but also minimises the redundancy among selected features. Different
+search strategies can be applied using these two algorithms as
+heuristics.
 

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/derivations/Derivation.tex

--- 2014-01-31 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/derivations/Derivation.tex
@@
 
-\subsection{Recall case}
+\subsection{Recall}
 In order to select the subset of features providing high recall binary classifier we need at least one $y^d_i$ to predict true.
@@
 \begin{align}
-f_k^*&\equiv\operatorname*{arg\,max}_{f_k}\,log\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
+f_k^*&\equiv\operatorname*{arg\,max}_{f_k}\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
+&=\operatorname*{arg\,max}_{f_k}\,log\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
 &=\operatorname*{arg\,max}_{f_k}\sum_{d\in D}log\left(\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\right)\nonumber\\
@@
 
-Since $\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)$ is exactly the same as the result in the expectation case, and the logarithm is a monotonous function, the choice of likelihood instead of expectation has no further affect on the algorithm.
+Since $\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)$ is exactly the same as the result in the expectation case except the logarithm, which is a monotonous function, the choice of likelihood instead of expectation has no further affect on the algorithm.
 \end{document}

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/background.tex
Current version

@@
-\section{Background}
+\section{Classification and Feature Selection}
 
-in well-known contingency table
+In this section, we briefly define the task of binary classification
+along with standard definitions of performance metrics we may wish 
+to optimize.  We then follow this by a discussion of feature selection and
+existing criteria proposed in the literature.
 
+In the binary classification task, we assume we are given data $D = \{
+(\vec{x}^d, y^d) \}$ consisting of pairs of real-valued raw 
+feature vectors $\vec{x}^d \in \mathbb{R}^n$
+of length $n$ (e.g., counts of $n$ different words in a document) and
+\emph{actual} binary class label $y^d \in \{ 0 (\mathrm{false}), 1 (\mathrm{true}) \}$ (where
+we often write F for false and T for true).
+A binary classifier is a function $C: \vec{x}^d \to y^d$ such that given
+a new unlabeled raw feature vector, $C(\vec{x}^d)$ produces a \emph{predicted}
+classification.
+
+Given a trained classifier $C$ and a dataset $D$, we can build the 
+well-known contingency table
 \begin{center}
 \begin{tabular}{l|l|l|} 
-\multicolumn{1}{l}{} &  \multicolumn{1}{l}{Label T} & \multicolumn{1}{l}{Label F} \\ \cline{2-3}
+\multicolumn{1}{l}{} &  \multicolumn{1}{l}{Actual T} & \multicolumn{1}{l}{Actual F} \\ \cline{2-3}
 Predicted T & TP & FP \\ \cline{2-3}
@@
 \end{center}
+where each of the four entries
 
-accuracy = tp + tn / tp + fp + fn + tn
-
-precision = tp / tp + fp
-
-recall = tp / tp + fn
+\begin{align*}
+\textrm{Accuracy}  & = \frac{TP + TN}{TP + FP + FN + TN}
+\textrm{Precision} & = \frac{TP}{TP + FP}
+\textrm{Recall}    & = \frac{TP}{TP + FN}
+\end{align*}

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Current version

@@
 Newsgroup	& 500	& 1963	& 0.255	& 49 \%	& All Binary\\ \hline
-%Horse Colic	& 22	& 368	& 0.060	& 37 \%	& Categorical (16) and numeric (6)\\ \hline
-%Credit-American	& 15	& 690	& 0.022	& 44 \%	& Categorical(9) and numeric (6)\\ \hline
-%Credit-German	& 20	& 1000	& 0.020 & 30 \%	& Categorical (13) and Numeric (7)\\ \hline
-%Hepatitis	& 19	& 155	& 0.123	& 21 \%	& Categorical (13) and Numeric (6)\\ \hline
-%Ionosphere	& 34	& 351	& 0.097	& 36 \%	& All Numeric\\ \hline
+Horse Colic	& 22	& 368	& 0.060	& 37 \%	& Categorical (16) and numeric (6)\\ \hline
+Credit-American	& 15	& 690	& 0.022	& 44 \%	& Categorical(9) and numeric (6)\\ \hline
+Credit-German	& 20	& 1000	& 0.020 & 30 \%	& Categorical (13) and Numeric (7)\\ \hline
+Hepatitis	& 19	& 155	& 0.123	& 21 \%	& Categorical (13) and Numeric (6)\\ \hline
+Ionosphere	& 34	& 351	& 0.097	& 36 \%	& All Numeric\\ \hline
 %KR-vs-KP	& 36	& 3196	& 0.011	& 48 \%	& All Categorical\\ \hline
@@
 \centering
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/BarGraphs/dataSetXFeatureSelection_avgCl/Accuracy.pdf}\\
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/BarGraphs/dataSetXFeatureSelection_avgCl/Precision.pdf}\\
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/BarGraphs/dataSetXFeatureSelection_avgCl/Recall.pdf}
+\includegraphics[width=0.25\textwidth]{./figures/dataset_perf/Accuracy.pdf}\includegraphics[width=0.05\textwidth]{./figures/dataset_perf/legend.PNG}\\
+\includegraphics[width=0.25\textwidth]{./figures/dataset_perf/Recall.pdf}
 \caption{\footnotesize Performance of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.}
@@
 \centering
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/BarGraphs/FeatureSelectionXClassifier/vote Accuracy.pdf}\\
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/BarGraphs/FeatureSelectionXClassifier/vote Precision.pdf}\\
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/BarGraphs/FeatureSelectionXClassifier/vote Recall.pdf}
+\includegraphics[width=0.9\textwidth]{./figures/class_perf/Accuracy.pdf}\\
+\includegraphics[width=0.9\textwidth]{./figures/class_perf/Recall.pdf}
 \caption{\footnotesize Performance of various feature selection algorithms per classifier, averaged across dataset and each stage of feature selection.}
@@
 \centering
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/BoxPlot/BoxPlot1/Accuracy.pdf}\\
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/BoxPlot/BoxPlot1/Precision.pdf}\\
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/BoxPlot/BoxPlot1/Recall.pdf}
+\includegraphics[width=0.45\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall.pdf}
+\includegraphics[width=0.45\textwidth]{./figures/linegraphs/SpectNaiveBayesRecall.pdf}\\
+\includegraphics[width=0.45\textwidth]{./figures/linegraphs/NewsgroupLogisticRegressionRecall.pdf}
+\includegraphics[width=0.45\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall.pdf}
 \caption{\footnotesize Performance distribution of various feature selection algorithms with samples taken for each dataset, classifier type, and stage of feature selection.}

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/intro.tex
Current version

--- 2014-02-03 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/intro.tex
@@
 
-Feature selection~\cite{guyon_jmlr03}
+Feature selection is important in many practical supervised learning
+settings to address computational constraints (e.g., in large-scale or
+online learning) or to prevent overfitting when the data may be
+high-dimensional but contain relatively few samples (e.g., as may
+occur in medical or bioinformatics domains where features are abundant
+but data is costly to obtain)~\cite{guyon_jmlr03}.
 
-While historically, feature selection
+While a wide variety of feature selection methods have been proposed
+in the literature, little research seems to focus on feature selection
+specifically targeted to improve recall (minimization of false
+negatives) in binary classification.  One reason for this is simply
+that most feature selection methods are agnostic to the particular
+supervised learning task -- applying to tasks from classification to
+regression -- and hence are not focused on performance properties
+specific to binary classifiers.  Yet, recall is an important aspect of
+many binary classification problems (e.g., minimizing false negatives
+in the identification of cancerous tumors) and it is critical to have
+feature selection algorithms that are targeted to maintain high recall.
+
+Naturally though, it would not make sense for a classifier or feature
+selection method to focus on recall alone since the classifier which
+always predicts \emph{true} (independent of the data) obtains optimal
+recall performance.  To trade off precision with recall in order to
+maintain high accuracy, one often uses a geometric average of the two
+instead (known as F-score) but in practice most classifiers directly
+optimize accuracy or some surrogate, e.g., a convex surrogate of 0-1
+loss as in the SVM or maximum (conditional) likelihood as in Naive
+Bayes or logistic regression.  So how can one achieve a high recall
+SVM, Naive Bayes, or logistic regression classifier that already has a
+well-defined accuracy-focused optimization criterion?  The idea we
+pursue in this paper is that feature selection can help modulate the
+recall performance of existing classifiers by encouraging selection of
+features that cover more of the true cases in the data (hence
+discouraging false negatives).
+
+In this paper we propose a novel probabilistic voting model of feature
+selection with the intent of encouraging false negative reduction
+while still focusing on accuracy.  We argue that choosing features so
+as to maximize likelihood objectives w.r.t. this model provides an
+effective method for high recall feature selection.  Specifically, for
+each objective, we derive an efficient formula for feature selection
+in the filtering framework (i.e., greedy forward selection) and we
+empirically compare the resulting feature selection criteria to a wide
+variety of existing methods.
+
+Our results demonstrate that our high recall feature selection
+approach does indeed improve recall with improvements noticeable when
+there is a high feature to data ratio.  Such results provide a novel
+and efficient feature selection algorithm to target high-recall
+classification tasks.
+% TODO: elaborate more
 
 \COMMENT
+
+% Consider the feature set jointly, weighted voting model
+
+% We get a heavier weighting of effect of data... a feature that pushes more things to their
+% class improves recall... so summation is reason for recall.  Each data gets it's own feature vote.
+
+% We get best performance with prob. classifiers, due to alignment of assumptions
+
+% We get best results with conjunction on high ratio of features to data
+% - conjunction forces agreement and reduces noise
+% - summation encourages coverage of the data
+% ... this works best when lot's of features, let data vote, but get probabilistic agreement
+
+% Show anecdotal results for Newsgroup and Spect logistic... we're best across both
+
+%can switch in columns, but typically predicting more false hurts recall and more true hurts precision
+
+%So precision and recall become secondary objectives after accuracy... provides flexibility in feature selection that has not been explicitly considered.
+
+% Yet on other hand certain methods must have done better/wose b/c of implicit assumptions that we should analyze later.
+
 key insight: literature suggests redundancy is bad idea, but in fact, it is critical for precision (implies agreement)

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Current version

@@
 \begin{figure*}[tbp!]
-\centering
-\includegraphics[width=0.25\textwidth]{./figures/dataset_perf/Accuracy.pdf}\includegraphics[width=0.05\textwidth]{./figures/dataset_perf/legend.PNG}\\
-\includegraphics[width=0.25\textwidth]{./figures/dataset_perf/Recall.pdf}
+\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Accuracy.pdf}\vspace{-20mm}\includegraphics[width=0.10\textwidth]{./figures/dataset_perf/legend.PNG}\\
+\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Recall.pdf}
 \caption{\footnotesize Performance of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.}

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/background.tex
Updated empirical results

@@
 (\vec{x}^d, y^d) \}$ consisting of pairs of real-valued raw 
-feature vectors $\vec{x}^d \in \mathbb{R}^n$
-of length $n$ (e.g., counts of $n$ different words in a document) and
+input vectors $\vec{x}^d \in \mathbb{R}^n$
+of length $n$ (e.g., the results of $n$ different medical tests) and
 \emph{actual} binary class label $y^d \in \{ 0 (\mathrm{false}), 1 (\mathrm{true}) \}$ (where
@@
 \end{center}
-where each of the four entries
-
+where the four entries represent the counts of true positives (TP), false positives (FP), false negatives (FN)
+and true negatives (TN) and sum to the 
+total amount of data (i.e., $\mathrm{TP} + \mathrm{FP} + \mathrm{FN} + \mathrm{TN} = |D|$).
+Each table entry represents the count of data for which the respective row matched the 
+predicted classification $C(\vec{x}^d)$ and the respective column matched the actual label $y^d$.
+Given these definitions, we can easily define 
 \begin{align*}
 \textrm{Accuracy}  & = \frac{TP + TN}{TP + FP + FN + TN}
-\textrm{Precision} & = \frac{TP}{TP + FP}
+%\textrm{Precision} & = \frac{TP}{TP + FP}
 \textrm{Recall}    & = \frac{TP}{TP + FN}
 \end{align*}
+where accuracy represents the overall fraction of correct classification, but recall
+represents the overall fraction of true labeled data that has been classified as
+true (i.e., recalled).  For somewhat rare events such as medical diagnosis of cancer,
+we certainly care about accuracy, but we may also want to place additional emphasis
+on recall performance so as to avoid the occurrence of false negatives (cases of cancer
+that were missed by the classifier).  Of course false positives are also a problem,
+but additional tests would rule these out and hence not as critical of a classification
+failure as missing a potential cancer diagnosis.
+
+Previously we did not specify exactly how $C(\vec{x}^d)$ learns from the raw data
+$\vec{x}^d$.  In general, practitioners often process the raw input vectors
+$\vec{x}^d$ into a subset of features that we'll denote $f_1,\ldots,f_k$.  Whereas
+the raw input may consist of the results of individual tests, a feature $f_i \in \mathbb{R}$
+may represent some nonlinear function of one or more tests deemed to be relevant to
+the classification task.  Hence we might more appropriately write a classifier
+as $C(\vec{x}^d,f_1,\ldots,f_k)$ to represent the raw input data and the features
+of the data that the classifier may use.
+In the case of high-dimensional data or few data samples,
+we may wish to limit the set of features generated to improve classifier performance
+and this is the task of feature selection --- select $\{f_1,\ldots,f_k\}$ to optimize
+performance.  There are already a variety of feature selection methods that we outline
+next.

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Updated empirical results

@@
 \begin{figure*}[tbp!]
-\centering
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/BarGraphs/dataSetXFeatureSelection_avgCl/Accuracy.pdf}\\
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/BarGraphs/dataSetXFeatureSelection_avgCl/Recall.pdf}
+\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Accuracy.pdf}\\
+\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Recall.pdf}
+\includegraphics[width=0.10\textwidth]{./figures/dataset_perf/legend.PNG}
 \caption{\footnotesize Performance of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.}
@@
 \centering
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/BarGraphs/bargraph4/Accuracy.pdf}\\
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/BarGraphs/bargraph4/Recall.pdf}
+\includegraphics[width=0.42\textwidth]{./figures/class_perf/Accuracy.pdf}
+\includegraphics[width=0.42\textwidth]{./figures/class_perf/Recall.pdf}
+\includegraphics[width=0.15\textwidth]{./figures/class_perf/legend.PNG}
 \caption{\footnotesize Performance of various feature selection algorithms per classifier, averaged across dataset and each stage of feature selection.}
@@
 \centering
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/LineGraphs/FullResultsWithoutNoutOfK/Spect Logistic Regression Recall.pdf}
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/LineGraphs/FullResultsWithoutNoutOfK/Spect Naive Bayes Recall.pdf}\\
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/LineGraphs/FullResultsWithoutNoutOfK/Newsgroup Logistic Regression Recall.pdf}
-\includegraphics[width=0.35\textwidth]{../ResultsPlot/OthersDataSets/LineGraphs/FullResultsWithoutNoutOfK/Newsgroup Naive Bayes Recall.pdf}
+\includegraphics[width=0.45\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall.pdf}
+\includegraphics[width=0.45\textwidth]{./figures/linegraphs/SpectNaiveBayesRecall.pdf}\\
+\includegraphics[width=0.45\textwidth]{./figures/linegraphs/NewsgroupLogisticRegressionRecall.pdf}
+\includegraphics[width=0.45\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall.pdf}
 \caption{\footnotesize Performance distribution of various feature selection algorithms with samples taken for each dataset, classifier type, and stage of feature selection.}

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Current version

@@
 Dataset & \# Features & \# Data & \# Features/\# Data & \% True Labels & Feature Type\\ \hline \hline 
-Breast Cancer	& 9	& 699	& 0.013	& 34 \%	& All Numeric\\ \hline
-Diabetes        & 8	& 768	& 0.010	& 35 \%	& All Numeric\\ \hline
-Heart Statlog	& 13	& 270	& 0.048	& 44 \%	& All Numeric\\ \hline
-Spect	        & 22	& 80	& 0.275 & 33 \%	& Categorical\\ \hline
-Vote	        & 16	& 435	& 0.037	& 39 \%	& Categorical\\ \hline
-Newsgroup	& 500	& 1963	& 0.255	& 49 \%	& All Binary\\ \hline
-Horse Colic	& 22	& 368	& 0.060	& 37 \%	& Categorical (16) and numeric (6)\\ \hline
-Credit-American	& 15	& 690	& 0.022	& 44 \%	& Categorical(9) and numeric (6)\\ \hline
-Credit-German	& 20	& 1000	& 0.020 & 30 \%	& Categorical (13) and Numeric (7)\\ \hline
-Hepatitis	& 19	& 155	& 0.123	& 21 \%	& Categorical (13) and Numeric (6)\\ \hline
-Ionosphere	& 34	& 351	& 0.097	& 36 \%	& All Numeric\\ \hline
+Breast Cancer(BC)	& 9	& 699	& 0.013	& 34 \%	& All Numeric\\ \hline
+Diabetes(D)        & 8	& 768	& 0.010	& 35 \%	& All Numeric\\ \hline
+Heart Statlog(HS)	& 13	& 270	& 0.048	& 44 \%	& All Numeric\\ \hline
+Spect(S)	        & 22	& 80	& 0.275 & 33 \%	& Categorical\\ \hline
+Vote(V)	        & 16	& 435	& 0.037	& 39 \%	& Categorical\\ \hline
+Newsgroup(NG)	& 500	& 1963	& 0.255	& 49 \%	& All Binary\\ \hline
+Horse Colic(HC)	& 22	& 368	& 0.060	& 37 \%	& Categorical (16) and numeric (6)\\ \hline
+Credit-American(CR)	& 15	& 690	& 0.022	& 44 \%	& Categorical(9) and numeric (6)\\ \hline
+Credit-German(GC)	& 20	& 1000	& 0.020 & 30 \%	& Categorical (13) and Numeric (7)\\ \hline
+Hepatitis(H)	& 19	& 155	& 0.123	& 21 \%	& Categorical (13) and Numeric (6)\\ \hline
+Ionosphere(I)	& 34	& 351	& 0.097	& 36 \%	& All Numeric\\ \hline
 %KR-vs-KP	& 36	& 3196	& 0.011	& 48 \%	& All Categorical\\ \hline
@@
 performances of several well known methods such as Symmetrical
-Uncertainty Rank (SUR), Gain Ratio Rank (GRR), Information Gain Rank
-(IGR), Correlation Based Rank (CBR), Conditional Entropy Rank (CER)~\cite{guyon_jmlr03}, 
-Correlation-based Feature Subset Selection (CFS)~\cite{Hall1998}, 
-Reliff (R)~\cite{Robnik-Sikonja2003} , mRMR~\cite{peng2005} and our proposed 
-methods: High Recall Expectation (HRE) and High Recall Log likelihood (HRL), 
-High Precision Expectation (HPE), High Precision Log likelihood (HPL). 
-The first five methods are variable rank methods and the last seven
-are subset rank methods.
+Uncertainty Rank (SUR), Gain Ratio Rank (GRR), Mutual Information Rank
+(MIR), Correlation Based Rank (CR), Conditional Entropy Rank (CER)~\cite{guyon_jmlr03}, Correlation-based Feature Subset Selection (CS)~\cite{Hall1998}, Reliff (RF)~\cite{Robnik-Sikonja2003} , Minimum Redundancy Maximum Relevancem(MRMR)~\cite{peng2005} and our proposed methods:  Disjunction Voting Expectation(DVE) and  Disjunction Voting likelihood (DVL), Conjunction Voting Expectation (CVE), Conjunction Voting likelihood (CVL).
+The first five methods are variable rank methods and the last seven are subset rank methods.
 The first five methods are variable rank methods that select variables by ranking them with some metric and the last seven are subset rank methods that assess subsets of variables and consider previous selections to decide the next selection.
-
-{\bf TODO Rodrigo: please update acronyms in plots with those given above,
-use MRMR for MRMR... sorry, does not seem sensible to shorten this to 3 letters.}
-
-% TODO: Scott... any interesting things to point out?  
-%       Class imbalance / feature-data ratios?
 
@@
 In addition, we used three different classifiers to solve each of the
-binary classifier problem. Logistic Regression (LR), SVM Linear (SVM) and Naive
-Bayes (NB) were used in the experiments and the first two are implemented
+binary classifier problem. Logistic Regression, SVM Linear and Naive
+Bayes were used in the experiments and the first two are implemented
 in the LibLinear library~\cite{REF08a} and the last one is implemented in
@@
 \begin{figure*}[tbp!]
-\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Accuracy.pdf}\vspace{-20mm}\includegraphics[width=0.10\textwidth]{./figures/dataset_perf/legend.PNG}\\
+\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Accuracy.pdf}\\
 \includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Recall.pdf}
+\includegraphics[width=0.10\textwidth]{./figures/dataset_perf/legend.PNG}
 \caption{\footnotesize Performance of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.}
@@
 \centering
-\includegraphics[width=0.9\textwidth]{./figures/class_perf/Accuracy.pdf}\\
-\includegraphics[width=0.9\textwidth]{./figures/class_perf/Recall.pdf}
+\includegraphics[width=0.42\textwidth]{./figures/class_perf/Accuracy.pdf}
+\includegraphics[width=0.42\textwidth]{./figures/class_perf/Recall.pdf}
+\includegraphics[width=0.15\textwidth]{./figures/class_perf/legend.PNG}
 \caption{\footnotesize Performance of various feature selection algorithms per classifier, averaged across dataset and each stage of feature selection.}
@@
 various feature selection algorithms per dataset, averaged across
-classifier type and each stage of feature selection.  We observe...
+classifier type and each stage of feature selection. We can observe that our approaches improve recall and accuracy in many of the binary classification problem.
 % TODO Scott
@@
 In Figure~\ref{fig:perf_vs_classifier}, we examine how well our 
-novel feature selection algorithms HRE, HRL, HPE, HPL 
+novel feature selection algorithms DVE, DVL, CVE, CVL 
 perform vs. classifier, noting that overall performance is best
 for Naive Bayes followed by Logistic Regression and noticeably worse for
-the SVM --- it seems simply that the probabilistic nature of our feature selection
+the SVM Linear --- it seems simply that the probabilistic nature of our feature selection
 dovetail best with classification methods that are themselves probabilistic,
 and overall best with Naive Bayes which makes the same independence assumptions.
-{\bf TODO Rodrigo: can we get bargraphs like those in FeatureSelection classifier,
-except only showing HRE, HRL, HPE, HPL *and* averaging over all datasets?
-So major group={HRE, HRL, HPE, HPL}, minor group={SVM,LR,NB} and one graph
-for each of A/P/R/F.  Also the filename should not have spaces.}
 
@@
 samples taken for each dataset, classifier type, and stage of feature
-selection.  Here we see Y.  We observe...
+selection.
+This graph shows that our high recall feature selection improve recall with improvements noticeable when there is a high feature to data ratio such as in the Newsgroup(NG) and Spect(S) data sets.

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/conclusions.tex
Update

\section{Conclusion}

In this paper we argued that no feature selection methods have
previously targeted recall for the task of binary classification and
we proposed a model and objectives to address this task.  Empirically,
our results show that our high recall feature selection approach shows
strong performance on recall with significant improvements over other
methods in cases where there is a high feature to data ratio.
Future extensions of this work may examine tighter integration of the
feature selection method with the algorithm to make an \emph{embedded}
approach based on our model since at it's core is a voting-based
classifier.

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Update

@@
-\section{Empirical}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In this section, we conduct experiments to study the feature selection
-performances of several well known methods such as Symmetrical
-Uncertainty Rank (SUR), Gain Ratio Rank (GRR), Information Gain Rank
-(IGR), Correlation Based Rank (CBR), Conditional Entropy Rank (CER)~\cite{guyon_jmlr03}, 
-Correlation-based Feature Subset Selection (CFS)~\cite{Hall1998}, 
-Reliff (R)~\cite{Robnik-Sikonja2003} , mRMR~\cite{peng2005} and our proposed 
-methods: High Recall Expectation (HRE) and High Recall Log likelihood (HRL), 
-High Precision Expectation (HPE), High Precision Log likelihood (HPL). 
-The first five methods are variable rank methods and the last seven
-are subset rank methods.
-The first five methods are variable rank methods that select variables by ranking them with some metric and the last seven are subset rank methods that assess subsets of variables and consider previous selections to decide the next selection.
-
-{\bf TODO Rodrigo: please update acronyms in plots with those given above,
-use MRMR for MRMR... sorry, does not seem sensible to shorten this to 3 letters.}
-
-% TODO: Scott... any interesting things to point out?  
-%       Class imbalance / feature-data ratios?
-
-In this experimental study, we evaluated each feature selection
-method on a variety of binary classification problems 
-from the UCI machine learning repository \cite{Bache+Lichman:2013}.
-These datasets along with their properties are outlined in 
-Table~\ref{table:stats}.
-
-In addition, we used three different classifiers to solve each of the
-binary classifier problem. Logistic Regression (LR), SVM Linear (SVM) and Naive
-Bayes (NB) were used in the experiments and the first two are implemented
-in the LibLinear library~\cite{REF08a} and the last one is implemented in
-the Weka software~\cite{weka}.
-
-To evaluate feature selection algorithm performance, we perform 
-10-fold nested cross-validation (nesting for tuning hyperparameters of each classification
-algorithm) and evaluate accuracy, precision, and recall at each stage of
-feature selection from the first selected feature through to the maximum
-(either 50 or the number of features in the dataset, whichever is smaller).
-%and F-Score for the true label class, that
-%could be identified by the context of the problem and usually be the
-%class with least samples in the data set.
-
-In our evaluation, we wish to answer the following questions:
-Do different feature selection methods perform better with
-each classifier or on each dataset in comparison to others?
-How reliably do the different feature selection methods perform overall
-in terms of their performance distribution?
-%\item Do any dataset features seem to correlate with algorithm performance?
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall.pdf}
-\includegraphics[width=0.45\textwidth]{./figures/linegraphs/SpectNaiveBayesRecall.pdf}\\
-\includegraphics[width=0.45\textwidth]{./figures/linegraphs/NewsgroupLogisticRegressionRecall.pdf}
-\includegraphics[width=0.45\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall.pdf}
+\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall.pdf}
+\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectNaiveBayesRecall.pdf}\\
+\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupLogisticRegressionRecall.pdf}
+\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall.pdf}
 \caption{\footnotesize Performance distribution of various feature selection algorithms with samples taken for each dataset, classifier type, and stage of feature selection.}
@@
 
+\section{Empirical}
+
+In this section, we conduct experiments to study the feature selection
+performances of several well known methods such as Symmetrical
+Uncertainty Rank (SUR), Gain Ratio Rank (GRR), Mutual Information Rank
+(MIR), Correlation Based Rank (CR), Conditional Entropy Rank (CER)~\cite{guyon_jmlr03}, Correlation-based Feature Subset Selection (CS)~\cite{Hall1998}, Reliff (RF)~\cite{Robnik-Sikonja2003} , Minimum Redundancy Maximum Relevancem(MRMR)~\cite{peng2005} and our proposed methods:  Disjunction Voting Expectation(DVE) and  Disjunction Voting likelihood (DVL), Conjunction Voting Expectation (CVE), Conjunction Voting likelihood (CVL).
+The first five methods are variable rank methods and the last seven are subset rank methods.
+The first five methods are variable rank methods that select variables by ranking them with some metric and the last seven are subset rank methods that assess subsets of variables and consider previous selections to decide the next selection.
+
+In this experimental study, we evaluated each feature selection
+method on a variety of binary classification problems 
+from the UCI machine learning repository \cite{Bache+Lichman:2013}.
+These datasets along with their properties are outlined in 
+Table~\ref{table:stats}.
+
+In addition, we used three different classifiers to solve each of the
+binary classifier problem. Logistic Regression, SVM Linear and Naive
+Bayes were used in the experiments and the first two are implemented
+in the LibLinear library~\cite{REF08a} and the last one is implemented in
+the Weka software~\cite{weka}.
+
+To evaluate feature selection algorithm performance, we perform 
+10-fold nested cross-validation (nesting for tuning hyperparameters of each classification
+algorithm) and evaluate accuracy, precision, and recall at each stage of
+feature selection from the first selected feature through to the maximum
+(either 50 or the number of features in the dataset, whichever is smaller).
+%and F-Score for the true label class, that
+%could be identified by the context of the problem and usually be the
+%class with least samples in the data set.
+
+In our evaluation, we wish to answer the following questions:
+Do different feature selection methods perform better with
+each classifier or on each dataset in comparison to others?
+How reliably do the different feature selection methods perform overall
+in terms of their performance distribution?
+%\item Do any dataset features seem to correlate with algorithm performance?
+
 To answer these questions, we first start with

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/model.tex
Update

--- 2014-02-03 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/model.tex
@@
 
-Feature selection is the selection of a subset of features $F^*$ from the complete feature space $F,$ for a specific classification/prediction problem, without loosing too much performance on some given measures.
-The benefit of feature selection include more explainable model, reduced computation time/power, and the avoidance of overfitting.
+%Feature selection is the selection of a subset of features $F^*$ from
+%the complete feature space $F,$ for a specific
+%classification/prediction problem, without loosing too much
+%performance on some given measures. The benefit of feature selection
+%include more explainable model, reduced computation time/power, and
+%the avoidance of overfitting.
+%
+%Existing feature selection algorithms, whose performance show no
+%statistical difference on out benchmark, are mostly ad-hoc. They give
+%various answers to optimisation, but none of them gives the
+%question. In this project, we started from the first principles,
+%proposed a graphical model, and built a new feature selection system
+%upon it.
 
-Existing feature selection algorithms, whose performance show no statistical difference on out benchmark, are mostly ad-hoc.
-They give various answers to optimisation, but none of them gives the question.
-In this project, we started from the first principles, proposed a graphical model, and built a new feature selection system upon it.
+%\subsection{Graphical Model}
 
-\subsection{Graphical Model}
+In our work, we wish to derive a model of feature selection in the
+filtering framework that focuses specifically on recall (we assume the
+classifier itself aims to maximize accuracy or some surrogate).  To
+begin our derivation, we propose a graphical model of feature
+selection for the binary classification problem, as shown in
+Figure~\ref{fig:model}. Double-walled nodes represent observed
+variables, including the data point vector $\vec{x}^{d},$ selected
+features $f_i^*$ (where $1\leq i\leq k,$ $f_i\in F$) and the
+supervised class label $y^d.$ Single-walled circle nodes represent
+latent (unobserved) variables, including a selected attribute of data
+point vector $f_i^x,$ and prediction from a feature $y^d_i.$
 
-To begin the derivation, we propose a graphical model of feature selection for binary classification problem, as shown in figure~\ref{fig:model}.
-Double-circle nodes represent observed variables, including the data point vector $\vec{x}^{\,d},$ selected features $f_i^*$ (where $1\leq i\leq k,$ $f_i\in F$) and the supervised class label $y^d.$ Single-circle nodes represent latent variables, including a selected attribute of data point vector $f_i^x,$ and prediction from a feature $y^d_i.$
-
-Since jointly optimising this objective is NP-hard, we will build $F^*$ in a greedy manner by choosing the next optimal feature $f^*_k$ given the previous set of optimal features $F^*_{k-1}$ and recursively defining $F^*_k = F^*_{k-1}\cup f^*_k$ with $F^*_0 = \emptyset$.
-The measure of the fitness of a model can either be Expectation or Likelihood.
+Since jointly optimizing this objective is NP-hard, we will build
+$F^*$ in a greedy manner by choosing the next optimal feature $f^*_k$
+given the previous set of optimal features $F^*_{k-1}$ and recursively
+defining $F^*_k = F^*_{k-1}\cup f^*_k$ with $F^*_0 = \emptyset$. The
+measure of the fitness of a set of selected features $^*_k$ can be
+expressed in terms of log or expected likelihood, derived as follows:
 
@@
 	\includegraphics[scale=0.9]{Plots_1.pdf}
-	\caption{Graphical model. Double-wall circle denotes observed nodes, single-wall circle denotes hidden nodes.}
+	\caption{\footnotesize A probabilistic voting model of classification represented as a graphical model. 
+Double-walled circles denote observed nodes, single-walled circles denote latent (unobserved) nodes.}
 	\label{fig:model}
@@
 
-\section{Expectation}
+%\subsection{Objective}
+
+\COMMENT
+\subsubsection{Expected Likelihood}
 The initial objective is defined as:
@@
 Now we can optimise our initial objective aiming three goals of classification tasks: Precision, Recall, and General n-out-of-k.
+\ENDCOMMENT
+
+\paragraph{Log Likelihood}
+
+Because Figure~\ref{fig:model} essentially provides a probabilistic classifier model as a function
+of the input data and selected features, we can choose features as to maximize the log likelihood
+of the data given the model (i.e., features selected), i.e., $l(D|F)$ as follow:
+
+\begin{align}
+f_k^*&\equiv\argmax_{f_k} l(D|F^*_k) \nonumber\\
+f_k^*&\equiv\argmax_{f_k}\,log\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
+&=\argmax_{f_k}\sum_{d\in D}log\left(\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\right)\nonumber\\
+&=\argmax_{f_k}\sum_{d\in D}log\sum_{\{y_i^d\}_{1\leq i\leq k}}\frac{P\left(y^d,\vec{x}^{\,d}, F_k,\{y_i^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
+&=\argmax_{f_k} \sum_{d \in D} log\sum_{{\{y_i^d\}}_{1\leq i \leq k}} \frac{P\left(y^d| \{y^d_i\}_{1 \leq i \leq k}\right) \prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d}, F_k\right)}\nonumber\\
+&=\argmax_{f_k}\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\nonumber
+\end{align}
+
+Here, we rewrote the likelihood of a binary event as its probability,
+factorized the conditional probability in the joint probability
+divided by the marginal, marginalized over $\{y^d_i\}_{1\leq i\leq
+  k}$, factorized joint probability in conditional and prior following
+the graphical model and exploited D-separation to remove irrelevant
+conditions and to cancel terms in the equation.
+
+\paragraph{Expected Likelihood}
+
+In contrast to log likelihood which tends to give more weight to extreme
+probabilities, we may wish to instead maximize expected likelihood
+defined as follows:
+\begin{align*}
+f_k^*&=\argmax_{f_k}E_D\left[P\left(y^d|\vec{x}^{\,d},F_k\right)\right]\nonumber\\
+&=\argmax_{f_k}\frac{1}{|D|}\sum_{d\in D} P\left(y^d | \vec{x}^{\,d},F_k\right)\nonumber\\
+&=\argmax_{f_k} \sum_{d\in D} P\left(y^d | \vec{x}^{\,d},F_k\right)\nonumber\\
+\end{align*}
+If we remove the logarithm from the previous derivation above, we easily
+derive the final result of the log likelihood, except without the logarithm.
+
+%Since $\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq
+%    k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq
+%  k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)$ is
+%exactly the same as the result in the expectation case, and the
+%logarithm is a monotonous function, the choice of likelihood instead
+%of expectation has no further affect on the algorithm.
+
+\paragraph{Voting Schemes for High Recall}
+
+Critically, it is how we specify the model and objective that we
+believe should encourage feature selection with high recall.  
+In the following we focus on ***
 
@@
 Meanwhile, if $y^d$ is true, \eqref{eq:expect_recall_2} gives lower score to features that have higher probability to predict false, penalizing false negatives.
-
-\subsection{Likelihood}
-\begin{align}
-f_k^*&\equiv\argmax_{f_k}\,log\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
-&=\argmax_{f_k}\sum_{d\in D}log\left(\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\right)\nonumber\\
-&=\argmax_{f_k}\sum_{d\in D}log\sum_{\{y_i^d\}_{1\leq i\leq k}}\frac{P\left(y^d,\vec{x}^{\,d}, F_k,\{y_i^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
-&=\argmax_{f_k} \sum_{d \in D} log\sum_{{\{y_i^d\}}_{1\leq i \leq k}} \frac{P\left(y^d| \{y^d_i\}_{1 \leq i \leq k}\right) \prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d}, F_k\right)}\nonumber\\
-&=\argmax_{f_k}\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\nonumber
-\end{align}
-Here, we rewrote the likelihood of a binary event as its probability, factorized the conditional probability in the joint probability divided by the marginal, marginalized over $\{y^d_i\}_{1\leq i\leq k}$, factorized joint probability in conditional and prior following the graphical model and exploited d-separation to remove irrelevant conditions and to cancel terms in the equation.
-
-Since $\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)$ is exactly the same as the result in the expectation case, and the logarithm is a monotonous function, the choice of likelihood instead of expectation has no further affect on the algorithm.

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/related_work.tex
Updated empirical results
Update

@@
-\section{Related Work}
+\section{Existing Feature Selection Algorithms}
 
@@
 by evaluating their usefulness to a given classifier, filter methods
-evaluate feature subsets according to certain properties of
+evaluate feature subsets according to certain properties of features 
 themselves. Within filter methods, feature selection algorithms can be
 further classified into ranking methods and subset methods. The former
-evaluates each features independently, while the latter evaluates a
+evaluate each feature independently, while the latter evaluate a
 subset at a time \cite{brown2012conditional}. Listed below is a brief
-introduction to algorithms to which we compared our proposed model.
+introduction to popular feature selection algorithms that we later
+compare to.
 
@@
 
-Correlation based subset \cite{Hall1998} is an extension
+Correlation-based subset \cite{Hall1998} is an extension
 of Pearson's $r$ to subset methods. It measures the linear correlation
@@
 algorithm to which we compared our work is MRMR \cite{peng2005}.
-MRMR is an information-theory-based method that not only maximises
+MRMR is an information-theoretic method that not only maximizes
 the relevance of selected features to the supervised output class,
-but also minimises the redundancy among selected features. Different
+but also minimizes the redundancy among selected features. Different
 search strategies can be applied using these two algorithms as
@@
 Although existing algorithms give various solutions, they are mostly
-ad-hoc, until \cite{brown2012conditional}. Brown et al.\ derived an
-information-theoretical model from first principles, and retro-fitted
+ad-hoc, until \cite{brown2012conditional}. Brown et al.\ derived a 
+probabilistic model with information-theoretic motivations from first principles, and retro-fitted
 existing information-theory-based feature selection methods to the
-model. In this paper, we consider the other side of the same coin. We
-proposed a probability-theory-based graphical model that has intuitive
-qualitative meaning in precision and recall, and we built a
-generalized feature selection scheme upon it.
+model. In this paper, we also take a derivational approach to
+specifying a probabilistic model and optimizing a feature selection
+objective w.r.t. that model, but in our case we focus on the specific
+task of optimizing for recall in binary classification, which it 
+seems no prior method has focused on in previous work.

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/model.tex
Near Final Draft

@@
 
-Feature selection is the selection of a subset of features $F^*$ from the complete feature space $F,$ for a specific classification/prediction problem, without loosing too much performance on some given measures.
-The benefit of feature selection include more explainable model, reduced computation time/power, and the avoidance of overfitting.
+%Feature selection is the selection of a subset of features $F^*$ from
+%the complete feature space $F,$ for a specific
+%classification/prediction problem, without loosing too much
+%performance on some given measures. The benefit of feature selection
+%include more explainable model, reduced computation time/power, and
+%the avoidance of overfitting.
+%
+%Existing feature selection algorithms, whose performance show no
+%statistical difference on out benchmark, are mostly ad-hoc. They give
+%various answers to optimisation, but none of them gives the
+%question. In this project, we started from the first principles,
+%proposed a graphical model, and built a new feature selection system
+%upon it.
 
-Existing feature selection algorithms, whose performance show no statistical difference on out benchmark, are mostly ad-hoc.
-They give various answers to optimisation, but none of them gives the question.
-In this project, we started from the first principles, proposed a graphical model, and built a new feature selection system upon it.
+%\subsection{Graphical Model}
 
-\subsection{Graphical Model}
+In our work, we wish to derive a model of feature selection in the
+filtering framework that focuses specifically on recall (we assume the
+classifier itself aims to maximize accuracy or some surrogate).  To
+begin our derivation, we propose a graphical model of feature
+selection for the binary classification problem, as shown in
+Figure~\ref{fig:model}. Double-walled nodes represent observed
+variables, including the data point vector $\vec{x}^{d},$ selected
+features $f_i^*$ (where $1\leq i\leq k,$ $f_i\in F$) and the
+supervised class label $y^d.$ Single-walled circle nodes represent
+latent variables, including a selected attribute of data
+point vector $f_i^x,$ and prediction from a feature $y^d_i.$
 
-To begin the derivation, we propose a graphical model of feature selection for binary classification problem, as shown in figure~\ref{fig:model}.
-Double-circle nodes represent observed variables, including the data point vector $\vec{x}^{\,d},$ selected features $f_i^*$ (where $1\leq i\leq k,$ $f_i\in F$) and the supervised class label $y^d.$ Single-circle nodes represent latent variables, including a selected attribute of data point vector $f_i^x,$ and prediction from a feature $y^d_i.$
-
-Since jointly optimising this objective is NP-hard, we will build $F^*$ in a greedy manner by choosing the next optimal feature $f^*_k$ given the previous set of optimal features $F^*_{k-1}$ and recursively defining $F^*_k = F^*_{k-1}\cup f^*_k$ with $F^*_0 = \emptyset$.
-The measure of the fitness of a model can either be Expectation or Likelihood.
+Since jointly optimizing this objective is NP-hard, we build
+$F^*$ in a greedy manner by choosing the next optimal feature $f^*_k$
+given the previous set of optimal features $F^*_{k-1}$ and recursively
+defining $F^*_k = F^*_{k-1}\cup f^*_k$ with $F^*_0 = \emptyset$. The
+fitness measure of a set of selected features $^*_k$ can be
+expressed in terms of log or expected likelihood, discussed next.
 
@@
 
+{\small
 \begin{align}
@@
 &=\argmax_{f_k}\sum_{d\in D}\sum_{\{y_{i}^d\}_{1\leq i\leq k}}\frac{P\left(y^d,\vec{x}^{\,d},F_k,\{y_{i}^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
-=\argmax_{f_k}&\sum_{d \in D}\sum_{{\{y_{i}^d\}}_{1\leq i\leq k}}\frac{P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\left(\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d}, f_i\right)\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
+%=\argmax_{f_k}&\sum_{d \in D}\sum_{{\{y_{i}^d\}}_{1\leq i\leq k}}\frac{P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\left(\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d}, f_i\right)\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
 &=\argmax_{f_k}\sum_{d\in D}\sum_{\{y_i^d\}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\label{eq:expect}
-\end{align}
+\end{align}}
 
-Here, we rewrote the expectation of a binary event as its probability, factorized the conditional probability in the joint probability divided by the marginal, marginalised over $\{y^d_i\}_{1\leq i\leq k}$, factorized joint probability in conditional and prior following the graphical model and exploited d-separation to remove irrelevant conditions and to cancel terms in the equation.
+Here, we rewrote the expectation of a binary event as its probability,
+factorized the conditional probability in the joint probability
+divided by the marginal, marginalised over $\{y^d_i\}_{1\leq i\leq
+  k}$, factorized joint probability in conditional and prior following
+the graphical model and exploited d-separation to remove irrelevant
+conditions and to cancel terms in the equation.
 
 Now we can optimise our initial objective aiming three goals of classification tasks: Precision, Recall, and General n-out-of-k.
+\ENDCOMMENT
 
-\subsection{Precision}
-In order to select the subset of features providing high precision binary classifier we need the agreement of all features predictors $y^d_i$ to predict true.
-That is, when $y^d$ is true we need all of the predictors $y^d_i$ equals to true, and if $y^d$ were false, just one of the predictors $y^d_i$ would have to be false.
-Then the probability $P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)$ can be expressed as follows:
-\begin{equation}
-P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)=I\left[y^d=\bigwedge_{i=1}^k y^d_i\right]=
-\begin{cases}
+\paragraph{Log Likelihood (L)}
+
+Because Figure~\ref{fig:model} essentially provides a probabilistic classifier model as a function
+of the input data and selected features, we can choose features as to maximize the log likelihood
+of the data given the model (i.e., features selected), i.e., $l(D|F)$ as follows:
+{\small 
+\begin{align}
+f_k^*&=\argmax_{f_k} l(D|F^*_k) \nonumber\\
+&=\argmax_{f_k}\,\log\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
+&=\argmax_{f_k}\sum_{d\in D}\log\left(\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\right)\nonumber \\
+%\end{align}
+%\begin{align}
+&=\argmax_{f_k}\sum_{d\in D}\log \!\!\! \sum_{\{y_i^d\}_{1\leq i\leq k}} \!\!\! \frac{P\left(y^d,\vec{x}^{\,d}, F_k,\{y_i^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
+%&=\argmax_{f_k} \sum_{d \in D} \log\sum_{{\{y_i^d\}}_{1\leq i \leq k}} \frac{P\left(y^d| \{y^d_i\}_{1 \leq i \leq k}\right) \prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d}, F_k\right)}\nonumber\\
+&=\argmax_{f_k}\sum_{d\in D}\log \!\!\! \sum_{{\{y_i^d\}}_{1\leq i\leq k}} \!\!\! P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right) \prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right) \label{eq:expect} 
+\end{align}}
+
+Here, we rewrote the likelihood of a binary event as its probability,
+factorized the conditional probability in the joint probability
+divided by the marginal, marginalized over $\{y^d_i\}_{1\leq i\leq
+  k}$, factorized joint probability in conditional and prior following
+the graphical model and exploited D-separation to remove irrelevant
+conditions and to cancel terms in the equation.
+
+\paragraph{Expected Likelihood (E)}
+
+In contrast to log likelihood which tends to give more weight to extreme
+probabilities, we may wish to instead maximize expected likelihood
+defined as follows:
+\begin{align*}
+f_k^*&=\argmax_{f_k}E_D\left[P\left(y^d|\vec{x}^{\,d},F_k\right)\right]\nonumber\\
+&=\argmax_{f_k}\frac{1}{|D|}\sum_{d\in D} P\left(y^d | \vec{x}^{\,d},F_k\right)\nonumber\\
+&=\argmax_{f_k} \sum_{d\in D} P\left(y^d | \vec{x}^{\,d},F_k\right)\nonumber\\
+\end{align*}
+If we remove the logarithm from the previous derivation above, we easily
+derive the final result of the log likelihood in~\eqref{eq:expect} without the $\log$.
+
+%Since $\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq
+%    k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq
+%  k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)$ is
+%exactly the same as the result in the expectation case, and the
+%logarithm is a monotonous function, the choice of likelihood instead
+%of expectation has no further affect on the algorithm.
+
+\paragraph{Voting Schemes for High Recall}
+
+Critically, it is how we specify the model and objective that we
+believe should encourage feature selection with high recall.
+Specifically, we have complete license in Figure~\ref{fig:model} to
+determine the conditional probability $P(y^d|\{y^d_i\})$, which
+represents how the class prediction $y_d$ is determined from the class
+prediction of each feature denoted as $y^d_i$.  Here we consider two
+different extreme voting schemes represent logical conjuntion and
+disjunction of the feature votes (defined shortly).  If we use
+conjunction, we require strong agreement among all features for a
+datum to be classified as true while for the disjunctive case, only
+one feature need vote true for the classification to be true.
+Overall, we believe conjunctive is better in terms of cancelling
+effects of noisy features (hence leading to accuracy), but we derive
+the results for both conjunction and disjunction since they are
+symmetric and will allow us to test this hypothesis.  We remark that a
+critical feature of our two objectives above based on log and expected
+likelihood is that each datum is weighted equally and the newly
+selected features $f_k^*$ which leads to more correct classifications
+for more data (especially those not already classified correctly under
+the model of Figure~\ref{fig:model}) are more likely to be selected,
+hence overall targeted recall.
+
+\paragraph{Conjunctive Voting (CV)}
+In order to select the subset of features with conjunctive voting, 
+we need the agreement of all features predictors
+$y^d_i$ to predict true. That is, when $y^d$ is true we need all of
+the predictors $y^d_i$ equals to true, and if $y^d$ were false, just
+one of the predictors $y^d_i$ would have to be false. Then the
+probability $P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)$ can be
+expressed as follows:
+{\small 
+\begin{align}
+P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right) & =I\left[y^d=\bigwedge_{i=1}^k y^d_i\right] \nonumber\\
+&= \begin{cases}
 	y^d=1 \text{ when } \{y_i^d=1\}_{1\leq i\leq k}\\
@@
 \end{cases}\label{eq:expect_pre_1}
-\end{equation}
-Then, we combined equations \eqref{eq:expect} and \eqref{eq:expect_pre_1}, separated each term according to the actual label value $y^d$ and used the probability sum rule to rewire the second term as follows:
+\end{align}}
+Then, we combined equations \eqref{eq:expect} and
+\eqref{eq:expect_pre_1}, separated each term according to the actual
+label value $y^d$ and used the probability sum rule to rewire the
+second term as follows:
 \begin{align}
@@
 \end{align}
-From \eqref{eq:expect_pre_2} we can intuitively describe how this equation is related to the precision metric.
-In the confusion matrix, Precision is calculated dividing the numbers of true positives by the number of all examples predicted as positive (true positives and false positives).
-When $y^d$ is true, \eqref{eq:expect_pre_2} gives higher score to feature that have higher probability to predict true, encouraging true positives.
-Meanwhile, if $y^d$ is false, \eqref{eq:expect_pre_2} gives lower score to features that have higher probability to predict true, penalising false positives.
+From \eqref{eq:expect_pre_2} we can intuitively describe how this
+equation is related to the precision metric. In the confusion matrix,
+Precision is calculated dividing the numbers of true positives by the
+number of all examples predicted as positive (true positives and false
+positives). When $y^d$ is true, \eqref{eq:expect_pre_2} gives higher
+score to feature that have higher probability to predict true,
+encouraging true positives. Meanwhile, if $y^d$ is false,
+\eqref{eq:expect_pre_2} gives lower score to features that have higher
+probability to predict true, penalising false positives.
 
-\subsection{Recall case}
-In order to select the subset of features providing high recall binary classifier we need at least one $y^d_i$ to predict true.
-Therefore, we need a disjunction operation between the predictors $y^d_i$.
-That is, when $y^d$ is true, we need at least one predictor $y^d_i$ to equals to true, and if $y^d$ were false, all of the predictors $y^d_i$ would have to be false.
-Then the probability $P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)$ can be expressed as follows:
-\begin{equation}
-P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)=I\left[y^d=\bigvee_{i=1}^k y^d_i\right]=
-\begin{cases}
+\paragraph{Disjunctive Voting (DV)}
+In order to select the subset of features with disjunctive voting,
+we need at least one $y^d_i$ to predict true. Therefore, we
+need a disjunction operation between the predictors $y^d_i$. That is,
+when $y^d$ is true, we need at least one predictor $y^d_i$ to equals
+to true, and if $y^d$ were false, all of the predictors $y^d_i$ would
+have to be false. Then the probability $P\left(y^d|\{y^d_i\}_{1\leq
+  i\leq k}\right)$ can be expressed as follows:
+{\small 
+\begin{align}
+P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right) & =I\left[y^d=\bigvee_{i=1}^k y^d_i\right] \nonumber \\
+& = \begin{cases}
 	y^d=1 \text{ when } \{y_i^d\}_{1\leq i\leq k,\exists{y_j^d\|y_j^d=1}}\\
@@
 \end{cases}\label{eq:expect_recall_1}
-\end{equation}
-Here, we combined equations \eqref{eq:expect} and \eqref{eq:expect_recall_1}, separated each term according to the actual label value $y^d$ and used the probability sum rule to rewrite the second term as follows:
+\end{align}}
+Here, we combined equations \eqref{eq:expect} and
+\eqref{eq:expect_recall_1}, separated each term according to the
+actual label value $y^d$ and used the probability sum rule to rewrite
+the second term as follows:
 \begin{align}
@@
 \end{align}
-From \eqref{eq:expect_recall_2} we can intuitively describe how this equation is related to the precision metric.
-In the confusion matrix, Recall is calculated dividing the numbers of actual true positives by the number of all true positives (true positives and false negatives).
-When $y^d$ is false, \eqref{eq:expect_recall_2} gives higher score to feature that have higher probability to predict false, encouraging true negatives.
-Meanwhile, if $y^d$ is true, \eqref{eq:expect_recall_2} gives lower score to features that have higher probability to predict false, penalizing false negatives.
-
-\subsection{Likelihood}
-\begin{align}
-f_k^*&\equiv\argmax_{f_k}\,log\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
-&=\argmax_{f_k}\sum_{d\in D}log\left(\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\right)\nonumber\\
-&=\argmax_{f_k}\sum_{d\in D}log\sum_{\{y_i^d\}_{1\leq i\leq k}}\frac{P\left(y^d,\vec{x}^{\,d}, F_k,\{y_i^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
-&=\argmax_{f_k} \sum_{d \in D} log\sum_{{\{y_i^d\}}_{1\leq i \leq k}} \frac{P\left(y^d| \{y^d_i\}_{1 \leq i \leq k}\right) \prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d}, F_k\right)}\nonumber\\
-&=\argmax_{f_k}\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\nonumber
-\end{align}
-Here, we rewrote the likelihood of a binary event as its probability, factorized the conditional probability in the joint probability divided by the marginal, marginalized over $\{y^d_i\}_{1\leq i\leq k}$, factorized joint probability in conditional and prior following the graphical model and exploited d-separation to remove irrelevant conditions and to cancel terms in the equation.
-
-Since $\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)$ is exactly the same as the result in the expectation case, and the logarithm is a monotonous function, the choice of likelihood instead of expectation has no further affect on the algorithm.
+From \eqref{eq:expect_recall_2} we can intuitively describe how this
+equation is related to the precision metric. In the confusion matrix,
+Recall is calculated dividing the numbers of actual true positives by
+the number of all true positives (true positives and false
+negatives). When $y^d$ is false, \eqref{eq:expect_recall_2} gives
+higher score to feature that have higher probability to predict false,
+encouraging true negatives. Meanwhile, if $y^d$ is true,
+\eqref{eq:expect_recall_2} gives lower score to features that have
+higher probability to predict false, penalizing false negatives.

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
UpdatE

@@
 \begin{table*}[tbp!]
+%\vspace{-1mm}
 \centering
+{\small 
 \begin{tabular}{|l|r|r|r|r|l|} \hline
@@
 %Sonar	        & 60	& 208	& 0.288 & 47 \%	& All Numeric\\ \hline
-\end{tabular}
-\caption{\footnotesize Statistics of the various datasets evaluated in this work.}
+\end{tabular}}
+\vspace{-1mm}
+\caption{\footnotesize Descriptive statistics of the various datasets evaluated in this work.}
 \label{table:stats}
+\vspace{-4mm}
 \end{table*}
@@
 \includegraphics[width=0.10\textwidth]{./figures/dataset_perf/legend.PNG}
-\caption{\footnotesize Performance of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.}
+\vspace{-2mm}
+\caption{\footnotesize Performance of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.
+Overall the newly proposed CVL method performs well on Recall on most datasets, while the Recall performance of other feature selection algorithms vary; interestingly the best performance is achieved for datasets a high ratio of features to data indicating that the strong conjunctive voting scheme of CVL may help reduce noise in feature selection for these datasets.
+}
 \label{fig:perf_vs_dataset}
+\vspace{-4mm}
 \end{figure*}
@@
 \includegraphics[width=0.15\textwidth]{./figures/class_perf/legend.PNG}
-\caption{\footnotesize Performance of various feature selection algorithms per classifier, averaged across dataset and each stage of feature selection.}
+\vspace{-6mm}
+\caption{\footnotesize Performance of various feature selection algorithms per classifier, averaged across dataset and each stage of feature selection.
+DVE, DVL, CVE, and CVL align with the independence assumptions of Naive Bayes and the maximum (conditional) likelihood framework of Naive Bayes and Logistic Regression, which may explain the better excellent performance of these algorithms with these classifiers.}
 \label{fig:perf_vs_classifier}
 \end{figure*}
+%\vspace{-6mm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall.pdf}
-\caption{\footnotesize Performance distribution of various feature selection algorithms with samples taken for each dataset, classifier type, and stage of feature selection.}
+%\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall2.pdf}
+%\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectNaiveBayesRecall2.pdf}\\
+%\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupLogisticRegressionRecall2.pdf}
+%\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall2.pdf}
+\caption{\footnotesize Performance distribution of various feature selection algorithms for two datasets and classifier types at each stage of feature selection.
+The conjunctive voting methods do best overall in these datasets.}
 \label{fig:perf_vs_fs_alg}
@@
 samples taken for each dataset, classifier type, and stage of feature
-selection.
-This graph shows that our high recall feature selection improve recall with improvements noticeable when there is a high feature to data ratio such as in the Newsgroup(NG) and Spect(S) data sets.
+selection. This graph shows that our CVL high recall feature selection approach 
+improves recall with the most improvement noticeable when there is a high
+feature to data ratio such as in the Newsgroup (NG) and Spect (S) data
+sets.  We conjecture the reason for this stems from the strong agreement of
+features provided by the conjunctive voting scheme that helps reduce noise
+in the feature selection process.

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/model.tex
UpdatE

@@
 features $f_i^*$ (where $1\leq i\leq k,$ $f_i\in F$) and the
-supervised class label $y^d.$ Single-walled circle nodes represent
+supervised class label $y^d$. Single-walled circle nodes represent
 latent variables, including a selected attribute of data
-point vector $f_i^x,$ and prediction from a feature $y^d_i.$
+point vector $f_i^x$ (i.e., the value resulting from applying
+a deterministic feature function $f_i$ to data input $\vec{x}$) and
+the prediction from a feature $y^d_i \in \{0,1\}$ (whose conditional
+probability is the maximum likelihood estimate w.r.t.\ the data $D$).
+The only part of this model that we have not yet specified is 
+$P(y^d|\{y^d_i\})$ which determines how an observed classification 
+prediction $y^d$ is made given the latent predictions $y^d_i$ of each 
+selected feature $f_i$.  We use a deterministic voting scheme
+to represent this conditional probability, which we will discuss
+in-depth shortly.  First we focus on selecting features which optimize
+this model.
 
@@
 defining $F^*_k = F^*_{k-1}\cup f^*_k$ with $F^*_0 = \emptyset$. The
-fitness measure of a set of selected features $^*_k$ can be
+fitness measure of a selected feature set $F^*_k$ can be
 expressed in terms of log or expected likelihood, discussed next.
@@
 of the input data and selected features, we can choose features as to maximize the log likelihood
-of the data given the model (i.e., features selected), i.e., $l(D|F)$ as follows:
+of the data given the model (i.e., features selected), i.e., $l(D|F_k^*)$ as follows:
+
 {\small 
 \begin{align}
-f_k^*&=\argmax_{f_k} l(D|F^*_k) \nonumber\\
+f_k^*&=\argmax_{f_k} l(D|F^*_k) \nonumber
+\end{align}
+\begin{align}
 &=\argmax_{f_k}\,\log\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
 &=\argmax_{f_k}\sum_{d\in D}\log\left(\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\right)\nonumber \\
-%\end{align}
-%\begin{align}
 &=\argmax_{f_k}\sum_{d\in D}\log \!\!\! \sum_{\{y_i^d\}_{1\leq i\leq k}} \!\!\! \frac{P\left(y^d,\vec{x}^{\,d}, F_k,\{y_i^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/related_work.tex

--- 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/related_work.tex
@@
 Existing feature selection algorithms fall into categories of filter
-methods and wrapper methods \cite{guyon_jmlr03}. While
-wrapper methods, such as SVM-RFE \cite{guyon2002gene}, select features
-by evaluating their usefulness to a given classifier, filter methods
+methods and wrapper methods \cite{guyon_jmlr03}.
+Wrapper methods, such as SVM-RFE \cite{guyon2002gene}, select features by evaluating their usefulness to a given classifier, they usually produce the best results but they are computationally expensive to large data sets or to high dimensional problems.
+Filter methods
 evaluate feature subsets according to certain properties of features 

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/related_work.tex

@@
   class $Y,$ i.e.\ $I\left(X;Y\right).$
-\item The gain ratio of feature $X$ is defined as the information gain
+\item The gain ratio of feature $X$ is defined as the mutual information
   of feature $X$ normalized against the entropy of itself,

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/model.tex
Update

@@
 features $f_i^*$ (where $1\leq i\leq k,$ $f_i\in F$) and the
-supervised class label $y^d.$ Single-walled circle nodes represent
-latent (unobserved) variables, including a selected attribute of data
-point vector $f_i^x,$ and prediction from a feature $y^d_i.$
+supervised class label $y^d$. Single-walled circle nodes represent
+latent variables, including a selected attribute of data
+point vector $f_i^x$ (i.e., the value resulting from applying
+a deterministic feature function $f_i$ to data input $\vec{x}$) and
+the prediction from a feature $y^d_i \in \{0,1\}$ (whose conditional
+probability is the maximum likelihood estimate w.r.t.\ the data $D$).
+The only part of this model that we have not yet specified is 
+$P(y^d|\{y^d_i\})$ which determines how an observed classification 
+prediction $y^d$ is made given the latent predictions $y^d_i$ of each 
+selected feature $f_i$.  We use a deterministic voting scheme
+to represent this conditional probability, which we will discuss
+in-depth shortly.  First we focus on selecting features which optimize
+this model given some $P(y^d|\{y^d_i\})$.
 
-Since jointly optimizing this objective is NP-hard, we will build
+Since jointly optimizing this objective is NP-hard, we build
 $F^*$ in a greedy manner by choosing the next optimal feature $f^*_k$
@@
 defining $F^*_k = F^*_{k-1}\cup f^*_k$ with $F^*_0 = \emptyset$. The
-measure of the fitness of a set of selected features $^*_k$ can be
-expressed in terms of log or expected likelihood, derived as follows:
+fitness measure of a selected feature set $F^*_k$ can be
+expressed in terms of log or expected likelihood, discussed next.
 
@@
 &=\argmax_{f_k}\sum_{d\in D}\sum_{\{y_{i}^d\}_{1\leq i\leq k}}\frac{P\left(y^d,\vec{x}^{\,d},F_k,\{y_{i}^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
-=\argmax_{f_k}&\sum_{d \in D}\sum_{{\{y_{i}^d\}}_{1\leq i\leq k}}\frac{P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\left(\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d}, f_i\right)\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
+%=\argmax_{f_k}&\sum_{d \in D}\sum_{{\{y_{i}^d\}}_{1\leq i\leq k}}\frac{P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\left(\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d}, f_i\right)\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
 &=\argmax_{f_k}\sum_{d\in D}\sum_{\{y_i^d\}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\label{eq:expect}
-\end{align}
+\end{align}}
 
-Here, we rewrote the expectation of a binary event as its probability, factorized the conditional probability in the joint probability divided by the marginal, marginalised over $\{y^d_i\}_{1\leq i\leq k}$, factorized joint probability in conditional and prior following the graphical model and exploited d-separation to remove irrelevant conditions and to cancel terms in the equation.
+Here, we rewrote the expectation of a binary event as its probability,
+factorized the conditional probability in the joint probability
+divided by the marginal, marginalised over $\{y^d_i\}_{1\leq i\leq
+  k}$, factorized joint probability in conditional and prior following
+the graphical model and exploited d-separation to remove irrelevant
+conditions and to cancel terms in the equation.
 
@@
 
-\paragraph{Log Likelihood}
+\paragraph{Log Likelihood (L)}
 
 Because Figure~\ref{fig:model} essentially provides a probabilistic classifier model as a function
-of the input data and selected features, we can choose features as to maximize the log likelihood
-of the data given the model (i.e., features selected), i.e., $l(D|F)$ as follow:
+of the input data and selected features, we can choose features so as to maximize the log likelihood
+of the data given the model (i.e., features selected), i.e., $l(D|F_k^*)$ as follows:
 
+{\small 
 \begin{align}
-f_k^*&\equiv\argmax_{f_k} l(D|F^*_k) \nonumber\\
-f_k^*&\equiv\argmax_{f_k}\,log\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
-&=\argmax_{f_k}\sum_{d\in D}log\left(\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\right)\nonumber\\
-&=\argmax_{f_k}\sum_{d\in D}log\sum_{\{y_i^d\}_{1\leq i\leq k}}\frac{P\left(y^d,\vec{x}^{\,d}, F_k,\{y_i^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
-&=\argmax_{f_k} \sum_{d \in D} log\sum_{{\{y_i^d\}}_{1\leq i \leq k}} \frac{P\left(y^d| \{y^d_i\}_{1 \leq i \leq k}\right) \prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d}, F_k\right)}\nonumber\\
-&=\argmax_{f_k}\sum_{d\in D}log\sum_{{\{y_i^d\}}_{1\leq i\leq k}}P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)\prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)\nonumber
+f_k^*&=\argmax_{f_k} l(D|F^*_k) \nonumber
 \end{align}
+\begin{align}
+&=\argmax_{f_k}\,\log\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
+&=\argmax_{f_k}\sum_{d\in D}\log\left(\frac{P\left(y^d,\vec{x}^{\,d},F_k\right)}{P\left(\vec{x}^{\,d},F_k\right)}\right)\nonumber \\
+&=\argmax_{f_k}\sum_{d\in D}\log \!\!\! \sum_{\{y_i^d\}_{1\leq i\leq k}} \!\!\! \frac{P\left(y^d,\vec{x}^{\,d}, F_k,\{y_i^d\}_{1\leq i\leq k}\right)}{P\left(\vec{x}^{\,d},F_k\right)}\nonumber\\
+%&=\argmax_{f_k} \sum_{d \in D} \log\sum_{{\{y_i^d\}}_{1\leq i \leq k}} \frac{P\left(y^d| \{y^d_i\}_{1 \leq i \leq k}\right) \prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right)P\left(\vec{x}^{\,d}\right)\prod_{i=1}^kP\left(f_i\right)}{P\left(\vec{x}^{\,d}, F_k\right)}\nonumber\\
+&=\argmax_{f_k}\sum_{d\in D}\log \!\!\! \sum_{{\{y_i^d\}}_{1\leq i\leq k}} \!\!\! P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right) \prod_{i=1}^kP\left(y_i^d|\vec{x}^{\,d},f_i\right) \label{eq:expect} 
+\end{align}}
 
@@
 
-\paragraph{Expected Likelihood}
+\paragraph{Expected Likelihood (E)}
 
@@
 If we remove the logarithm from the previous derivation above, we easily
-derive the final result of the log likelihood, except without the logarithm.
+derive the final result of the log likelihood in~\eqref{eq:expect} without the $\log$.
 
@@
 believe should encourage feature selection with high recall.
-In the following we focus on ***
+Specifically, we have complete license in Figure~\ref{fig:model} to
+determine the conditional probability $P(y^d|\{y^d_i\})$, which
+represents how the class prediction $y_d$ is determined from the class
+prediction of each feature denoted as $y^d_i$.  Here we consider two
+different extreme voting schemes represent logical conjuntion and
+disjunction of the feature votes (defined shortly).  If we use
+conjunction, we require strong agreement among all features for a
+datum to be classified as true while for the disjunctive case, only
+one feature need vote true for the classification to be true.
+Overall, we believe conjunctive is better in terms of cancelling
+effects of noisy features (hence leading to accuracy), but we derive
+the results for both conjunction and disjunction since they are
+symmetric and will allow us to test this hypothesis.  We remark that a
+critical feature of our two objectives above based on log and expected
+likelihood is that each datum is weighted equally and the newly
+selected features $f_k^*$ which leads to more correct classifications
+for more data (especially those not already classified correctly under
+the model of Figure~\ref{fig:model}) are more likely to be selected,
+hence overall targeted recall.
 
-\subsection{Precision}
-In order to select the subset of features providing high precision binary classifier we need the agreement of all features predictors $y^d_i$ to predict true.
-That is, when $y^d$ is true we need all of the predictors $y^d_i$ equals to true, and if $y^d$ were false, just one of the predictors $y^d_i$ would have to be false.
-Then the probability $P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)$ can be expressed as follows:
-\begin{equation}
-P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)=I\left[y^d=\bigwedge_{i=1}^k y^d_i\right]=
-\begin{cases}
+\paragraph{Conjunctive Voting (CV)}
+In order to select the subset of features with conjunctive voting, 
+we need the agreement of all features predictors
+$y^d_i$ to predict true. That is, when $y^d$ is true we need all of
+the predictors $y^d_i$ equals to true, and if $y^d$ were false, just
+one of the predictors $y^d_i$ would have to be false. Then the
+probability $P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)$ can be
+expressed as follows:
+{\small 
+\begin{align}
+P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right) & =I\left[y^d=\bigwedge_{i=1}^k y^d_i\right] \nonumber\\
+&= \begin{cases}
 	y^d=1 \text{ when } \{y_i^d=1\}_{1\leq i\leq k}\\
@@
 \end{align}
-From \eqref{eq:expect_recall_2} we can intuitively describe how this equation is related to the precision metric.
-In the confusion matrix, Recall is calculated dividing the numbers of actual true positives by the number of all true positives (true positives and false negatives).
-When $y^d$ is false, \eqref{eq:expect_recall_2} gives higher score to feature that have higher probability to predict false, encouraging true negatives.
-Meanwhile, if $y^d$ is true, \eqref{eq:expect_recall_2} gives lower score to features that have higher probability to predict false, penalizing false negatives.
+From \eqref{eq:expect_recall_2} we can intuitively describe how this
+equation is related to the precision metric. In the confusion matrix,
+Recall is calculated dividing the numbers of actual true positives by
+the number of all true positives (true positives and false
+negatives). When $y^d$ is false, \eqref{eq:expect_recall_2} gives
+higher score to feature that have higher probability to predict false,
+encouraging true negatives. Meanwhile, if $y^d$ is true,
+\eqref{eq:expect_recall_2} gives lower score to features that have
+higher probability to predict false, penalizing false negatives.

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/conclusions.tex
Update

@@
 feature selection method with the algorithm to make an \emph{embedded}
-approach based on our model since at it's core is a voting-based
-classifier.
+approach 
+using the classifier implicit in our model.
+%based on our model since at it's core is a voting-based
+%classifier.

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Update

@@
-\section{Empirical}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table*}[tbp!]
+%\vspace{-1mm}
 \centering
+{\small 
 \begin{tabular}{|l|r|r|r|r|l|} \hline
@@
 %Sonar	        & 60	& 208	& 0.288 & 47 \%	& All Numeric\\ \hline
-\end{tabular}
-\caption{\footnotesize Statistics of the various datasets evaluated in this work.}
+\end{tabular}}
+\vspace{-1mm}
+\caption{\footnotesize Descriptive statistics of the various datasets evaluated in this work.}
 \label{table:stats}
+\vspace{-4mm}
 \end{table*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tbp!]
+\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Accuracy.pdf}\\
+\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Recall.pdf}
+\includegraphics[width=0.10\textwidth]{./figures/dataset_perf/legend.PNG}
+\vspace{-2mm}
+\caption{\footnotesize Performance of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.
+Overall the newly proposed CVL method performs well on Recall on most datasets, while the Recall performance of other feature selection algorithms vary; interestingly the best performance is achieved for datasets a high ratio of features to data indicating that the strong conjunctive voting scheme of CVL may help reduce noise in feature selection for these datasets.
+}
+\label{fig:perf_vs_dataset}
+\vspace{-4mm}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tbp!]
+\centering
+\includegraphics[width=0.42\textwidth]{./figures/class_perf/Accuracy.pdf}
+\includegraphics[width=0.42\textwidth]{./figures/class_perf/Recall.pdf}
+\includegraphics[width=0.15\textwidth]{./figures/class_perf/legend.PNG}
+\vspace{-6mm}
+\caption{\footnotesize Performance of various feature selection algorithms per classifier, averaged across dataset and each stage of feature selection.
+DVE, DVL, CVE, and CVL align with the independence assumptions of Naive Bayes and the maximum (conditional) likelihood framework of Naive Bayes and Logistic Regression, which may explain the better excellent performance of these algorithms with these classifiers.}
+\label{fig:perf_vs_classifier}
+\end{figure*}
+%\vspace{-6mm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tbp!]
+\centering
+\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall.pdf}
+\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectNaiveBayesRecall.pdf}\\
+\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupLogisticRegressionRecall.pdf}
+\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall.pdf}
+%\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall2.pdf}
+%\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectNaiveBayesRecall2.pdf}\\
+%\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupLogisticRegressionRecall2.pdf}
+%\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall2.pdf}
+\caption{\footnotesize Performance distribution of various feature selection algorithms for two datasets and classifier types at each stage of feature selection.
+The conjunctive voting methods do best overall in these datasets.}
+\label{fig:perf_vs_fs_alg}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Empirical Evaluation}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[tbp!]
-\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Accuracy.pdf}\\
-\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Recall.pdf}
-\includegraphics[width=0.10\textwidth]{./figures/dataset_perf/legend.PNG}
-\caption{\footnotesize Performance of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.}
-\label{fig:perf_vs_dataset}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[tbp!]
-\centering
-\includegraphics[width=0.42\textwidth]{./figures/class_perf/Accuracy.pdf}
-\includegraphics[width=0.42\textwidth]{./figures/class_perf/Recall.pdf}
-\includegraphics[width=0.15\textwidth]{./figures/class_perf/legend.PNG}
-\caption{\footnotesize Performance of various feature selection algorithms per classifier, averaged across dataset and each stage of feature selection.}
-\label{fig:perf_vs_classifier}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[tbp!]
-\centering
-\includegraphics[width=0.45\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall.pdf}
-\includegraphics[width=0.45\textwidth]{./figures/linegraphs/SpectNaiveBayesRecall.pdf}\\
-\includegraphics[width=0.45\textwidth]{./figures/linegraphs/NewsgroupLogisticRegressionRecall.pdf}
-\includegraphics[width=0.45\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall.pdf}
-\caption{\footnotesize Performance distribution of various feature selection algorithms with samples taken for each dataset, classifier type, and stage of feature selection.}
-\label{fig:perf_vs_fs_alg}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 To answer these questions, we first start with
@@
 for Naive Bayes followed by Logistic Regression and noticeably worse for
-the SVM Linear --- it seems simply that the probabilistic nature of our feature selection
-dovetail best with classification methods that are themselves probabilistic,
+the SVM Linear --- it seems that the probabilistic nature of our feature selection
+dovetail best with classifiers that are themselves probabilistic,
 and overall best with Naive Bayes which makes the same independence assumptions.
@@
 samples taken for each dataset, classifier type, and stage of feature
-selection.
-This graph shows that our high recall feature selection improve recall with improvements noticeable when there is a high feature to data ratio such as in the Newsgroup(NG) and Spect(S) data sets.
+selection. This graph shows that our CVL high recall feature selection approach 
+improves recall with the most improvement noticeable when there is a high
+feature to data ratio such as in the Newsgroup (NG) and Spect (S) data
+sets.  
+%We conjecture the reason for this stems from the strong agreement of
+%features provided by the conjunctive voting scheme that helps reduce noise
+%during feature selection process.

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/related_work.tex
Update

@@
 Existing feature selection algorithms fall into categories of filter
-methods and wrapper methods \cite{guyon_jmlr03}.
-Wrapper methods, such as SVM-RFE \cite{guyon2002gene}, select features by evaluating their usefulness to a given classifier, they usually produce the best results but they are computationally expensive to large data sets or to high dimensional problems.
-Filter methods
-evaluate feature subsets according to certain properties of features 
-themselves. Within filter methods, feature selection algorithms can be
-further classified into ranking methods and subset methods. The former
-evaluate each feature independently, while the latter evaluate a
-subset at a time \cite{brown2012conditional}. Listed below is a brief
-introduction to popular feature selection algorithms that we later
+methods and wrapper methods \cite{guyon_jmlr03}. Wrapper methods, such
+as SVM-RFE \cite{guyon2002gene}, select features by evaluating their
+usefulness \emph{after} training a given classifier; they often
+produce good results but are computationally expensive when training
+on large data sets or to high-dimensional problems.  In contrast,
+filter methods evaluate feature subsets according to certain
+properties of features themselves.  Within filter methods, feature
+selection algorithms can be further classified into ranking methods
+and subset methods. The former evaluate each feature independently,
+while the latter evaluate a subset at a time
+\cite{brown2012conditional}. Listed below is a brief introduction to
+popular filter-based feature selection algorithms that we later
 compare to.

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/background.tex
Intermediate update
Update

--- 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/background.tex
@@
 along with standard definitions of performance metrics we may wish 
-to optimize.  We then follow this by a discussion of feature selection and
-existing criteria proposed in the literature.
+to optimize.  We then follow this by a discussion of feature selection.
+% and existing criteria proposed in the literature.
 
@@
 of length $n$ (e.g., the results of $n$ different medical tests) and
-\emph{actual} binary class label $y^d \in \{ 0 (\mathrm{false}), 1 (\mathrm{true}) \}$ (where
+\emph{actual} binary class label $y^d \in \{ 0 (\mathrm{ false}), 1 (\mathrm{ true}) \}$ (where
 we often write F for false and T for true).
@@
 \begin{align*}
-\textrm{Accuracy}  & = \frac{TP + TN}{TP + FP + FN + TN}
+\textrm{Accuracy}  & = \frac{TP + TN}{TP + FP + FN + TN} \\
 %\textrm{Precision} & = \frac{TP}{TP + FP}
@@
 $\vec{x}^d$.  In general, practitioners often process the raw input vectors
-$\vec{x}^d$ into a subset of features that we'll denote $f_1,\ldots,f_k$.  Whereas
+$\vec{x}^d$ into a subset of features that we'll denote $F_k = \{ f_1,\ldots,f_k \}$.  Whereas
 the raw input may consist of the results of individual tests, a feature $f_i \in \mathbb{R}$
@@
 the classification task.  Hence we might more appropriately write a classifier
-as $C(\vec{x}^d,f_1,\ldots,f_k)$ to represent the raw input data and the features
+as $C(\vec{x}^d,F_k)$ to represent the raw input data and the features
 of the data that the classifier may use.
@@
 we may wish to limit the set of features generated to improve classifier performance
-and this is the task of feature selection --- select $\{f_1,\ldots,f_k\}$ to optimize
+and this is the task of feature selection --- select $F_k$ to optimize
 performance.  There are already a variety of feature selection methods that we outline

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Update

@@
 Dataset & \# Features & \# Data & \# Features/\# Data & \% True Labels & Feature Type\\ \hline \hline 
-Breast Cancer(BC)	& 9	& 699	& 0.013	& 34 \%	& All Numeric\\ \hline
-Diabetes(D)        & 8	& 768	& 0.010	& 35 \%	& All Numeric\\ \hline
-Heart Statlog(HS)	& 13	& 270	& 0.048	& 44 \%	& All Numeric\\ \hline
-Spect(S)	        & 22	& 80	& 0.275 & 33 \%	& Categorical\\ \hline
-Vote(V)	        & 16	& 435	& 0.037	& 39 \%	& Categorical\\ \hline
-Newsgroup(NG)	& 500	& 1963	& 0.255	& 49 \%	& All Binary\\ \hline
-Horse Colic(HC)	& 22	& 368	& 0.060	& 37 \%	& Categorical (16) and numeric (6)\\ \hline
-Credit-American(CR)	& 15	& 690	& 0.022	& 44 \%	& Categorical(9) and numeric (6)\\ \hline
-Credit-German(GC)	& 20	& 1000	& 0.020 & 30 \%	& Categorical (13) and Numeric (7)\\ \hline
-Hepatitis(H)	& 19	& 155	& 0.123	& 21 \%	& Categorical (13) and Numeric (6)\\ \hline
-Ionosphere(I)	& 34	& 351	& 0.097	& 36 \%	& All Numeric\\ \hline
+Breast Cancer (BC)	& 9	& 699	& 0.013	& 34 \%	& All Numeric\\ \hline
+Diabetes (D)        & 8	& 768	& 0.010	& 35 \%	& All Numeric\\ \hline
+Heart Statlog (HS)	& 13	& 270	& 0.048	& 44 \%	& All Numeric\\ \hline
+Spect (S)	        & 22	& 80	& 0.275 & 33 \%	& Categorical\\ \hline
+Vote (V)	        & 16	& 435	& 0.037	& 39 \%	& Categorical\\ \hline
+Newsgroup (NG)	& 500	& 1963	& 0.255	& 49 \%	& All Binary\\ \hline
+Horse Colic (HC)	& 22	& 368	& 0.060	& 37 \%	& Categorical (16) and numeric (6)\\ \hline
+Credit-American (CR)	& 15	& 690	& 0.022	& 44 \%	& Categorical(9) and numeric (6)\\ \hline
+Credit-German (GC)	& 20	& 1000	& 0.020 & 30 \%	& Categorical (13) and Numeric (7)\\ \hline
+Hepatitis (H)	& 19	& 155	& 0.123	& 21 \%	& Categorical (13) and Numeric (6)\\ \hline
+Ionosphere (I)	& 34	& 351	& 0.097	& 36 \%	& All Numeric\\ \hline
 %KR-vs-KP	& 36	& 3196	& 0.011	& 48 \%	& All Categorical\\ \hline
@@
 \end{tabular}}
-\vspace{-1mm}
+\vspace{-2mm}
 \caption{\footnotesize Descriptive statistics of the various datasets evaluated in this work.}
 \label{table:stats}
-\vspace{-4mm}
+\vspace{-3mm}
 \end{table*}
@@
 \caption{\footnotesize Performance distribution of various feature selection algorithms for two datasets and classifier types at each stage of feature selection.
-The conjunctive voting methods do best overall in these datasets.}
+The conjunctive voting methods (CVE and CVL)
+perform well (and reliably) across all four combinations of classifier and dataset.}
 \label{fig:perf_vs_fs_alg}
+\vspace{-3mm}
 \end{figure*}
@@
 Uncertainty Rank (SUR), Gain Ratio Rank (GRR), Mutual Information Rank
-(MIR), Correlation Based Rank (CR), Conditional Entropy Rank (CER)~\cite{guyon_jmlr03}, Correlation-based Feature Subset Selection (CS)~\cite{Hall1998}, Reliff (RF)~\cite{Robnik-Sikonja2003} , Minimum Redundancy Maximum Relevancem(MRMR)~\cite{peng2005} and our proposed methods:  Disjunction Voting Expectation(DVE) and  Disjunction Voting likelihood (DVL), Conjunction Voting Expectation (CVE), Conjunction Voting likelihood (CVL).
+(MIR), Correlation Based Rank (CR), Conditional Entropy Rank (CER)~\cite{guyon_jmlr03}, Correlation-based Feature Subset Selection (CS)~\cite{Hall1998}, Reliff (RF)~\cite{Robnik-Sikonja2003} , Minimum Redundancy Maximum Relevancem(MRMR)~\cite{peng2005} and our proposed methods:  Disjunction Voting Expectation (DVE) and  Disjunction Voting likelihood (DVL), Conjunction Voting Expectation (CVE), Conjunction Voting likelihood (CVL).
 The first five methods are variable rank methods and the last seven are subset rank methods.
@@
 Next we examine Figure~\ref{fig:perf_vs_fs_alg}, where we evaluate the
-performance distribution of various feature selection algorithms with
-samples taken for each dataset, classifier type, and stage of feature
-selection. This graph shows that our CVL high recall feature selection approach 
-improves recall with the most improvement noticeable when there is a high
-feature to data ratio such as in the Newsgroup (NG) and Spect (S) data
-sets.  
+performance distribution of various feature selection algorithms for
+two datasets -- NG and S -- and classifier types -- Logistic
+Regression and Naive Bayes -- at each stage of feature selection.
+This graph shows that our CVL and CVE high recall feature selection
+approaches provide strong recall performance at all stages of
+feature selection in comparison to other selection methods.
+%whose performance varies widely.
 %We conjecture the reason for this stems from the strong agreement of

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/intro.tex
Update

@@
 in the identification of cancerous tumors) and it is critical to have
-feature selection algorithms that are targeted to maintain high recall.
+feature selection algorithms that can target features which provide
+high recall coverage of the data.
 
@@
 features that cover more of the true cases in the data (hence
-discouraging false negatives).
+discouraging false negatives harmful to recall).
 
@@
 empirically compare the resulting feature selection criteria to a wide
-variety of existing methods.
+variety of existing filtering methods.
 
 Our results demonstrate that our high recall feature selection
-approach does indeed improve recall with improvements noticeable when
+approach does indeed improve recall with improvements most significant when 
 there is a high feature to data ratio.  Such results provide a novel

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/abstract.tex
Update

@@
-Feature selection is important in many practical classification
+Feature selection is important in many practical supervised learning
 settings to address computational constraints or to prevent
@@
 methods have been proposed in the literature, little research seems to
-focus on feature selection specifically targeted for precision or
-recall.  In this paper we propose a novel probabilistic model of
-feature selection and argue that MAP inference w.r.t. to two extreme
-objectives in this model respectively yield high precision and high
-recall feature selection.  From each objective, we then derive an
-efficient formula for feature selection in the filtering framework
-(i.e., greedy forward selection) and we empirically compare the
-resulting feature selection criteria to a wide variety of existing
-methods.  Results show that our high precision and high recall feature
-selection approaches improve their intended objectives and more
-reliably than existing methods whose precision and recall performance
-may vary widely across datasets and classifiers.
+focus on feature selection specifically targeted to improve recall in
+the case of binary classification.  In this paper we propose a novel
+probabilistic voting model of feature selection and argue that
+choosing features so as to maximize likelihood objectives w.r.t. this
+model provides an effective method for high recall feature selection.
+For each objective, we derive an efficient formula for feature
+selection in the filtering framework (i.e., greedy forward selection)
+and we empirically compare the resulting feature selection criteria to
+a wide variety of existing methods.  Results show that our high recall
+feature selection approach does indeed improve recall with
+improvements most significant when there is a high feature to data ratio.
+Such results provide a novel and efficient feature selection algorithm
+to target high-recall classification tasks.
 

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/model.tex
Update

@@
 in-depth shortly.  First we focus on selecting features which optimize
-this model.
+this model given some $P(y^d|\{y^d_i\})$.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[tbp!]
@@
 	\caption{\footnotesize A probabilistic voting model of classification represented as a graphical model. 
-Double-walled circles denote observed nodes, single-walled circles denote latent (unobserved) nodes.}
+Double-walled circles denote observed nodes, single-walled circles denote latent (unobserved) nodes.
+In this model, feature class predictions $y_i^d$ are aggregated under a voting scheme to determine 
+label $y^d$.}
 	\label{fig:model}
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Because Figure~\ref{fig:model} essentially provides a probabilistic classifier model as a function
-of the input data and selected features, we can choose features as to maximize the log likelihood
+of the input data and selected features, we can choose features so as to maximize the log likelihood
 of the data given the model (i.e., features selected), i.e., $l(D|F_k^*)$ as follows:

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/model.tex
Update

@@
 probability is the maximum likelihood estimate w.r.t.\ the data $D$).
+
 The only part of this model that we have not yet specified is 
@@
 Since jointly optimizing this objective is NP-hard, we build
-$F^*$ in a greedy manner by choosing the next optimal feature $f^*_k$
+$F_k^*$ in a greedy manner by choosing the next optimal feature $f^*_k$
 given the previous set of optimal features $F^*_{k-1}$ and recursively
@@
 Double-walled circles denote observed nodes, single-walled circles denote latent (unobserved) nodes.
-In this model, feature class predictions $y_i^d$ are aggregated under a voting scheme to determine 
-label $y^d$.}
+In this model, feature $f_i^x$ class predictions $y_i^d$ are aggregated under a voting scheme to determine 
+the output class label $y^d$.}
 	\label{fig:model}
 \end{figure}
+\vspace{-3mm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 &=\argmax_{f_k}\frac{1}{|D|}\sum_{d\in D} P\left(y^d | \vec{x}^{\,d},F_k\right)\nonumber\\
-&=\argmax_{f_k} \sum_{d\in D} P\left(y^d | \vec{x}^{\,d},F_k\right)\nonumber\\
+&=\argmax_{f_k} \sum_{d\in D} P\left(y^d | \vec{x}^{\,d},F_k\right)\nonumber
 \end{align*}
-If we remove the logarithm from the previous derivation above, we easily
-derive the final result of the log likelihood in~\eqref{eq:expect} without the $\log$.
+From here, we derive the result in~\eqref{eq:expect} without the $\log$.
+
+% We may argue for a paper that focuses on feature selection in the
+% case of high feature to data ratios, but we don't do so well on accuracy.
+
+We remark that a critical feature of our two objectives based on log
+and expected likelihood are that each datum is weighted equally in the
+summation and the features $f_k$ that lead to a higher probability of
+correct classification for \emph{more} data w.r.t.\ the existing
+feature set $F_{k-1}$ are more likely to be selected.  By encouraging
+each selected feature to improve the likelihood over all data and
+especially data not covered well by previous selected features, we aim
+to target recall.
+
+With our two data-oriented feature selection objectives now defined,
+we need only plug in a suitable definition of $P(y^d|\{y^d_i\})$ to
+derive our novel feature evaluation criterion.
 
@@
 
-\paragraph{Voting Schemes for High Recall}
+\paragraph{Voting Schemes}
 
-Critically, it is how we specify the model and objective that we
-believe should encourage feature selection with high recall.
-Specifically, we have complete license in Figure~\ref{fig:model} to
-determine the conditional probability $P(y^d|\{y^d_i\})$, which
-represents how the class prediction $y_d$ is determined from the class
-prediction of each feature denoted as $y^d_i$.  Here we consider two
-different extreme voting schemes represent logical conjuntion and
-disjunction of the feature votes (defined shortly).  If we use
-conjunction, we require strong agreement among all features for a
-datum to be classified as true while for the disjunctive case, only
-one feature need vote true for the classification to be true.
-Overall, we believe conjunctive is better in terms of cancelling
-effects of noisy features (hence leading to accuracy), but we derive
-the results for both conjunction and disjunction since they are
-symmetric and will allow us to test this hypothesis.  We remark that a
-critical feature of our two objectives above based on log and expected
-likelihood is that each datum is weighted equally and the newly
-selected features $f_k^*$ which leads to more correct classifications
-for more data (especially those not already classified correctly under
-the model of Figure~\ref{fig:model}) are more likely to be selected,
-hence overall targeted recall.
+Critically, while we believe the use of a log or expected likelihood
+metric should lead to coverage of the data (i.e., recall), our choice
+of model $P(y^d|\{y^d_i\})$ can help reduce noise in the selection
+process.  $P(y^d|\{y^d_i\})$ represents how the class prediction $y_d$
+is determined from the class prediction of each feature denoted as
+$y^d_i$.  Here we consider two different extreme voting schemes
+representing logical conjunction and disjunction of the feature
+``votes'' $y^d_i$, respectively representing strong and weak
+agreement.  If we use conjunction, we require strong agreement among
+all features for a datum to be classified as true, while for the
+disjunctive case, only one feature need vote true for the
+classification to be true.  Overall, we conjecture that conjunctive
+voting is better in terms of reducing noise among features by
+selecting those which tend to agree more often on the true class, but
+we derive the results for both conjunction and disjunction since they
+are symmetric and will allow us to test this hypothesis.
 
@@
 \eqref{eq:expect_pre_1}, separated each term according to the actual
-label value $y^d$ and used the probability sum rule to rewire the
+label value $y^d$ and used the probability sum rule to rewrite the
 second term as follows:
@@
 	y^d=0: 1-\prod_{i=1}^kP\left(y_i^d = 1|\vec{x}^{\,d},f_i\right)
-\end{cases}\label{eq:expect_pre_2}\\[0.5em]
-&=\argmax_{f_k}\sum_{d\in D}
-\begin{cases}
-	y^d=1: \prod_{i=1}^kP\left(y^d = 1|\vec{x}_i^{\,d},f_i\right)\\
-	y^d=0: 1-\prod_{i=1}^kP\left(y^d = 1|\vec{x}_i^{\,d},f_i\right)\nonumber
-\end{cases}
+\end{cases}\label{eq:expect_pre_2}%\\[0.5em]
+%&=\argmax_{f_k}\sum_{d\in D}
+%\begin{cases}
+%	y^d=1: \prod_{i=1}^kP\left(y^d = 1|\vec{x}_i^{\,d},f_i\right)\\
+%	y^d=0: 1-\prod_{i=1}^kP\left(y^d = 1|\vec{x}_i^{\,d},f_i\right)\nonumber
+%\end{cases}
 \end{align}
@@
 	y^d=1: 1-\prod_{i=1}^kP\left(y_i^d=0|\vec{x}^{\,d},f_i\right)
-\end{cases}\label{eq:expect_recall_2}\\
-&=\argmax_{f_k}\sum_{d\in D}
-\begin{cases}
-	y^d=0: \prod_{i=1}^kP\left(y^d=0|\vec{x}_i^{\,d},f_i\right)\\
-	y^d=1: 1-\prod_{i=1}^kP\left(y^d=0|\vec{x}_i^{\,d},f_i\right)
-\end{cases}\nonumber
+\end{cases}\label{eq:expect_recall_2}%\\
+%&=\argmax_{f_k}\sum_{d\in D}
+%\begin{cases}
+%	y^d=0: \prod_{i=1}^kP\left(y^d=0|\vec{x}_i^{\,d},f_i\right)\\
+%	y^d=1: 1-\prod_{i=1}^kP\left(y^d=0|\vec{x}_i^{\,d},f_i\right)
+%\end{cases}\nonumber
 \end{align}

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Latest submitted version

@@
 Dataset & \# Features & \# Data & \# Features/\# Data & \% True Labels & Feature Type\\ \hline \hline 
-Breast Cancer(BC)	& 9	& 699	& 0.013	& 34 \%	& All Numeric\\ \hline
-Diabetes(D)        & 8	& 768	& 0.010	& 35 \%	& All Numeric\\ \hline
-Heart Statlog(HS)	& 13	& 270	& 0.048	& 44 \%	& All Numeric\\ \hline
-Spect(S)	        & 22	& 80	& 0.275 & 33 \%	& Categorical\\ \hline
-Vote(V)	        & 16	& 435	& 0.037	& 39 \%	& Categorical\\ \hline
-Newsgroup(NG)	& 500	& 1963	& 0.255	& 49 \%	& All Binary\\ \hline
-Horse Colic(HC)	& 22	& 368	& 0.060	& 37 \%	& Categorical (16) and numeric (6)\\ \hline
-Credit-American(CR)	& 15	& 690	& 0.022	& 44 \%	& Categorical(9) and numeric (6)\\ \hline
-Credit-German(GC)	& 20	& 1000	& 0.020 & 30 \%	& Categorical (13) and Numeric (7)\\ \hline
-Hepatitis(H)	& 19	& 155	& 0.123	& 21 \%	& Categorical (13) and Numeric (6)\\ \hline
-Ionosphere(I)	& 34	& 351	& 0.097	& 36 \%	& All Numeric\\ \hline
+Breast Cancer (BC)	& 9	& 699	& 0.013	& 34 \%	& All Numeric\\ \hline
+Diabetes (D)        & 8	& 768	& 0.010	& 35 \%	& All Numeric\\ \hline
+Heart Statlog (HS)	& 13	& 270	& 0.048	& 44 \%	& All Numeric\\ \hline
+Spect (S)	        & 22	& 80	& 0.275 & 33 \%	& Categorical\\ \hline
+Vote (V)	        & 16	& 435	& 0.037	& 39 \%	& Categorical\\ \hline
+Newsgroup (NG)	& 500	& 1963	& 0.255	& 49 \%	& All Binary\\ \hline
+Horse Colic (HC)	& 22	& 368	& 0.060	& 37 \%	& Categorical (16) and Numeric (6)\\ \hline
+Credit-American (CR)	& 15	& 690	& 0.022	& 44 \%	& Categorical (9) and Numeric (6)\\ \hline
+Credit-German (GC)	& 20	& 1000	& 0.020 & 30 \%	& Categorical (13) and Numeric (7)\\ \hline
+Hepatitis (H)	& 19	& 155	& 0.123	& 21 \%	& Categorical (13) and Numeric (6)\\ \hline
+Ionosphere (I)	& 34	& 351	& 0.097	& 36 \%	& All Numeric\\ \hline
 %KR-vs-KP	& 36	& 3196	& 0.011	& 48 \%	& All Categorical\\ \hline
@@
 \end{tabular}}
-\vspace{-1mm}
+\vspace{-2mm}
 \caption{\footnotesize Descriptive statistics of the various datasets evaluated in this work.}
 \label{table:stats}
-\vspace{-4mm}
+\vspace{-3.5mm}
 \end{table*}
@@
 \label{fig:perf_vs_dataset}
-\vspace{-4mm}
+\vspace{-3mm}
 \end{figure*}
@@
 \centering
-\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall.pdf}
-\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectNaiveBayesRecall.pdf}\\
-\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupLogisticRegressionRecall.pdf}
-\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall.pdf}
+\includegraphics[width=0.38\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall.pdf}
+\includegraphics[width=0.38\textwidth]{./figures/linegraphs/SpectNaiveBayesRecall.pdf}\\
+\includegraphics[width=0.38\textwidth]{./figures/linegraphs/NewsgroupLogisticRegressionRecall.pdf}
+\includegraphics[width=0.38\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall.pdf}
 %\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall2.pdf}
@@
 %\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall2.pdf}
-\caption{\footnotesize Performance distribution of various feature selection algorithms for two datasets and classifier types at each stage of feature selection.
-The conjunctive voting methods do best overall in these datasets.}
+\caption{\footnotesize Recall performance of various feature selection algorithms for two datasets and classifier types at each stage of feature selection.
+The conjunctive voting methods (CVE and CVL)
+perform well (and reliably) across all four combinations of classifier and dataset.}
 \label{fig:perf_vs_fs_alg}
+%\vspace{-2mm}
 \end{figure*}
@@
 
-\section{Empirical}
+\section{Empirical Evaluation}
 
@@
 Uncertainty Rank (SUR), Gain Ratio Rank (GRR), Mutual Information Rank
-(MIR), Correlation Based Rank (CR), Conditional Entropy Rank (CER)~\cite{guyon_jmlr03}, Correlation-based Feature Subset Selection (CS)~\cite{Hall1998}, Reliff (RF)~\cite{Robnik-Sikonja2003} , Minimum Redundancy Maximum Relevancem(MRMR)~\cite{peng2005} and our proposed methods:  Disjunction Voting Expectation(DVE) and  Disjunction Voting likelihood (DVL), Conjunction Voting Expectation (CVE), Conjunction Voting likelihood (CVL).
-The first five methods are variable rank methods and the last seven are subset rank methods.
-The first five methods are variable rank methods that select variables by ranking them with some metric and the last seven are subset rank methods that assess subsets of variables and consider previous selections to decide the next selection.
+(MIR), Correlation Based Rank (CR), Conditional Entropy Rank
+(CER)~\cite{guyon_jmlr03}, Correlation-based Feature Subset Selection
+(CS)~\cite{Hall1998}, Reliff (RF)~\cite{Robnik-Sikonja2003} , Minimum
+Redundancy Maximum Relevancem(MRMR)~\cite{peng2005} and our proposed
+methods: Disjunction Voting Expectation (DVE) and Disjunction Voting
+likelihood (DVL), Conjunction Voting Expectation (CVE), Conjunction
+Voting likelihood (CVL).  The first five methods are ranking methods
+that select features by ranking them with some metric and the last
+seven are subset rank methods that assess subsets of features and
+consider previous selections to decide the next selection.  The final
+four methods were introduced and derived in the previous section.
 
@@
 each classifier or on each dataset in comparison to others?
-How reliably do the different feature selection methods perform overall
-in terms of their performance distribution?
-%\item Do any dataset features seem to correlate with algorithm performance?
+How reliably do the different feature selection methods perform at
+different stages of feature selection?  
+Do any descriptive dataset features suggest where the different 
+algorithms may perform well?
 
@@
 various feature selection algorithms per dataset, averaged across
-classifier type and each stage of feature selection. We can observe that our approaches improve recall and accuracy in many of the binary classification problem.
+classifier type and each stage of feature selection. We can observe
+here that our approaches generally perform well on recall (at a
+reasonable accuracy level).  Notably, CVL performs best and
+significantly better than competing methods on the NG and S datasets,
+which we remark have the highest feature-to-data ratio and hence 
+represent noisy cases for feature selection.  
+%These results 
+%indicate that the strong conjunctive voting scheme of CVL may help reduce 
+%noise in feature selection for these datasets as previously conjectured.
+
 % TODO Scott
@@
 Next we examine Figure~\ref{fig:perf_vs_fs_alg}, where we evaluate the
-performance distribution of various feature selection algorithms with
-samples taken for each dataset, classifier type, and stage of feature
-selection. This graph shows that our CVL high recall feature selection approach 
-improves recall with the most improvement noticeable when there is a high
-feature to data ratio such as in the Newsgroup (NG) and Spect (S) data
-sets.  We conjecture the reason for this stems from the strong agreement of
-features provided by the conjunctive voting scheme that helps reduce noise
-in the feature selection process.
+performance distribution of various feature selection algorithms for
+two datasets -- NG and S -- and classifier types -- Logistic
+Regression and Naive Bayes -- at each stage of feature selection.
+This graph shows that our CVL and CVE high recall feature selection
+approaches provide strong recall performance at all stages of
+feature selection in comparison to other selection methods.
+%whose performance varies widely.
+%We conjecture the reason for this stems from the strong agreement of
+%features provided by the conjunctive voting scheme that helps reduce noise
+%during feature selection process.

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/intro.tex
Latest submitted version

--- 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/intro.tex
@@
 
-Feature selection~\cite{guyon_jmlr03}
+Feature selection is important in many practical supervised learning
+settings to address computational constraints (e.g., in large-scale or
+online learning) or to prevent overfitting when the data may be
+high-dimensional but contain relatively few samples (e.g., as may
+occur in medical or bioinformatics domains where features are abundant
+but data is costly to obtain)~\cite{guyon_jmlr03}.
 
-While historically, feature selection
+While a wide variety of feature selection methods have been proposed
+in the literature, little research seems to focus on feature selection
+specifically targeted to improve recall (minimization of false
+negatives) in binary classification.  One reason for this is simply
+that most feature selection methods are agnostic to the particular
+supervised learning task --- applying to tasks from classification to
+regression --- and hence are not focused on performance properties
+specific to binary classifiers.  Yet, recall is an important aspect of
+many binary classification problems (e.g., minimizing false negatives
+in the identification of cancerous tumors) and it is critical to have
+feature selection algorithms that can target features which facilitate
+high-recall classification.
 
-Naturally do not want to optimize for precision and recall directly (all false trivially optimizes precision, while all true trivially optimizes accuracy).
-But when selecting features for a classifier intended to maximize accuracy, we may have a secondary preference for features that improve precision (reduce false positive rate) or improve recall (reduce false negative rate).
-To this end, we remark that no previous work seems to have examined feature selection in the context of the precision-recall trade-off/
+Naturally though, it would not make sense for a classifier or feature
+selection method to focus on recall alone since the classifier which
+always predicts \emph{true} (independent of the data) obtains optimal
+recall performance.  To trade off precision with recall in order to
+maintain high accuracy, one often uses a geometric average of the two
+instead (known as F-score) but in practice most classifiers directly
+optimize accuracy or some surrogate, e.g., a convex surrogate of 0-1
+loss as in the SVM or maximum (conditional) likelihood as in Naive
+Bayes or logistic regression.  So how can one achieve a high recall
+SVM, Naive Bayes, or logistic regression classifier that already has a
+well-defined accuracy-focused optimization criterion?  The idea we
+pursue in this paper is that feature selection can help modulate the
+recall performance of existing classifiers by encouraging selection of
+features that cover more of the true cases in the data (hence
+discouraging false negatives harmful to recall).
 
-% Part of the reason is that previous feature selection has not been specific to classification whereas precision/recall are
+In this paper we propose a novel probabilistic voting model of feature
+selection with the intent of encouraging false negative reduction
+while still focusing on accuracy.  We argue that choosing features so
+as to maximize likelihood objectives w.r.t. this model provides an
+effective method for high recall feature selection.  Specifically, for
+each objective, we derive an efficient formula for feature selection
+in the filtering framework (i.e., greedy forward selection) and we
+empirically compare the resulting feature selection criteria to a wide
+variety of existing filtering methods.
+
+Our results demonstrate that our high recall feature selection
+approach does indeed improve recall with improvements most significant when 
+there is a high feature to data ratio.  Such results provide a novel
+and efficient feature selection algorithm to target high-recall
+classification tasks.
+% TODO: elaborate more
+
+\COMMENT
 
@@
 
-in well-known contingency table
+%can switch in columns, but typically predicting more false hurts recall and more true hurts precision
 
-\begin{center}
-\begin{tabular}{l|l|l|} 
-\multicolumn{1}{l}{} &  \multicolumn{1}{l}{Label T} & \multicolumn{1}{l}{Label F} \\ \cline{2-3}
-Predicted T & TP & FP \\ \cline{2-3}
-Predicted F & FN & TN \\ \cline{2-3}
-%Predicted T & TP & FP & \#$T_P$ \\ \cline{2-3}
-%Predicted F & FN & TN & \#$F_P$ \\ \cline{2-3}
-%          &   & \#$T_A$ & \#$F_A$ & \\ \cline{2-3}
-\end{tabular}
-\end{center}
-
-accuracy = tp + tn / tp + fp + fn + tn
-
-precision = tp / tp + fp
-
-recall = tp / tp + fn
-
-can switch in columns, but typically predicting more false hurts recall and more true hurts precision
-
-So precision and recall become secondary objectives after accuracy... provides flexibility in feature selection that has not been explicitly considered.
+%So precision and recall become secondary objectives after accuracy... provides flexibility in feature selection that has not been explicitly considered.
 
@@
 
-\COMMENT
 key insight: literature suggests redundancy is bad idea, but in fact, it is critical for precision (implies agreement)

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/model.tex
Latest submitted version

@@
 selected feature $f_i$.  We use a deterministic voting scheme
-to represent this conditional probability, which we will discuss
-in-depth shortly.  First we focus on selecting features which optimize
+to represent this conditional probability, which we discuss
+in-depth shortly, but first we focus on selecting features which optimize
 this model given some $P(y^d|\{y^d_i\})$.
@@
 	\caption{\footnotesize A probabilistic voting model of classification represented as a graphical model. 
-Double-walled circles denote observed nodes, single-walled circles denote latent (unobserved) nodes.}
+Double-walled circles denote observed nodes, single-walled circles denote latent (unobserved) nodes.
+In this model, feature $f_i^x$ class predictions $y_i^d$ are aggregated under a voting scheme to determine 
+the output class label $y^d$.}
 	\label{fig:model}
 \end{figure}
+\vspace{-3mm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 the graphical model and exploited d-separation to remove irrelevant
-conditions and to cancel terms in the equation.
+conditions and to cancel factors in the equation.
 
@@
 \begin{align}
-f_k^*&=\argmax_{f_k} l(D|F^*_k) \nonumber
-\end{align}
-\begin{align}
+f_k^*&=\argmax_{f_k} l(D|F^*_k) \nonumber\\
+%\end{align}
+%\begin{align}
 &=\argmax_{f_k}\,\log\prod_{d\in D}P\left(y^d|\vec{x}^{\,d},F_k\right)\nonumber\\
@@
 the graphical model and exploited D-separation to remove irrelevant
-conditions and to cancel terms in the equation.
+conditions and to cancel factors in the equation.
 
@@
 &=\argmax_{f_k}\frac{1}{|D|}\sum_{d\in D} P\left(y^d | \vec{x}^{\,d},F_k\right)\nonumber\\
-&=\argmax_{f_k} \sum_{d\in D} P\left(y^d | \vec{x}^{\,d},F_k\right)\nonumber\\
+&=\argmax_{f_k} \sum_{d\in D} P\left(y^d | \vec{x}^{\,d},F_k\right)\nonumber
 \end{align*}
-If we remove the logarithm from the previous derivation above, we easily
-derive the final result of the log likelihood in~\eqref{eq:expect} without the $\log$.
+From here, we easily derive the result in~\eqref{eq:expect} without the $\log$.
+
+% We may argue for a paper that focuses on feature selection in the
+% case of high feature to data ratios, but we don't do so well on accuracy.
+
+We remark that a critical feature of our two objectives based on log
+and expected likelihood are that each datum is weighted equally in the
+summation and the features $f_k$ that lead to a higher probability of
+correct classification for \emph{more} data w.r.t.\ the existing
+feature set $F_{k-1}$ are more likely to be selected.  By encouraging
+each selected feature to improve the likelihood over all data and
+especially data not covered well by previous selected features, we aim
+to target recall.
+
+With our two data-oriented feature selection objectives now defined,
+we need only plug in a suitable definition of $P(y^d|\{y^d_i\})$ to
+derive our novel feature evaluation criterion.  
+%  We discuss this next.
 
@@
 
-\paragraph{Voting Schemes for High Recall}
+\paragraph{Voting Schemes}
 
-Critically, it is how we specify the model and objective that we
-believe should encourage feature selection with high recall.
-Specifically, we have complete license in Figure~\ref{fig:model} to
-determine the conditional probability $P(y^d|\{y^d_i\})$, which
-represents how the class prediction $y_d$ is determined from the class
-prediction of each feature denoted as $y^d_i$.  Here we consider two
-different extreme voting schemes represent logical conjuntion and
-disjunction of the feature votes (defined shortly).  If we use
-conjunction, we require strong agreement among all features for a
-datum to be classified as true while for the disjunctive case, only
-one feature need vote true for the classification to be true.
-Overall, we believe conjunctive is better in terms of cancelling
-effects of noisy features (hence leading to accuracy), but we derive
-the results for both conjunction and disjunction since they are
-symmetric and will allow us to test this hypothesis.  We remark that a
-critical feature of our two objectives above based on log and expected
-likelihood is that each datum is weighted equally and the newly
-selected features $f_k^*$ which leads to more correct classifications
-for more data (especially those not already classified correctly under
-the model of Figure~\ref{fig:model}) are more likely to be selected,
-hence overall targeted recall.
+While we conjectured
+above that expected or log likelihood criteria should help encourage
+recall, we conjecture that our choice of a suitable aggregation or
+``voting'' definition for $P(y^d|\{y^d_i\})$ can help reduce noise in
+the feature selection process.
+%Critically, while we believe the use of a log or expected likelihood
+%metric should lead to coverage of the data (i.e., recall), our choice
+%of model $P(y^d|\{y^d_i\})$ can help reduce noise in the selection
+%process.  $P(y^d|\{y^d_i\})$ represents how the class prediction $y_d$
+%is determined from the class prediction of each feature denoted as
+%$y^d_i$.  
+Here we consider two different extreme voting schemes
+representing logical conjunction and disjunction of the feature
+``votes'' $y^d_i$, respectively representing strong and weak
+agreement.  If we use conjunction, we require strong agreement among
+all features for a datum to be classified as true, while for the
+disjunctive case, only one feature need vote true for the
+classification to be true.
+
+Overall, we conjecture that conjunctive voting is better in terms of
+reducing noise among features by selecting those which tend to agree
+more often on the true class, but we derive the results for both
+conjunction and disjunction since they are symmetric and will allow us
+to test this hypothesis.
 
@@
 $y^d_i$ to predict true. That is, when $y^d$ is true we need all of
-the predictors $y^d_i$ equals to true, and if $y^d$ were false, just
-one of the predictors $y^d_i$ would have to be false. Then the
+the predictors $y^d_i$ equal to true, and when $y^d$ is false, any 
+one of the predictors $y^d_i$ could be false. Then the
 probability $P\left(y^d|\{y^d_i\}_{1\leq i\leq k}\right)$ can be
@@
 \end{align}}
-Then, we combined equations \eqref{eq:expect} and
-\eqref{eq:expect_pre_1}, separated each term according to the actual
-label value $y^d$ and used the probability sum rule to rewire the
+We can combine this with the non-log version of \eqref{eq:expect} to
+obtain CVE where we  
+separate each term according to the actual
+label value $y^d$ and use the probability sum rule to rewrite the
 second term as follows:
@@
 	y^d=0: 1-\prod_{i=1}^kP\left(y_i^d = 1|\vec{x}^{\,d},f_i\right)
-\end{cases}\label{eq:expect_pre_2}\\[0.5em]
-&=\argmax_{f_k}\sum_{d\in D}
-\begin{cases}
-	y^d=1: \prod_{i=1}^kP\left(y^d = 1|\vec{x}_i^{\,d},f_i\right)\\
-	y^d=0: 1-\prod_{i=1}^kP\left(y^d = 1|\vec{x}_i^{\,d},f_i\right)\nonumber
-\end{cases}
+\end{cases}\label{eq:expect_pre_2}%\\[0.5em]
+%&=\argmax_{f_k}\sum_{d\in D}
+%\begin{cases}
+%	y^d=1: \prod_{i=1}^kP\left(y^d = 1|\vec{x}_i^{\,d},f_i\right)\\
+%	y^d=0: 1-\prod_{i=1}^kP\left(y^d = 1|\vec{x}_i^{\,d},f_i\right)\nonumber
+%\end{cases}
 \end{align}
-From \eqref{eq:expect_pre_2} we can intuitively describe how this
-equation is related to the precision metric. In the confusion matrix,
-Precision is calculated dividing the numbers of true positives by the
-number of all examples predicted as positive (true positives and false
-positives). When $y^d$ is true, \eqref{eq:expect_pre_2} gives higher
-score to feature that have higher probability to predict true,
-encouraging true positives. Meanwhile, if $y^d$ is false,
-\eqref{eq:expect_pre_2} gives lower score to features that have higher
-probability to predict true, penalising false positives.
+Under this scheme, we note that when $y^d$ is true,
+\eqref{eq:expect_pre_2} gives higher score to features that have
+higher probability to predict true, encouraging true positives.
+Meanwhile, if $y^d$ is false, \eqref{eq:expect_pre_2} gives lower
+score to features that have higher probability to predict true,
+penalizing false positives.
+
+If we wish to derive the log likelihood version (CVL), we simply insert
+$\log$ after the summation in~\eqref{eq:expect_pre_2}.
 
@@
 \end{align}}
-Here, we combined equations \eqref{eq:expect} and
-\eqref{eq:expect_recall_1}, separated each term according to the
-actual label value $y^d$ and used the probability sum rule to rewrite
+We can combine this with the non-log version of \eqref{eq:expect} to
+obtain DVE, where we  
+separate each term according to the
+actual label value $y^d$ and use the probability sum rule to rewrite
 the second term as follows:
@@
 	y^d=1: 1-\prod_{i=1}^kP\left(y_i^d=0|\vec{x}^{\,d},f_i\right)
-\end{cases}\label{eq:expect_recall_2}\\
-&=\argmax_{f_k}\sum_{d\in D}
-\begin{cases}
-	y^d=0: \prod_{i=1}^kP\left(y^d=0|\vec{x}_i^{\,d},f_i\right)\\
-	y^d=1: 1-\prod_{i=1}^kP\left(y^d=0|\vec{x}_i^{\,d},f_i\right)
-\end{cases}\nonumber
+\end{cases}\label{eq:expect_recall_2}%\\
+%&=\argmax_{f_k}\sum_{d\in D}
+%\begin{cases}
+%	y^d=0: \prod_{i=1}^kP\left(y^d=0|\vec{x}_i^{\,d},f_i\right)\\
+%	y^d=1: 1-\prod_{i=1}^kP\left(y^d=0|\vec{x}_i^{\,d},f_i\right)
+%\end{cases}\nonumber
 \end{align}
-From \eqref{eq:expect_recall_2} we can intuitively describe how this
-equation is related to the precision metric. In the confusion matrix,
-Recall is calculated dividing the numbers of actual true positives by
-the number of all true positives (true positives and false
-negatives). When $y^d$ is false, \eqref{eq:expect_recall_2} gives
-higher score to feature that have higher probability to predict false,
-encouraging true negatives. Meanwhile, if $y^d$ is true,
-\eqref{eq:expect_recall_2} gives lower score to features that have
-higher probability to predict false, penalizing false negatives.
+Under this scheme, we note that when $y^d$ is false,
+\eqref{eq:expect_recall_2} gives a higher score to features that have
+higher probability to predict false, encouraging true negatives.
+Meanwhile, if $y^d$ is true, \eqref{eq:expect_recall_2} gives lower
+score to features that have higher probability to predict false,
+penalizing false negatives.
+
+If we wish to derive the log likelihood version (DVL), we simply insert
+$\log$ after the summation in~\eqref{eq:expect_recall_2}.

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/abstract.tex
Latest submitted version

@@
 a wide variety of existing methods.  Results show that our high recall
-feature selection approach does indeed improve recall with
-improvements noticeable when there is a high feature to data ratio.
+feature selection approach does indeed improve recall --- with
+improvements most significant when there is a high feature to data ratio.
 Such results provide a novel and efficient feature selection algorithm

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/conclusions.tex
Latest submitted version

@@
 methods in cases where there is a high feature to data ratio.
-Future extensions of this work may examine tighter integration of the
-feature selection method with the algorithm to make an \emph{embedded}
-approach 
-using the classifier implicit in our model.
+Future work may examine tighter integration of our 
+feature selection method with its implicit classification 
+algorithm in an efficient embedded approach to high-recall feature selection.
+%using the classifier implicit in our model.
 %based on our model since at it's core is a voting-based

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/related_work.tex
Latest submitted version

@@
 
-Although existing algorithms give various solutions, they are mostly
-ad-hoc, until \cite{brown2012conditional}. Brown et al.\ derived a 
-probabilistic model with information-theoretic motivations from first principles, and retro-fitted
-existing information-theory-based feature selection methods to the
-model. In this paper, we also take a derivational approach to
-specifying a probabilistic model and optimizing a feature selection
+While most existing feature selection methods provide heuristic
+motivation,   \citeauthor{brown2012conditional} 
+\shortcite{brown2012conditional} derived a
+probabilistic model with information-theoretic motivations from first
+principles, and retro-fitted existing information-theory-based feature
+selection methods to their model.
+
+In this paper, we take a derivational approach similar to \citeauthor{brown2012conditional} 
+\shortcite{brown2012conditional}
+that specifies a probabilistic model and optimizes a feature selection
 objective w.r.t. that model, but in our case we focus on the specific
 task of optimizing for recall in binary classification, which it 
-seems no prior method has focused on in previous work.
+seems no prior method has focused on in previous work.  We present
+our model and derivation next.

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Final version

@@
 significantly better than competing methods on the NG and S datasets,
-which we remark have the highest feature-to-data ratio and hence 
+which we remark have the highest feature to data ratio and hence 
 represent noisy cases for feature selection.  
@@
 
-Next we examine Figure~\ref{fig:perf_vs_fs_alg}, where we evaluate the
+Finally, we examine Figure~\ref{fig:perf_vs_fs_alg}, where we evaluate the
 performance distribution of various feature selection algorithms for

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/conclusions.tex
Final version

@@
 we proposed a model and objectives to address this task.  Empirically,
-our results show that our high recall feature selection approach shows
-strong performance on recall with significant improvements over other
-methods in cases where there is a high feature to data ratio.
-Future work may examine tighter integration of our 
-feature selection method with its implicit classification 
-algorithm in an efficient embedded approach to high-recall feature selection.
+our results show that one of our novel feature selection methods (CVL)
+shows strong performance on recall with significant improvements over
+other methods in cases where there is a high feature to data ratio.
+Future work may examine tighter integration of our feature selection
+method with its implicit classification algorithm in an efficient
+embedded approach to high-recall feature selection.
 %using the classifier implicit in our model.

### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Final version (again)

@@
 \begin{figure*}[tbp!]
-\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Accuracy.pdf}\\
-\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Recall.pdf}
+$\qquad$\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Accuracy.pdf}\\
+
+\vspace{-4mm}$\qquad$\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Recall.pdf}
 \includegraphics[width=0.10\textwidth]{./figures/dataset_perf/legend.PNG}
 \vspace{-2mm}
-\caption{\footnotesize Performance of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.
+\caption{\footnotesize Performance (top -- Accuracy, bottom -- Recall) of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.
 Overall the newly proposed CVL method performs well on Recall on most datasets, while the Recall performance of other feature selection algorithms vary; interestingly the best performance is achieved for datasets a high ratio of features to data indicating that the strong conjunctive voting scheme of CVL may help reduce noise in feature selection for these datasets.
@@
 \vspace{-6mm}
-\caption{\footnotesize Performance of various feature selection algorithms per classifier, averaged across dataset and each stage of feature selection.
-DVE, DVL, CVE, and CVL align with the independence assumptions of Naive Bayes and the maximum (conditional) likelihood framework of Naive Bayes and Logistic Regression, which may explain the better excellent performance of these algorithms with these classifiers.}
+\caption{\footnotesize Performance (left -- Accuracy, right -- Recall) of feature selection algorithms per classifier, averaged across dataset and each stage of feature selection.
+DVE, DVL, CVE, and CVL align with the independence assumptions of Naive Bayes and the maximum likelihood framework of Naive Bayes and Logistic Regression, which may explain the better performance of these algorithms with these classifiers.}
 \label{fig:perf_vs_classifier}

### 2014-03-22 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/aaai14_rebuttal_1253.txt

We thank the reviewers for their comments and analysis.

Reviewer 1

1> Empirical evidence and presentation:

Figure 2: In all experiments our method performs well in accuracy and recall, especially on data sets with high feature to data ratio such as S and NG (also shown in figure 4). In these data sets CVL performs significantly better than competing methods. Fig 3 shows our method works better with Naive Bayes.

2> Assumption of independence:

The independence assumptions are encoded in figure 1, and can be deduced with the Bayes Ball algorithm.

3> Joint optimization is NP-hard:

It’s a variant of Knapsack Problem.

4> Why expected likelihood:

We use both so that we can compare their performance empirically.

5> Why disjunctive voting:

Disjunctive voting encourages diversity. If a single feature predicts true, the whole datum predicts true. Theoretically, it should penalize false negative, hence encourage recall. However, we conjecture that conjunctive voting is better due to its advantage in noise reduction.

6> SVM parameters:

The LibLINEAR package is set to run L2-loss support vector machines (dual). All other parameters are tuned via nested cross-validation.

Reviewer 2

1> Why conjunctive voting:

The OR nature of disjunctive voting makes it highly vulnerable to noise in a real-world scenario. Meanwhile, conjunctive voting is noise-resistant, yet it is still able to find novel features that agree *strongly* with the supervised result. It encourages true positives, and therefore, improves recall.

2> Presentation of result:

Refer to reviewer 1, comment 1.

3> Solution looks like a heuristic:

Our method is rigorously derived from the graphical model. Please refer to comment 1 and reviewer 1, comment 5.

Reviewer 3

1> How to get from f_k^x to y_k^d?

f_k*x is a cell in datum vector x^d, as determined by f_k. y_k^d is the prediction using that cell alone.

2> Size of conditional probability table:

Since the algorithm applies to binary classification, and data is discretised, the conditional probability table has size (number of features)*(2)*(number of types of values on that feature).

3> Why deterministic voting?

The two deterministic voting schemes are the two extreme cases. They make the graphical model simple, generative, and allow y_i^d to be inferred from y^d. Also refer to reviewer 1, comment 5 and reviewer 2, comment 1.

4> Lack of references:

Our focus is on feature selection algorithms that encourage classification recall. This topic has not been well explored. In addition, the derivation is based entirely on the proposed graphical model, requiring few references.

5> Why conjunctive voting:

Refer to reviewer 2, comment 1.

6> How the algorithm can be used with probabilistic models that don't apply voting schemes?

Our feature selection algorithms fall within the subset subcategory of filter methods. They are classifier independent.

7> PR-ROC paper:

Our paper focuses on feature selection with the intent of encouraging recall by false negative reduction while still focusing on accuracy. Therefore, PR and ROC curves don't fit in our analysis.
